---
title: "TMEM184B IPMS Analysis"
author: "Erik Larsen"
date: "2025-01-20"
output: 
  html_notebook:
    code_folding: hide
    toc: TRUE
---

## Overview

This markdown was developed to formally document the data analysis pipeline for TMEM184B immunoprecipitation tandem mass-spec
experiments for **Dr. Martha Bhattacharya's lab** at the **University of Arizona** for the (to be published) endolysosomal paper.

Until a container is built, the `R version` used was **R 4.3.2** with the packages installed below

## Set up Environment {.tabset .tabset-pills .tabset-fade}

Load packages

```{r Package Load, include = T, message = F, warning = F, echo = T}
packages <- c('stringr', 'tidyverse', 'ggplot2', 'rstatix', 'tidyr', 'forcats')
for ( package in packages ) {
  if (!require(package, character.only = T)) {
    install.packages(package)
    library(package, character.only = T)
  }
}
```

Adjust the path to the file containing the functions used to extract `GO information`

```{r Source Function Script, include = T, message = F, warning = F, echo = T}
source("C:/Users/Erik/Desktop/Programming/R/Bio/Proteomics/GO_Analysis_Functions.R")
```

Load the IPMS raw data

```{r IPMS data load, include = T, message = F, warning = F, echo = F}
ALL_DF <- read.csv("C:/Users/Erik/Downloads/20220307_4552_4553_BirA_GFP_Samples_View_Report.csv")
```

## Wrangle the TSC Data {.tabset .tabset-pills .tabset-fade}

Break the original wrangling call into commented chunks for clarity

```{r IPMS Data Wrangle 1, include = T, message = F, warning = F, echo = T}
ALL_DF <- ALL_DF |> 
  dplyr::select(-1) |> ## remove empty column
  dplyr::rename_with(~read.csv("C:/Users/Erik/Downloads/20220307_4552_4553_BirA_GFP_Samples_View_Report.csv") |>
                       dplyr::select(-1) |>
                       dplyr::slice(1) |>
                       unlist() |>
                       as.character()) |> # rename the columns using the first row
  dplyr::slice(-1) |> # remove the first row
  dplyr::slice_tail(n = -1) |> # remove the last row
  dplyr::select(-contains("307-411")) |> # remove C terminus samples
  
  dplyr::rename(Proteins.Identified = contains("Proteins"), # rename the protein ID column
                Accession.Number = contains("Accession"), # rename the protein accession number column
                MW = contains("Molecular")) |> # rename the molecular weight column
  
  dplyr::filter(!grepl(Accession.Number, pattern = "DECOY")) |> # filter decoy proteins out
  dplyr::rename_with(~gsub(.x, pattern = '[0-9]+_', replacement = '')) |> # remove _'s from column names
  dplyr::rename_with(~gsub(.x, pattern = '^m', replacement = '')) |> # remove m's from column names (mTMEM)
  
  dplyr::rename(BirAV5_1 = `BirA-V1`, # rename the V5 columns by replacing hyphens with _'s
                BirAV5_2 = `BirA-V2`,
                TMEMV5_1 = `TMEM-V1`,
                TMEMV5_2 = `TMEM-V2`)
```

```{r IPMS Data Wrangle 2, include = T, message = F, warning = F, echo = T}
ALL_DF <- ALL_DF |>
  dplyr::mutate(HumanGeneID = str_extract(Proteins.Identified, pattern = 'GN=[:alnum:]+') |>
                  gsub(Proteins.Identified, pattern = 'GN=', replacement = ''),
                .after = Proteins.Identified) |> # create a column containing proteins' HUGO symbols
  dplyr::mutate(Proteins.Identified = gsub(Proteins.Identified, pattern = ' O.+$', replacement = '')) |> # remove extra strings
  dplyr::mutate(MW = gsub(MW, pattern = ' kDa', replacement = '') |>
                  as.numeric()) |> # remove kDa's from MW column to enable math operations

  dplyr::mutate(across(contains("_"), ~if_else(.x == '?', '0', .x)),
                across(contains("_"), ~if_else(.x == '', '0', .x)),
                across(contains("_"), ~as.numeric(.x)), # replace ?'s and empty columns with 0's and convert to numeric
                
                across(contains("_"), ~if_else(.x == 0, 0.1, .x)), # add 0.1 to 0's for FC calculations
                
                across(contains("_"), .fns = list("MW_norm" = ~.x/MW)) ) # add new columns that normalize TSC's by MW
```

```{r IPMS Data Wrangle 3, include = T, message = F, warning = F, echo = T}
ALL_DF <- ALL_DF |> 
  dplyr::mutate(V5ControlAvg = (BirAV5_1_MW_norm + BirAV5_2_MW_norm)/2,
                mycControlAvg = (GFPmyc_1_MW_norm + GFPmyc_2_MW_norm)/2,
                V5TMEMAvg = (TMEMV5_1_MW_norm + TMEMV5_2_MW_norm)/2,
                mycTMEMAvg = (TMEMmyc_1_MW_norm + TMEMmyc_2_MW_norm)/2, # find tag & bait averages
                
                avgV5_FC = V5TMEMAvg/V5ControlAvg,
                avgmyc_FC = mycTMEMAvg/mycControlAvg, # find the avg FC for each tag
                
                ControlAvg = (BirAV5_1_MW_norm+BirAV5_2_MW_norm+GFPmyc_1_MW_norm+GFPmyc_2_MW_norm)/4, # compute the average MW-normalized average across control bait samples
                TMEMAvg = (TMEMV5_1_MW_norm+TMEMV5_2_MW_norm+TMEMmyc_1_MW_norm+TMEMmyc_2_MW_norm)/4, # compute the average MW-normalized average across target bait samples
                
                avgFC = TMEMAvg/ControlAvg) |> # compute the grand FC
  dplyr::mutate(MouseGeneID = paste(substr(HumanGeneID, 1, 1),
                                    tolower(substr(HumanGeneID, 2, 10)), sep = ''),
                MouseGeneID = case_when(grepl(Accession.Number, pattern = 'p53_HUMAN') ~ "Trp53",
                                        HumanGeneID == 'birA' ~ HumanGeneID,
                                        Proteins.Identified == 'Green fluorescent protein' ~ HumanGeneID,
                                        TRUE ~ MouseGeneID)) |> # create mouse EntrezID column
  dplyr::relocate(MouseGeneID, .after = HumanGeneID) |>
  dplyr::arrange(desc(avgFC)) # sort by grand FC from highest to lowest)
```

## Filter Wrangled IPMS Counts Data {.tabset .tabset-pills .tabset-fade}

Filter using aggressive heuristics Dr. Paul Langlais (University of Arizona College of Molecular Medicine Proteomics; personal communication)

```{r IPMS Filtering, include = T, warning = F, message = F, echo = T}
Compiled_Candidate_List <- ALL_DF |>
  dplyr:::arrange(desc(avgFC)) |>
  dplyr::filter(avgFC > 2,
                avgV5_FC > 2,
                avgmyc_FC > 2, # at least twice as many MW-normalized count avg for each tag, and across all
                (TMEMV5_1 & TMEMV5_2 > 5),
                (TMEMmyc_1 & TMEMmyc_2 > 5), # minimum 5 TSCs across duplicates for each tag AND
                (
                  TMEMV5_1 > 10 |
                    TMEMV5_2 > 10 |
                    TMEMmyc_1 > 10 |
                    TMEMmyc_2 > 10
                ) # at least 10 TSCs in at least one sample
                ) |>
  
  # Remove Mulcahy contams (2008 paper)
  dplyr::filter(!grepl(HumanGeneID,
                       pattern = 'AHNAK|ALB|ANXA(1|2)|ASS1|ATP5|CFL1|CLTC|CSDA|EDARRAD|ENO|FARS(A|B)|FASN|FKSG30|GAPDH|GFAP|ILF(2|3)|LDHA|LGALS(1|3)|PCB(1|2)|PDIA6|PHB|PHB2|POTE2|PPIA|PRDX(1|2|3|4)|SERPIN(H1|A11)|SLC25A|TUFM|TXN|UBA52')) |>
  
  # Remove Dunham contams (2012 review)
  dplyr::filter(!grepl(HumanGeneID,
                       pattern = 'EEF1|EIF|HNRN|HSPA|KRT|TUB(A|B)|RPL|HIST2|H2A|RRP|(X|I)PO|NUP|DNAJ')) |>
  
  dplyr::filter(HumanGeneID != "TMEM184B") |>
  dplyr::select(HumanGeneID) |>
  unlist() |> as.character()
```

Export the candidate list to `.csv` (not shown)

```{r Pre Crapome Candidates, include = F, message = F, warning = F, echo = F}
## export data as csv to upload on CRAPome to find common contaminants
write.table(Compiled_Candidate_List, 'C:/Users/Erik/Desktop/Programming/R/Bio/PreCrapomeCandidateList.csv', row.names = F, col.names = F, sep =',')
```

Import CRAPome results (amend file path; not shown)

```{r Load CRAPome Results 1, include = T, message = F, warning = F, echo = F}
Crapome_results <- read_table(file = 'C:/Users/Erik/Desktop/Programming/R/Bio/CRAPome_results_272.txt')
```

Wrangle CRAPome results

```{r Wrangle Crapome Results, include = T, message = F, warning = F, echo = T}
Crapome_results <- Crapome_results |>
  dplyr::filter(!grepl(Mapped, pattern = '/|identifier')) |>
  dplyr::select(1:7) |>
  dplyr::rename(User_input = User,
                Mapped_Gene_Symbol = Input,
                Num_Exp_Found = Mapped,
                Num_Exp_Total = Symbol,
                Avg_SC = Num,
                Max_SC = of) |>
  dplyr::mutate(across(c(3,5:7), ~as.numeric(.x))) |>
  dplyr::select(-Gene)
```

Identify proteins in **> 5%** of CRAPome studies and remove them

```{r ID Candidates after Crapome filtering, include = T, message = F, warning = F, echo = T}
Crapome_hits <- Crapome_results |>
  dplyr::filter(Num_Exp_Found <= 35.8) |>
  dplyr::select(Mapped_Gene_Symbol) |>
  unlist() |>
  as.character()
```

Export the CRAPome filtered candidate list to `.csv` (not shown)

```{r Write Crapome Hits to file, include = F, message = F, warning = F, echo = F}
write.table(Crapome_hits, 'C:/Users/Erik/Desktop/Programming/R/Bio/PostCrapomeCandidateList.csv', row.names = F, col.names = F, sep = ',')
```

### Apply filtering to TSCs

Use CRAPome list to annotate the TSC data

```{r Filter by CRAPome results, include = T, message = F, warning = F, echo = T}
ALL_DF_filtered <- ALL_DF |>
  dplyr::mutate(poi = 'Background', .after = MouseGeneID) |>
  dplyr::full_join(Crapome_hits |> as.data.frame() |> dplyr::mutate(HumanGeneID = Crapome_hits)) |> 
  dplyr::mutate(poi = case_when(!is.na(Crapome_hits) ~ 'Candidates',
                                HumanGeneID == 'TMEM184B' ~ 'TMEM184B',
                                TRUE ~ poi)) |>
  dplyr::select(-Crapome_hits)
```

## Upload GO Results {.tabset .tabset-pills .tabset-fade}

Upload the result `.txt` files from the `geneontology.org` query

### Cell Component Results

(amend file path)

```{r GO CC, include = T, message = F, warning = F, echo = T}
GO_CC_results <- read.table('C:/Users/Erik/Desktop/Programming/R/Bio/GO_CC_complete_fisher_FDR_all_136.txt', sep = '\t', skip = 11, header = T, quote = '') |>
  dplyr::rename_with(~gsub(.x, pattern = '\\.\\.', replacement = '')) |> # remove .'s from GO CC column
  dplyr::rename_with(~gsub(.x, pattern = 'Homo.sapiens.|upload_1|\\.$', replacement = '')) |> # remove excess strings
  dplyr::rename(GO_Term = GO.cellular.component.complete) |> # rename the CC column
  dplyr::rename(GO_Term_Size = REFLIST20580) |> # rename the GO Term Size column
  dplyr::rename(Overlap = `138`) |> # rename the overlap column
  dplyr::mutate(across(c(2:4,7,8), ~as.numeric(.x))) |> # convert to numeric
  # dplyr::slice(c(1:925)) |> 
  tidyr::separate(GO_Term, into = c("GO_Term", "GO_Term_ID"), sep = '\\s\\(GO:') |> # split the Term ID from the Term
  dplyr::mutate(GO_Term_ID = paste0('GO:', gsub(GO_Term_ID, pattern = '\\)', replacement = ''))) |>
  dplyr::mutate(GO_Type = "CC", .after = GO_Term_ID) |> # create the category column
  dplyr::mutate(fold.Enrichment = str_extract(fold.Enrichment, pattern = '[:alnum:]+') |> as.numeric(fold.Enrichment)) |> # convert the FE column to numeric
  dplyr::arrange(FDR, desc(fold.Enrichment)) # sort by the highest FE and lowest adjusted p-value
```

### Biological Process Results

(amend file path)

```{r GO BP, include = T, message = F, warning = F, echo = T}
GO_BP_results <- read.table('C:/Users/Erik/Desktop/Programming/R/Bio/GO_BP_complete_fisher_FDR_all_136.txt', sep = '\t', skip = 11, header = T, quote = '') |>
  dplyr::rename_with(~gsub(.x, pattern = '\\.\\.', replacement = '')) |> # remove the .'s  from the GO BP column
  dplyr::rename_with(~gsub(.x, pattern = 'Homo.sapiens.|upload_1|\\.$', replacement = '')) |> # remove excess strings
  dplyr::rename(GO_Term = GO.biological.process.complete) |> # rename the BP column
  dplyr::rename(GO_Term_Size = REFLIST20580) |> # rename the GO Term Size column
  dplyr::rename(Overlap = `138`) |> # rename the overlap column
  dplyr::mutate(across(c(2:4,7,8), ~as.numeric(.x))) |> # convert to numeric
  tidyr::separate(GO_Term, into = c("GO_Term", "GO_Term_ID"), sep = '\\s\\(GO:') |> # split the Term ID from the Term
  dplyr::mutate(GO_Term_ID = paste0('GO:', gsub(GO_Term_ID, pattern = '\\)', replacement = ''))) |>
  dplyr::mutate(GO_Type = "BP", .after = GO_Term_ID) |> # create the category column
  dplyr::mutate(fold.Enrichment = str_extract(fold.Enrichment, pattern = '[:alnum:]+') |> as.numeric(fold.Enrichment)) |> # convert the FE column to numeric
  dplyr::arrange(FDR, desc(fold.Enrichment)) # sort by the highest FE and lowest adjusted p-value
```

### Molecular Function Results

(amend file path)

```{r GO MF, include = T, message = F, warning = F, echo = T}
GO_MF_results <- read.table('C:/Users/Erik/Desktop/Programming/R/Bio/GO_MF_complete_fisher_FDR_all_136.txt', sep = '\t', skip = 11, header = T, quote = '') |>
  dplyr::rename_with(~gsub(.x, pattern = '\\.\\.', replacement = '')) |> # remove the .'s from the GO BP column
  dplyr::rename_with(~gsub(.x, pattern = 'Homo.sapiens.|upload_1|\\.$', replacement = '')) |> # remove excess strings
  dplyr::rename(GO_Term = GO.molecular.function.complete) |> # rename the MF column
  dplyr::rename(GO_Term_Size = REFLIST20580) |> # rename the GO Term Size column
  dplyr::rename(Overlap = `138`) |> # rename the overlap column
  dplyr::mutate(across(c(2:4,7,8), ~as.numeric(.x))) |> # convert to numeric
  tidyr::separate(GO_Term, into = c("GO_Term", "GO_Term_ID"), sep = '\\s\\(GO:') |> # split the Term ID from the Term
  dplyr::mutate(GO_Term_ID = paste0('GO:', gsub(GO_Term_ID, pattern = '\\)', replacement = ''))) |>
  dplyr::mutate(GO_Type = "MF", .after = GO_Term_ID) |> # create the category column
  dplyr::mutate(fold.Enrichment = str_extract(fold.Enrichment, pattern = '[:alnum:]+') |> as.numeric(fold.Enrichment)) |> # convert the FE column to numeric
  dplyr::arrange(FDR, desc(fold.Enrichment)) # sort by the highest FE and lowest adjusted p-value
```

### Combine the Results

```{r Combine GO Results, inclue = T, message = F, warning = F, echo = T}
GO_results <- GO_BP_results |>
  dplyr::full_join(GO_CC_results) |>
  dplyr::full_join(GO_MF_results) |>
  dplyr::filter(!grepl(GO_Term, pattern = 'unclassified', ignore.case = T))
```

## Integrate with Custom GO Query Function {.tabset .tabset-pills .tabset-fade}

Call a custom function created to aggregate all GO information for a provided list of gene/protein identifiers

  + queries both `Bioconductor` and `GO` dbs

### Query Bioconductor and GO dbs

```{r GO fn, include = T, message = F, warning = F, echo = T}
GO_INFO_fn(list_of_interest = Crapome_hits, species = 'human')
```

### Integrate Query Results into Counts DF

```{r Join DFs, include = T, message = F, warning = F, echo = T}
GO_INFO_by_TERM_df_sig <- GO_results |>
  dplyr::mutate(db = 'geneontology.org') |>
  dplyr::full_join(GO_INFO_by_TERM_df |> 
                     dplyr::mutate(db = 'bioconductor')) |>
  dplyr::filter(!is.na(GO_Term)) |>
  
  # dplyr::filter(!is.na(GO_Type)) |> # for discrepancies between 
  # geneontology.org and bioconductor; default to geneontology.org
  
  dplyr::mutate(fold.Enrichment = as.numeric(fold.Enrichment)) |>
  dplyr::arrange(desc(fold.Enrichment), FDR) |>
  dplyr::filter(!grepl(GO_Term, pattern = "Unclassified", ignore.case = T)) |>
  dplyr::mutate(sig = case_when(FDR <= 0.001 ~ "***",
                                between(FDR, 0.001, 0.0499) ~ "**",
                                between(FDR, 0.01, 0.05) ~ "*",
                                TRUE ~ "NS"), .after = FDR
  ) # create a statistical significance column for filtering/annotation
```

### Write Result DF to file

Write GO Results DF to file (not shown)

```{r Write GO Results DF to file, include = F, message = F, warning = F, echo = F}
write.table(GO_INFO_by_TERM_df_sig, 'C:\\Users\\Erik\\Desktop\\Programming\\R\\Bio\\MBNeuRoLab\\IPMS_GO_DF.csv', row.names = F, col.names = T, sep = ',')
```

## Plot Results {.tabset .tabset-pills .tabset-fade}

Create DFs for each plot

### Plot Full Scatter

```{r Full Scatter, include = T, message = F, warning = F, echo = T}
ggplot(data = ALL_DF_filtered_full) +
  geom_point(data = subset(ALL_DF_filtered_full, poi == 'Background'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 0.1, size = 3) +
  geom_point(data = subset(ALL_DF_filtered_full, poi == 'Candidates'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 0.3, size = 3) +
  geom_point(data = subset(ALL_DF_filtered_full, poi == 'Control myc'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  geom_point(data = subset(ALL_DF_filtered_full, poi == 'Control V5'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  geom_point(data = subset(ALL_DF_filtered_full, poi == 'TMEM184B'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  coord_cartesian(xlim = c(0,17), ylim = c(0,17)) +
  labs(title = 'TMEM184B IPMS Total Spectral Counts',
       x = 'Average Control IP Prey Spectra (TSC)',
       y = 'Average TMEM184B IP Prey Spectra (TSC)',
       col = 'Protein\nCategory') +
  #guides(col = 'none')+
  geom_abline(slope = 2, intercept = 0, linetype = 'dashed', color = 'black') +
  geom_text(x = 6.5, y = 15, color = 'black', label = 'FC \u2265 2.0', fontface = 'bold', size = 4.5) +
  scale_color_manual(values = c('gray48', 'navy', 'green1', 'deeppink3', 'darkgoldenrod3')) +
  theme_classic()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = 'bold', hjust = 0.5, size = 20),
        axis.text = element_text(face = 'bold', size = 12),
        axis.title = element_text(face = 'bold', size = 15),
        legend.text = element_text(face = 'bold', size = 14),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.5)
        )
```

+ Full overview

```{r Create full plot df, include = T, message = F, warning = F, echo = T}
## redefine protiens of interest for labeling (control baits)
ALL_DF_filtered_full <- ALL_DF_filtered |>
  dplyr::mutate(poi = case_when(grepl(Proteins.Identified, pattern = 'Green fluorescent') ~ 'Control myc',
                                grepl(Proteins.Identified, pattern = 'BirA') ~ 'Control V5',
                                TRUE ~ poi)) # full scatter
```

### vATPase Scatter (zoom)

```{r vATPase Scatter zoom, include = T, message = F, warning = F, echo = T}
ggplot(data = ALL_DF_filtered_vATPASE_acidification) +
  geom_point(data = subset(ALL_DF_filtered_vATPASE_acidification, poi == 'Background'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 0.1) +
  geom_point(data = subset(ALL_DF_filtered_vATPASE_acidification, poi == 'Candidates'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 0.5, size = 3) +
  geom_point(data = subset(ALL_DF_filtered_vATPASE_acidification, poi == 'Other vATPase\nComplex Subunits'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  geom_point(data = subset(ALL_DF_filtered_vATPASE_acidification, poi == 'Candidates in\nVacuolar Acidification'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  geom_point(data = subset(ALL_DF_filtered_vATPASE_acidification, poi == 'TMEM184B'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0) +
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) +
  labs(title = 'TMEM184B IPMS Total Spectral Counts',
       x = 'Average Control IP Prey Spectra (TSC)',
       y = 'Average TMEM184B IP Prey Spectra (TSC)',
       col = 'Protein\nCategory') +
  #guides(col = 'none')+
  geom_abline(slope = 2, intercept = 0, linetype = 'dashed', color = 'black', size = 1) +
  geom_text(x = 1.2, y = 3, color = 'black', label = 'FC \u2265 2.0', fontface = 'bold', size = 4.5) +
  scale_color_manual(values = c('gray48', 'dodgerblue', 'navy', 'magenta', 'darkgoldenrod3')) +
  theme_classic()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = 'bold', hjust = 0.5, size = 20),
        axis.text = element_text(face = 'bold', size = 12),
        axis.title = element_text(face = 'bold', size = 15),
        legend.text = element_text(face = 'bold', size = 14),
        legend.title = element_blank(),
        legend.position = c(0.84, 0.5)
  )
```

+ vATPase hits

```{r Create vatpase plot df, include = T, message = F, warning = F, echo = T}
ALL_DF_filtered_vATPASE_acidification <- ALL_DF_filtered |> 
  dplyr::mutate(poi = case_when((grepl(HumanGeneID, pattern = 'ATP6V0A(1|2)') |
                                   grepl(HumanGeneID, pattern = 'DMXL|CLN6')) &
                                  grepl(HumanGeneID, pattern = paste0(Crapome_hits, collapse = '$|')) ~ 'Candidates in\nVacuolar Acidification',
                                grepl(HumanGeneID, pattern = 'ATP6V') &
                                  !grepl(HumanGeneID, pattern = paste0(Crapome_hits, collapse = '$|')) ~ 'Other vATPase\nComplex Subunits',
                                TRUE ~ poi)) # vATPase scatter
```

### Regulation of Macroautophagy (zoom)

```{r Macro zoom, include = T, message = F, warning = F, echo = T}
ggplot(data = ALL_DF_filterd_reg_macro) +
  geom_point(data = subset(ALL_DF_filterd_reg_macro, poi == 'Background'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 0.1) +
  geom_point(data = subset(ALL_DF_filterd_reg_macro, poi == 'Candidates'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 0.5, size = 3) +
  geom_point(data = subset(ALL_DF_filterd_reg_macro, poi == 'Candidates in\nRegulation of Macroautophagy'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  geom_point(data = subset(ALL_DF_filterd_reg_macro, poi == 'TMEM184B'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) +
  labs(title = 'TMEM184B IPMS Total Spectral Counts',
       x = 'Average Control IP Prey Spectra (TSC)',
       y = 'Average TMEM184B IP Prey Spectra (TSC)',
       col = 'Protein\nCategory') +
  #guides(col = 'none')+
  geom_abline(slope = 2, intercept = 0, linetype = 'dashed', color = 'black', size = 1) +
  geom_text(x = 1.2, y = 3, color = 'black', label = 'FC \u2265 2.0', fontface = 'bold', size = 4.5) +
  scale_color_manual(values = c('gray48', 'dodgerblue', 'navy', 'darkgoldenrod3')) +
  theme_classic()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = 'bold', hjust = 0.5, size = 20),
        axis.text = element_text(face = 'bold', size = 12),
        axis.title = element_text(face = 'bold', size = 15),
        legend.text = element_text(face = 'bold', size = 14),
        legend.title = element_blank(),
        legend.position = c(0.75, 0.3)
  )
```

+ Macroautophagy hits

```{r Create macroautophagy plot df, include = T, message = F, warning = F, echo = T}
ALL_DF_filterd_reg_macro <- ALL_DF_filtered |>
  dplyr::mutate(poi = case_when(grepl(HumanGeneID, pattern = 'ATP6V0A(1|2)|EXOC(1|8)|ATG2A|SPTLC2|TSC2|CALCOCO2|AMBRA1') &
                                  grepl(HumanGeneID, pattern = paste0(Crapome_hits, collapse = '$|')) ~ 'Candidates in\nRegulation of Macroautophagy',
                                TRUE ~ poi)) # regulation of macroautophagy
```

### Protein Transport (zoom)

```{r IC transport zoom, include = T, message = F, warning = F, echo = T}
ggplot(data = ALL_DF_filterd_IC_protein_transport) +
  geom_point(data = subset(ALL_DF_filterd_IC_protein_transport, poi == 'Background'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 0.1) +
  geom_point(data = subset(ALL_DF_filterd_IC_protein_transport, poi == 'Candidates'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 0.5, size = 3) +
  geom_point(data = subset(ALL_DF_filterd_IC_protein_transport, poi == 'Candidates in\nIntracellular Transport'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  geom_point(data = subset(ALL_DF_filterd_IC_protein_transport, poi == 'TMEM184B'),
             aes(x = ControlAvg, y = TMEMAvg, color = poi), alpha = 1.0, size = 3) +
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) +
  labs(title = 'TMEM184B IPMS Total Spectral Counts',
       x = 'Average Control IP Prey Spectra (TSC)',
       y = 'Average TMEM184B IP Prey Spectra (TSC)',
       col = 'Protein\nCategory') +
  #guides(col = 'none')+
  geom_abline(slope = 2, intercept = 0, linetype = 'dashed', color = 'black', size = 1) +
  geom_text(x = 1.2, y = 3, color = 'black', label = 'FC \u2265 2.0', fontface = 'bold', size = 4.5) +
  scale_color_manual(values = c('gray48', 'dodgerblue', 'navy', 'darkgoldenrod3')) +
  theme_classic()+
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = 'bold', hjust = 0.5, size = 20),
        axis.text = element_text(face = 'bold', size = 12),
        axis.title = element_text(face = 'bold', size = 15),
        legend.text = element_text(face = 'bold', size = 14),
        legend.title = element_blank(),
        legend.position = c(0.78, 0.4)
  )
```

+ Intracellular protein transport hits

```{r Create IC protein tranpsort plot df, include = T, message = F, warning = F, echo = T}
ALL_DF_filterd_IC_protein_transport <- ALL_DF_filtered |>
  dplyr::mutate(poi = case_when(grepl(HumanGeneID,
                                      pattern = '^(CCDC22)$|^(GLE1)$|^(TRAPPC3)$|^(RBM15B)$|^(EHD3)$|^(COG3)$|^(AUP1)$|^(TSC2)$|^(EHD1)$|^(VPS4A)$|^(MTX1)$|^(NOP9)$|^(TANC2)$|^(NDC1)$|^(DERL1)$|^(PEX3)$|^(EHD4)$|^(SMG6)$|^(VPS50)$|^(VPS4A)$') ~ 'Candidates in\nIntracellular Transport',
                                TRUE ~ poi)) # protein transport
```

### GO Bar Plot

```{r GO Bar Plot, include = T, message = F, warning = F, echo = T, fig.width=10}
GO_INFO_by_TERM_df_sig |> 
  dplyr::filter(sig != 'NS') |> 
  dplyr::arrange(desc(fold.Enrichment)) |> 
  dplyr::group_by(GO_Type) |> 
  dplyr::slice(c(1:10)) |>
  # dplyr::mutate(GO_Term = case_when(grepl(GO_Term, pattern = 'via multivesicular') ~ gsub(GO_Term, pattern = '(^.+)(\\s)(via.+$)', replacement = '\\1\\2\n\\3'),
  #                                   TRUE ~ GO_Term)) |>
  ggplot(aes(x = -log10(FDR), y = forcats::fct_rev(forcats::fct_infreq(GO_Term, -log10(FDR))), color = 'black', fill = GO_Type, alpha = fold.Enrichment)) +
  geom_bar(color = 'black', stat = 'identity') +
  labs(title = 'TMEM184B IPMS Candidate GO Analysis',
       x = bquote(~ -log[10] ~ '(Adj.P-value)'),
         # expression(paste0("-log",[10],'(Adj.P-value)')),
       y = 'GO Term',
       fill = 'GO\nCategory',
       size = '# Genes in List',
       alpha = 'Fold\nEnrichment') +
  geom_vline(xintercept = -log10(0.05), linetype = 'dashed', color = 'black') +
  geom_text(aes(label = 'FDR\n\u2264 0.05'),
            size = 5,
            color = 'black',
            x = 3,
            y = 4,
            show.legend = FALSE) +
  geom_text(aes(label = sig,
                fontface = 'bold'),
            size = 2.5,
            color = 'black',
            angle = 90,
            vjust = 1,
            alpha = 1) +
  # geom_text(aes(label = paste0(Overlap, ' / ', GO_Term_Size),
  #               fontface = 'bold'),
  #           hjust = 0,
  #           size = 5,
  #           color = 'black',
  #           alpha = 0.7) +
  theme_bw()+
  theme(plot.title = element_text(face = 'bold', size = 13, hjust = 0.5),
        axis.title = element_text(face = 'bold', size = 12),
        axis.text = element_text(face = 'bold', size = 10, vjust = 0.5),
        axis.ticks = element_line(linetype = 'solid'),
        legend.title = element_text(face = 'bold', size = 10),
        legend.text = element_text(face = 'bold', size = 9)) +
  guides(col = 'none',
         fill = guide_legend(override.aes = list(size = 2.5, shape = 19, color = 'black', fill = c('navy', 'darkgoldenrod3', 'darkgray'))),
         alpha = guide_legend(override.aes = list(size = 2.5, shape = 19))) +
  scale_color_manual(values = c('navy', 'darkgoldenrod3', 'darkgray')) +
  scale_fill_manual(values = c('navy', 'darkgoldenrod3', 'darkgray'))
```

### GO CC Bar Plot

```{r GO CC Bar Plot, include = T, message = F, warning = F, echo = T, fig.width=10}
GO_INFO_by_TERM_df_sig |> 
  dplyr::filter(sig != "NS") |> 
  dplyr::arrange(desc(fold.Enrichment)) |> 
  dplyr::filter(GO_Type == 'CC') |> 
  dplyr::slice(c(1:10)) |>
  dplyr::mutate(GO_Term = case_when(grepl(GO_Term, pattern = 'via multivesicular') ~ gsub(GO_Term, pattern = '(^.+)(\\s)(via.+$)', replacement = '\\1\\2\n\\3'),
                                    TRUE ~ GO_Term)) |>
  ggplot(aes(x = -log10(FDR), y = forcats::fct_rev(forcats::fct_infreq(GO_Term, -log10(FDR))), color = 'navy', fill = 'navy', alpha = -log10(FDR))) +
  geom_bar(color = 'black', stat = 'identity') +
  labs(title = 'TMEM184B IPMS Candidate GO Analysis',
       x = bquote(~ -log[10] ~ '(Adj.P-value)'),
       y = 'GO Cell Component Term',
       alpha = bquote(~ -log[10] ~ '(Adj.P-value)')) +
  theme_bw()+
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title = element_text(face = 'bold', size = 12),
        axis.text = element_text(face = 'bold', size = 12, vjust = 0.5),
        axis.ticks = element_line(linetype = 'solid'),
        legend.title = element_text(face = 'bold', size = 12),
        legend.text = element_text(face = 'bold', size = 12)) +
  scale_color_manual(values = c('navy')) +
  scale_fill_manual(values = c('navy')) +
  guides(col = 'none',
         fill = 'none',
         alpha = guide_legend(override.aes = list(size = 2.5, shape = 19, color = 'black', fill = 'navy'))) +
  geom_vline(xintercept = -log10(0.05), linetype = 'dashed', color = 'black') +
  geom_text(aes(label = 'FDR\n\u2264 0.05'),
            size = 5,
            color = 'black',
            x = 3,
            y = 4,
            show.legend = FALSE) +
  geom_text(aes(label = sig,
                fontface = 'bold'),
            size = 5,
            color = 'black',
            angle = 90,
            vjust = 1,
            alpha = 1)
```

### GO BP Bar Plot

```{r GO BP Bar Plot, include = T, message = F, warning = F, echo = T, fig.width=10}
GO_INFO_by_TERM_df_sig |> 
  dplyr::filter(sig != "NS") |> 
  dplyr::arrange(desc(fold.Enrichment)) |> 
  dplyr::filter(GO_Type == 'BP') |> 
  dplyr::slice(c(1:10)) |>
  dplyr::mutate(GO_Term = case_when(grepl(GO_Term, pattern = 'via multivesicular') ~ gsub(GO_Term, pattern = '(^.+)(\\s)(via.+$)', replacement = '\\1\\2\n\\3'),
                                    TRUE ~ GO_Term)) |>
  ggplot(aes(x = -log10(FDR), y = forcats::fct_rev(forcats::fct_infreq(GO_Term, -log10(FDR))), color = 'navy', fill = 'navy', alpha = -log10(FDR))) +
  geom_bar(color = 'black', stat = 'identity') +
  labs(title = 'TMEM184B IPMS Candidate GO Analysis',
       x = bquote(~ -log[10] ~ '(Adj.P-value)'),
       y = 'GO Biological Process Term',
       alpha = bquote(~ -log[10] ~ '(Adj.P-value)')) +
  theme_bw()+
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title = element_text(face = 'bold', size = 12),
        axis.text = element_text(face = 'bold', size = 12, vjust = 0.5),
        axis.ticks = element_line(linetype = 'solid'),
        legend.text = element_text(face = 'bold', size = 12),
        legend.title = element_text(face = 'bold', size = 12)) +
  scale_color_manual(values = c('navy')) +
  scale_fill_manual(values = c('navy')) +
  guides(col = 'none',
         fill = 'none',
         alpha = guide_legend(override.aes = list(size = 2.5, shape = 19, color = 'black', fill = 'navy'))) +
  geom_vline(xintercept = -log10(0.05), linetype = 'dashed', color = 'black') +
  geom_text(aes(label = 'FDR\n\u2264 0.05'),
            size = 5,
            color = 'black',
            x = 2.25,
            y = 4,
            show.legend = FALSE) +
  geom_text(aes(label = sig,
                fontface = 'bold'),
            size = 5,
            color = 'black',
            angle = 90,
            vjust = 1,
            alpha = 1)
```

