---
title: "FIREpHly"
author: "Erik Larsen"
date: "2025-01-22"
output:
  html_document:
    toc: yes
    toc_float: 
      collapsed: yes
      numbered_sections: yes
    code_folding: hide
---
```{r knitr opts, include = F}
knitr::opts_chunk$set(dev = 'jpeg', fig.path = 'C:/Users/Erik/Desktop/Programming/R/Bio/Endo/FIREpHly_plots/')
```

### Overview {.tabset .tabset-pills .tabset-fade}

This markdown was developed to formally document the data analysis of FIRE-pHly 
data for **Dr. Martha Bhattacharya's lab** at the **University of Arizona** for
the endolysosomal paper under revision (2025-02-10).

Until an image is built, the `R version` used was **R 4.3.2** with the
packages installed below

### Set up Environment {.tabset .tabset-pills .tabset-fade}

#### Attach packages

```{r Attach packages, include = T, message = F, warning = F, echo = T}
packages <- c(#'TMEM',
               'Endo',
              'tidyverse',
              'ggplot2',
              'ggtext',
              # 'readr',
              'ggsignif',
              'emmeans',
              'broom',
              'DT'
              )
for ( package in packages ) {
  if (!require(package, character.only = T)) {
    install.packages(package)
    library(package, character.only = T)
  }
}
```

### Import FIRE-pHly Data {.tabset .tabset-pills .tabset-fade}

<span style="color:black;font-size: 18px">Directly load the `tidied_puncta_data`</span>

```{r FIREpHly data load, include = T, message = F, warning = F, echo = T}
data(tidied_puncta_data)
Puncta_data <- tidied_puncta_data
rm(tidied_puncta_data)
```

<span style="color:black;font-size: 18px">Code chunks that clean the raw data
from separate Excel sheets into the data object, `tidied_puncta_data`, have been
included in `"Wrangle"` sections below</span>

#### Wrangle the WT Data

```{r WT data processing, eval = F, include = T, message = F, warning = F, echo = T}
data(FIREpHly_WT)
```

<span style="color:black;font-size: 16px">Re-arrange the data to make it analyzable</span>

```{r Extract WT cell level data, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_WT_cell_sum <- FIREpHly_WT |>
  dplyr::slice(c(3,4, 39,40, 74,75, 100,101)) |>
  dplyr::filter(!grepl(`...1`, pattern = 'From')) |>
  dplyr::select(where(~!all(is.na(.))))

col_names <- FIRE_pHly_WT_cell_sum |>
  dplyr::slice(1) |>
  unlist() |> as.character() %>%
  paste0('_', c(rep(1, 7), rep(2, 7), rep(3, 7), rep(4, 7)))

colnames(FIRE_pHly_WT_cell_sum) <- col_names
```

```{r ReArrange WT cell level data, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_WT_cell_sum <- FIRE_pHly_WT_cell_sum |>
  dplyr::filter(!grepl(Filename_1, pattern = 'Filename')) |>
  tidyr::pivot_longer(
    cols = tidyr::everything(),
    names_to = c('colname', 'iter'),
    names_sep = '_',
    values_to = 'value'
    ) |>
  dplyr::mutate(count = NA) |>
  dplyr::mutate(count = dplyr::case_when(colname == 'Filename' ~ 1,
                                  TRUE ~ NA_real_)) |>
  dplyr::group_by(colname) |>
  dplyr::mutate(count = cumsum(count)) |>
  dplyr::ungroup() |>
  tidyr::fill(count, .direction = 'down') |>
  tidyr::pivot_wider(
    id_cols = count, names_from = colname, values_from = value) |>
  dplyr::filter(!is.na(Filename)) |>
  dplyr::mutate(count = dplyr::row_number()) |>
  dplyr::rename(cell_num = count) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\[.*]$', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '``|\\.', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '_Mean_Int', replacement = '')) %>%
  dplyr::rename_with(
    ~dplyr::if_else(
      grepl(.x, pattern = '_Puncta'),
      gsub(paste0('Puncta_Mean_', .x, '_Intensity'),
           pattern = '_Puncta', replacement = ''),
      .x)
    ) |>
  dplyr::rename(Puncta_Mean_GreenRedRatio = `Green/Red_Ratio`)
```

```{r Extract WT puncta level data, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_WT_puncta <- FIREpHly_WT |> 
  dplyr::slice(c(6:36, 42:71, 77:97, 103:129)) %>%
  dplyr::select(where(~!all(is.na(.))))

col_names <- FIRE_pHly_WT_puncta |>
  dplyr::slice(1) |> unlist() |> as.character() %>%
  paste0('_', c(rep(1, 6), rep(2,6), rep(3,6), rep(4,6)))

colnames(FIRE_pHly_WT_puncta) <- col_names
```

```{r ReARR WT Cells 1 through 4, eval = F, include = T, message = F, warning = F, echo = T}
    ## break up into df of the 4 cells across the top
FIRE_pHly_WT_puncta_1_4 <- FIRE_pHly_WT_puncta |>
  dplyr::slice(-1) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+1$', replacement = 'Puncta Area_1')
    ) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+2$', replacement = 'Puncta Area_2')
    ) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+3$', replacement = 'Puncta Area_3')
    ) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+4$', replacement = 'Puncta Area_4')
    ) |>
  dplyr::mutate(
    dplyr::across(dplyr::contains('Puncta Area'), ~ as.numeric(.x))
    ) |>
  dplyr::rename_with(
    ~gsub(.x,
          pattern = 'GREEN/RED',
          replacement = 'Green/Red Ratio per puncta_3')
    ) |>
  dplyr::rename_with(
    ~gsub(.x,
          pattern = 'Gree/Red Ratio',
          replacement= 'Green/Red Ratio')
    ) |>
  dplyr::mutate(
    dummy_1 = dplyr::lag(`Puncta Area_1`) - `Puncta Area_1`, .after = 3
    ) |>
  dplyr::mutate(
    dummy_1 = dplyr::case_when(is.na(dummy_1) &
                                 dplyr::lead(!is.na(dummy_1)) ~ 0,
                               TRUE ~ dummy_1)
    ) |>
  
  dplyr::mutate(
    dummy_2 = dplyr::lag(`Puncta Area_2`) - `Puncta Area_2`, .after = 10
    ) |>
  dplyr::mutate(
    dummy_2 = dplyr::case_when(is.na(dummy_2) &
                                 dplyr::lead(!is.na(dummy_2)) ~ 0,
                               TRUE ~ dummy_2)
    ) |>
  
  dplyr::mutate(
    dummy_3 = dplyr::lag(`Puncta Area_3`) - `Puncta Area_3`, .after = 18
    ) |>
  dplyr::mutate(
    dummy_3 = dplyr::case_when(is.na(dummy_3) &
                                 dplyr::lead(!is.na(dummy_3)) ~ 0,
                               TRUE ~ dummy_3)
    ) |>
  
  dplyr::mutate(
    dummy_4 = dplyr::lag(`Puncta Area_4`) - `Puncta Area_4`, .after = 24
    ) |>
  dplyr::mutate(
    dummy_4 = dplyr::case_when(is.na(dummy_4) &
                                 dplyr::lead(!is.na(dummy_4)) ~ 0,
                               TRUE ~ dummy_4)
    ) |>
  
  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(is.na(dummy_1) ~ NA_real_,
                                       TRUE ~ `Puncta Area_1`)
    ) |>
  
  dplyr::mutate(
    `Puncta Area_2` = dplyr::case_when(is.na(dummy_2) ~ NA_real_,
                                       TRUE ~ `Puncta Area_2`)
    ) |>
  
  dplyr::mutate(
    `Puncta Area_3` = dplyr::case_when(is.na(dummy_3) ~ NA_real_,
                                       TRUE ~ `Puncta Area_3`)
    ) |>
  
  dplyr::mutate(
    `Puncta Area_4` = dplyr::case_when(is.na(dummy_4) ~ NA_real_,
                                       TRUE ~ `Puncta Area_4`)
    ) |>

  dplyr::mutate(
    `Puncta Circularity_1` = dplyr::case_when(is.na(dummy_1) &
                                                is.na(`Puncta ID_1`) ~ NA,
                                              TRUE ~ `Puncta Circularity_1`)
    ) |>
  
  dplyr::mutate(
    `Puncta Circularity_2` = dplyr::case_when(is.na(dummy_2) &
                                                is.na(`Puncta ID_2`) ~ NA,
                                              TRUE ~ `Puncta Circularity_2`)
    ) |>
  
  dplyr::mutate(
    `Puncta Circularity_3` = dplyr::case_when(is.na(dummy_3) &
                                                is.na(`Puncta ID_3`) ~ NA,
                                              TRUE ~ `Puncta Circularity_3`)
    ) |>
  
  dplyr::mutate(
    `Puncta Circularity_4` = dplyr::case_when(is.na(dummy_4) &
                                                is.na(`Puncta ID_4`) ~ NA,
                                              TRUE ~ `Puncta Circularity_4`)
    ) |>
  
  dplyr::select(-dplyr::contains('dummy')) |>

  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(
      
      `Puncta Circularity_1` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_1`))
    ) |>
  
  dplyr::mutate(
    `Puncta Area_2` = dplyr::case_when(
      
      `Puncta Circularity_2` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_2`))
    ) |>
  
  dplyr::mutate(`Puncta Area_3` = dplyr::case_when(
    
    `Puncta Circularity_3` == "Puncta Circularity" ~ 'Puncta Area',
    TRUE ~ as.character(`Puncta Area_3`))
    ) |>
  
  dplyr::mutate(
    `Puncta Area_4` = dplyr::case_when(
      
      `Puncta Circularity_4` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_4`))
    ) |>
  
  dplyr::slice(1:30) |>
  dplyr::mutate(
    `Puncta ID_3` = dplyr::case_when(
      
      grepl(`Puncta ID_3`, pattern = 'Avg') ~ NA,
      TRUE ~ `Puncta ID_3`)
    ) |>
  
  tidyr::pivot_longer(
    cols = tidyr::everything(),
    names_to = c('cell', 'cell_num'),
    names_sep = '_', values_to = 'values') |>
  
  dplyr::mutate(
    cell_num = gsub(cell_num, pattern = ' ratio', replacement = '')
    ) |>
  dplyr::mutate(
    cell = gsub(cell, pattern = ' per puncta', replacement = '')
    ) |>
  dplyr::mutate(
    puncta_num = dplyr::case_when(!grepl(values, pattern = '\\.') ~ values,
                                  TRUE ~ NA)
    ) |>
  dplyr::mutate(
    overall_puncta_num = dplyr::case_when(!is.na(puncta_num) ~ 1,
                                          TRUE ~ NA_real_)
    ) |>
  dplyr::group_by(overall_puncta_num) |>
  dplyr::mutate(overall_puncta_num = cumsum(overall_puncta_num)) |>
  dplyr::ungroup() |>
  tidyr::fill(overall_puncta_num, .direction = 'down') |>
  dplyr::filter(
    !is.na(values)

  ) |>
  tidyr::pivot_wider(
    id_cols = c('cell_num', 'puncta_num' ,'overall_puncta_num'),
    names_from = 'cell',
    values_from = 'values'
    ) |>
  tidyr::fill(`Puncta ID`, .direction = 'down') |>
  dplyr::filter(!is.na(`Puncta Area`)) %>%
  dplyr::select(where(~!all(is.na(.)))) |>
  dplyr::relocate(`Puncta ID`, .after = 1) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\/', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '``', replacement = '')) %>%
  # dplyr::mutate(across(c(4:8), ~as.numeric(.x))) |>
  dplyr::select(-overall_puncta_num)
```

```{r ReARR WT Cells 5 and 6, eval = F, include = T, message = F, warning = F, echo = T}
    ## break up into df of the next two vertically oriented cells
FIRE_pHly_WT_puncta_5_6 <- FIRE_pHly_WT_puncta |>
  dplyr::slice(-1) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+1$', replacement = 'Puncta Area_1')
    ) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+2$', replacement = 'Puncta Area_2')
    ) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+3$', replacement = 'Puncta Area_3')
    ) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+4$', replacement = 'Puncta Area_4')
    ) |>
  dplyr::mutate(
    dplyr::across(dplyr::contains('Puncta Area'), ~ as.numeric(.x))
    ) |>

  dplyr::mutate(
    dummy_1 = dplyr::lag(`Puncta Area_1`) - `Puncta Area_1`, .after = 3
    ) |>
  dplyr::mutate(dummy_1 = dplyr::case_when(is.na(dummy_1) &
                                             dplyr::lead(!is.na(dummy_1)) ~ 0,
                                           TRUE ~ dummy_1)) |>
  dplyr::mutate(
    dummy_2 = dplyr::lag(`Puncta Area_2`) - `Puncta Area_2`, .after = 10
    ) |>
  dplyr::mutate(dummy_2 = dplyr::case_when(is.na(dummy_2) &
                                             dplyr::lead(!is.na(dummy_2)) ~ 0,
                                           TRUE ~ dummy_2)) |>
  dplyr::mutate(
    dummy_3 = dplyr::lag(`Puncta Area_3`) - `Puncta Area_3`, .after = 18
    ) |>
  dplyr::mutate(dummy_3 = dplyr::case_when(is.na(dummy_3) &
                                             dplyr::lead(!is.na(dummy_3)) ~ 0,
                                           TRUE ~ dummy_3)) |>
  dplyr::mutate(
    dummy_4 = dplyr::lag(`Puncta Area_4`) - `Puncta Area_4`, .after = 24
    ) |>
  dplyr::mutate(dummy_4 = dplyr::case_when(is.na(dummy_4) &
                                             dplyr::lead(!is.na(dummy_4)) ~ 0,
                                           TRUE ~ dummy_4)) |>
  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(is.na(dummy_1) ~ NA_real_,
                                            TRUE ~ `Puncta Area_1`)) |>
  dplyr::mutate(`Puncta Area_2` = dplyr::case_when(is.na(dummy_2) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_2`)
                ) |>
  dplyr::mutate(`Puncta Area_3` = dplyr::case_when(is.na(dummy_3) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_3`)
                ) |>
  dplyr::mutate(`Puncta Area_4` = dplyr::case_when(is.na(dummy_4) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_4`)
                ) |>
  dplyr::mutate(
    `Puncta Circularity_1` = dplyr::case_when(is.na(dummy_1) &
                                                is.na(`Puncta ID_1`) ~ NA,
                                              TRUE ~ `Puncta Circularity_1`)
    ) |>
  dplyr::mutate(
    `Puncta Circularity_2` = dplyr::case_when(is.na(dummy_2) &
                                                is.na(`Puncta ID_2`) ~ NA,
                                              TRUE ~ `Puncta Circularity_2`)
    ) |>
  dplyr::mutate(
    `Puncta Circularity_3` = dplyr::case_when(is.na(dummy_3) &
                                                is.na(`Puncta ID_3`) ~ NA,
                                              TRUE ~ `Puncta Circularity_3`)
    ) |>
  dplyr::mutate(
    `Puncta Circularity_4` = dplyr::case_when(is.na(dummy_4) &
                                                is.na(`Puncta ID_4`) ~ NA,
                                              TRUE ~ `Puncta Circularity_4`)
    ) |>
  dplyr::select(-contains('dummy')) |>

  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(
      
      `Puncta Circularity_1` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_1`))
    
    ) |>
  dplyr::mutate(
    `Puncta Area_2` = dplyr::case_when(
      
      `Puncta Circularity_2` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_2`))
    
    ) |>
  dplyr::mutate(
    `Puncta Area_3` = dplyr::case_when(
      
      `Puncta Circularity_3` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_3`))
    
    ) |>
  dplyr::mutate(
    `Puncta Area_4` = dplyr::case_when(
      
      `Puncta Circularity_4` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_4`))
    
    ) |>
  dplyr::slice(31:75) %>%
  dplyr::select(where(~!all(is.na(.)))) %>%
  dplyr::rename_with(
    ~gsub(.x,
          pattern = 'Gree/Red Ratio per puncta_1',
          replacement = 'GreenRed_Ratio')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '_1', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '``', replacement = '')) %>%
  dplyr::slice(-c(1,31)) |>
  dplyr::mutate(cell_num = dplyr::case_when(dplyr::row_number() <= 23 ~ "5",
                                            dplyr::row_number() >= 30 ~ "6",
                                            TRUE ~ NA), .before = Puncta_ID
                ) |>
  dplyr::filter(!is.na(cell_num))
```

```{r ReARR WT Cells 7 through 10, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_WT_puncta_7_10 <- FIRE_pHly_WT_puncta |>
  dplyr::slice(-1) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+1$', replacement = 'Puncta Area_1')) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+2$', replacement = 'Puncta Area_2')) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+3$', replacement = 'Puncta Area_3')) |>
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+4$', replacement = 'Puncta Area_4')) |>
  dplyr::mutate(
    dplyr::across(dplyr::contains('Puncta Area'), ~ as.numeric(.x))) |>
  dplyr::rename_with(
    ~gsub(.x,
          pattern = 'GREEN/RED',
          replacement = 'Green/Red Ratio per puncta_3')) |>
  dplyr::rename_with(
    ~gsub(.x,
          pattern = 'Gree/Red Ratio',
          replacement= 'Green/Red Ratio')) |>
  
  dplyr::mutate(
    dummy_1 = dplyr::lag(`Puncta Area_1`) - `Puncta Area_1`, .after = 3) |>
  dplyr::mutate(
    dummy_1 = dplyr::case_when(is.na(dummy_1) &
                                 dplyr::lead(!is.na(dummy_1)) ~ 0,
                               TRUE ~ dummy_1)) |>
  
  dplyr::mutate(
    dummy_2 = dplyr::lag(`Puncta Area_2`) - `Puncta Area_2`, .after = 10) |>
  dplyr::mutate(
    dummy_2 = dplyr::case_when(is.na(dummy_2) &
                                 dplyr::lead(!is.na(dummy_2)) ~ 0,
                               TRUE ~ dummy_2)) |>
  
  dplyr::mutate(
    dummy_3 = dplyr::lag(`Puncta Area_3`) - `Puncta Area_3`, .after = 18) |>
  dplyr::mutate(
    dummy_3 = dplyr::case_when(is.na(dummy_3) &
                                 dplyr::lead(!is.na(dummy_3)) ~ 0,
                               TRUE ~ dummy_3)) |>
  
  dplyr::mutate(
    dummy_4 = dplyr::lag(`Puncta Area_4`) - `Puncta Area_4`, .after = 24) |>
  dplyr::mutate(
    dummy_4 = dplyr::case_when(is.na(dummy_4) &
                                 dplyr::lead(!is.na(dummy_4)) ~ 0,
                               TRUE ~ dummy_4)) |>
  
  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(is.na(dummy_1) ~ NA_real_,
                                       TRUE ~ `Puncta Area_1`)) |>
  
  dplyr::mutate(
    `Puncta Area_2` = dplyr::case_when(is.na(dummy_2) ~ NA_real_,
                                       TRUE ~ `Puncta Area_2`)) |>
  
  dplyr::mutate(
    `Puncta Area_3` = dplyr::case_when(is.na(dummy_3) ~ NA_real_,
                                       TRUE ~ `Puncta Area_3`)) |>
  
  dplyr::mutate(
    `Puncta Area_4` = dplyr::case_when(is.na(dummy_4) ~ NA_real_,
                                       TRUE ~ `Puncta Area_4`)) |>

  dplyr::mutate(
    `Puncta Circularity_1` = dplyr::case_when(is.na(dummy_1) &
                                                is.na(`Puncta ID_1`) ~ NA,
                                              TRUE ~ `Puncta Circularity_1`)
    ) |>
  dplyr::mutate(
    `Puncta Circularity_2` = dplyr::case_when(is.na(dummy_2) &
                                                is.na(`Puncta ID_2`) ~ NA,
                                              TRUE ~ `Puncta Circularity_2`)
    ) |>
  dplyr::mutate(
    `Puncta Circularity_3` = dplyr::case_when(is.na(dummy_3) &
                                                is.na(`Puncta ID_3`) ~ NA,
                                              TRUE ~ `Puncta Circularity_3`)
    ) |>
  dplyr::mutate(
    `Puncta Circularity_4` = dplyr::case_when(is.na(dummy_4) &
                                                is.na(`Puncta ID_4`) ~ NA,
                                              TRUE ~ `Puncta Circularity_4`)
    ) |>
  dplyr::select(-contains('dummy')) |>

  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(
      `Puncta Circularity_1` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_1`))) |>
  
  dplyr::mutate(
    `Puncta Area_2` = dplyr::case_when(
      `Puncta Circularity_2` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_2`))) |>
  
  dplyr::mutate(
    `Puncta Area_3` = dplyr::case_when(
      `Puncta Circularity_3` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_3`))) |>
  
  dplyr::mutate(
    `Puncta Area_4` = dplyr::case_when(
      `Puncta Circularity_4` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_4`))) |>
  
  dplyr::mutate(
    `Puncta ID_3` = dplyr::case_when(grepl(`Puncta ID_3`, pattern = 'Avg') ~ NA,
                                     TRUE ~ `Puncta ID_3`)) |>
  dplyr::slice(c(83:102)) |>
  tidyr::pivot_longer(
    cols = tidyr::everything(),
    names_to = c('cell', 'cell_num'),
    names_sep = '_',
    values_to = 'values') |>
  dplyr::mutate(
    cell_num = gsub(cell_num, pattern = ' ratio', replacement = '')) |>
  dplyr::mutate(
    cell = gsub(cell, pattern = ' per puncta', replacement = '')) |>
  dplyr::mutate(
    puncta_num = dplyr::case_when(!grepl(values, pattern = '\\.') ~ values,
                                  TRUE ~ NA)) |>
  dplyr::mutate(
    overall_puncta_num = dplyr::case_when(!is.na(puncta_num) ~ 1,
                                          TRUE ~ NA_real_)) |>
  dplyr::group_by(overall_puncta_num) |>
  dplyr::mutate(overall_puncta_num = cumsum(overall_puncta_num)) |>
  dplyr::ungroup() |>
  tidyr::fill(overall_puncta_num, .direction = 'down') |>
  dplyr::filter(
    !is.na(values)
  ) |>
  tidyr::pivot_wider(
    id_cols = c('cell_num', 'puncta_num' ,'overall_puncta_num'),
    names_from = 'cell',
    values_from = 'values') |>
  tidyr::fill(`Puncta ID`, .direction = 'down') |>
  dplyr::filter(!is.na(`Puncta Area`)) %>%
  dplyr::select(where(~!all(is.na(.)))) |>
  dplyr::relocate(`Puncta ID`, .after = 1) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\/', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '``', replacement = '')) %>%
  # dplyr::mutate(across(c(4:8), ~as.numeric(.x))) |>
  dplyr::mutate(overall_puncta_num = as.character(overall_puncta_num)) |>
  dplyr::mutate(cell_num = dplyr::case_when(cell_num == "1" ~ "7",
                                     cell_num == "2" ~ "8",
                                     cell_num == "3" ~ "9",
                                     cell_num == "4" ~ "10")) |>
  dplyr::select(-overall_puncta_num)
```

```{r Join WT Cells, eval = F, include = T, warning = F, message = F, echo = T}
    ## join the WT puncta across 10 cells
FIRE_pHly_WT_puncta_tot <- FIRE_pHly_WT_puncta_1_4 |>
  dplyr::full_join(FIRE_pHly_WT_puncta_5_6) |>
  dplyr::full_join(FIRE_pHly_WT_puncta_7_10)

WT_sum <- FIRE_pHly_WT_puncta_tot |>
  dplyr::group_by(cell_num) |>
  dplyr::mutate(n_puncta = dplyr::n()) %>%
  dplyr::mutate(dplyr::across(c(3:7), ~as.numeric(.x, digits = 22))) |>
  dplyr::summarize(
    
    n_puncta = dplyr::n(),
    tot_puncta_area = sum(Puncta_Area)#,
    # cell_mean_green_mean_intensity = mean(Green_Mean_Intensity),
    # cell_mean_red_mean_intensity = mean(Red_Mean_Intensity),
    # cell_mean_green_red_ratio = mean(GreenRed_Ratio)
    
    ) |>
  dplyr::full_join(FIRE_pHly_WT_cell_sum |>
                     dplyr::mutate(cell_num = as.character(cell_num))) |>
  # error in total puncta on cell sum, remove
  dplyr::select(-Puncta_Count) |>
  dplyr::mutate(
    # n_puncta_per_cell_area = n_puncta/(as.numeric(Cell_Body_Area)/100),
    puncta_cell_body_ratio = tot_puncta_area/(as.double(Cell_Body_Area)),
    sum_puncta_area = sum(tot_puncta_area),
    sum_Cell_Body_area = sum(as.double(Cell_Body_Area)))
```

#### Wrangle the MUT Data

```{r MUT data processing, eval = F, include = T, message = F, warning = F, echo = T}
data(FIREpHly_Mut)
```

<span style="color:black;font-size: 16px">Re-arrange the data to make it analyzable</span>

```{r Extract MUT cell level data, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_Mut_cell_sum <- FIREpHly_Mut |>
  dplyr::slice(c(2,3, 50,51, 101,102, 152,153)) %>%
  dplyr::select(where(~!all(is.na(.))))

col_names <- FIRE_pHly_Mut_cell_sum |>
  dplyr::slice(1) |> unlist() |> as.character() %>%
  paste0('_', c(rep(1, 7), rep(2, 7), rep(3, 7), rep(4, 7), rep(5, 7)))

colnames(FIRE_pHly_Mut_cell_sum) <- col_names
```

```{r ReArrange MUT cell level data, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_Mut_cell_sum <- FIRE_pHly_Mut_cell_sum |>
  dplyr::filter(!grepl(Filename_1, pattern = 'Filename')) |>
  tidyr::pivot_longer(
    cols = tidyr::everything(),
    names_to = c('colname', 'iter'),
    names_sep = '_',
    values_to = 'value') |>
  dplyr::mutate(count = NA) |>
  dplyr::mutate(count = dplyr::case_when(colname == 'Filename' ~ 1,
                                         TRUE ~ NA_real_)) |>
  dplyr::group_by(colname) |>
  dplyr::mutate(count = cumsum(count)) |>
  dplyr::ungroup() |>
  tidyr::fill(count, .direction = 'down') |>
  tidyr::pivot_wider(
    id_cols = count, names_from = colname, values_from = value) |>
  dplyr::filter(!is.na(Filename)) |>
  dplyr::mutate(count = dplyr::row_number()) |>
  dplyr::rename(cell_num = count) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = '\\[.*]$', replacement = '')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = '``|\\.', replacement = '')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = '_Mean_Int', replacement = '')) %>%
  dplyr::rename_with(
    ~dplyr::if_else(grepl(.x, pattern = '_Puncta'),
                    gsub(paste0('Puncta_Mean_', .x, '_Intensity'),
                         pattern = '_Puncta',
                         replacement = ''),
                    .x)) |>
  dplyr::rename(Puncta_Mean_GreenRedRatio = `Green/Red_Ratio`)
```

```{r Extract MUT puncta level data, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_Mut_puncta <- FIREpHly_Mut |>
  dplyr::slice(c(5:48, 50:90, 101:142, 152:178)) |>
  dplyr::slice(-c(45,46, 86,87, 128,129)) %>%
  dplyr::select(where(~!all(is.na(.)))) |> dplyr::select(-1)

col_names <- FIRE_pHly_Mut_puncta |>
  dplyr::slice(1) |> unlist() |> as.character() %>%
  paste0('_', c(rep(1, 6), rep(2,6), rep(3,6), rep(4,6), rep(5,6)))

colnames(FIRE_pHly_Mut_puncta) <- col_names
```

```{r ReARR MUT cells 1 through 5, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_Mut_puncta_1_5 <- FIRE_pHly_Mut_puncta |>
  dplyr::slice(-1) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+1$', replacement = 'Puncta Area_1')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+2$', replacement = 'Puncta Area_2')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+3$', replacement = 'Puncta Area_3')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+4$', replacement = 'Puncta Area_4')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+5$', replacement = 'Puncta Area_5')) %>%
  dplyr::mutate(dplyr::across(dplyr::contains('Puncta Area'), ~ as.numeric(.x))) %>%
  dplyr::mutate(
    dplyr::across(c(dplyr::contains('Puncta ID')), ~ 
                    dplyr::case_when(grepl(., pattern = 'Avg.') ~ NA,
                                     TRUE ~ .))) |>
  dplyr::mutate(
    dplyr::across(c(dplyr::contains("Circularity")), ~
                    dplyr::case_when(grepl(., pattern = '[:alpha:]') ~ NA,
                                     TRUE ~ .))) |>
  dplyr::slice(1:35) |>

  dplyr::mutate(dummy_1 = dplyr::lag(`Puncta Area_1`) - `Puncta Area_1`,
                .after = 3) |>
  dplyr::mutate(dummy_1 = dplyr::case_when(is.na(dummy_1) &
                                             dplyr::lead(!is.na(dummy_1)) ~ 0,
                                           TRUE ~ dummy_1)) |>
  dplyr::mutate(dummy_2 = dplyr::lag(`Puncta Area_2`) - `Puncta Area_2`,
                .after = 10) |>
  dplyr::mutate(dummy_2 = dplyr::case_when(is.na(dummy_2) &
                                             dplyr::lead(!is.na(dummy_2)) ~ 0,
                                           TRUE ~ dummy_2)) |>
  dplyr::mutate(dummy_3 = dplyr::lag(`Puncta Area_3`) - `Puncta Area_3`,
                .after = 18) |>
  dplyr::mutate(dummy_3 = dplyr::case_when(is.na(dummy_3) &
                                             dplyr::lead(!is.na(dummy_3)) ~ 0,
                                           TRUE ~ dummy_3)) |>
  dplyr::mutate(dummy_4 = dplyr::lag(`Puncta Area_4`) - `Puncta Area_4`,
                .after = 24) |>
  dplyr::mutate(dummy_4 = dplyr::case_when(is.na(dummy_4) &
                                             dplyr::lead(!is.na(dummy_4)) ~ 0,
                                           TRUE ~ dummy_4)) |>
  dplyr::mutate(dummy_5 = dplyr::lag(`Puncta Area_5`) - `Puncta Area_5`,
                .after = 24) |>
  dplyr::mutate(dummy_5 = dplyr::case_when(is.na(dummy_5) &
                                             dplyr::lead(!is.na(dummy_5)) ~ 0,
                                           TRUE ~ dummy_5)) |>
  dplyr::mutate(`Puncta Area_1` = dplyr::case_when(is.na(dummy_1) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_1`)) |>
  dplyr::mutate(`Puncta Area_2` = dplyr::case_when(is.na(dummy_2) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_2`)) |>
  dplyr::mutate(`Puncta Area_3` = dplyr::case_when(is.na(dummy_3) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_3`)) |>
  dplyr::mutate(`Puncta Area_4` = dplyr::case_when(is.na(dummy_4) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_4`)) |>
  dplyr::mutate(`Puncta Area_5` = dplyr::case_when(is.na(dummy_5) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_5`)) |>

  dplyr::mutate(
    `Puncta Circularity_1` = dplyr::case_when(is.na(dummy_1) &
                                                is.na(`Puncta ID_1`) ~ NA,
                                              TRUE ~ `Puncta Circularity_1`)) |>
  dplyr::mutate(
    `Puncta Circularity_2` = dplyr::case_when(is.na(dummy_2) &
                                                is.na(`Puncta ID_2`) ~ NA,
                                              TRUE ~ `Puncta Circularity_2`)) |>
  dplyr::mutate(
    `Puncta Circularity_3` = dplyr::case_when(is.na(dummy_3) &
                                                is.na(`Puncta ID_3`) ~ NA,
                                              TRUE ~ `Puncta Circularity_3`)) |>
  dplyr::mutate(
    `Puncta Circularity_4` = dplyr::case_when(is.na(dummy_4) &
                                                is.na(`Puncta ID_4`) ~ NA,
                                              TRUE ~ `Puncta Circularity_4`)) |>
  dplyr::mutate(
    `Puncta Circularity_5` = dplyr::case_when(is.na(dummy_5) &
                                                is.na(`Puncta ID_5`) ~ NA,
                                              TRUE ~ `Puncta Circularity_5`)) |>
  dplyr::select(-dplyr::contains('dummy')) |>

  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(
      `Puncta Circularity_1` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_1`))) |>
  dplyr::mutate(
    `Puncta Area_2` = dplyr::case_when(
      `Puncta Circularity_2` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_2`))) |>
  dplyr::mutate(
    `Puncta Area_3` = dplyr::case_when(
      `Puncta Circularity_3` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_3`))) |>
  dplyr::mutate(
    `Puncta Area_4` = dplyr::case_when(
      `Puncta Circularity_4` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_4`))) |>
  dplyr::mutate(
    `Puncta Area_5` = dplyr::case_when(
      `Puncta Circularity_5` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_5`))) |>

  tidyr::pivot_longer(
    cols = tidyr::everything(),
    names_to = c('cell', 'cell_num'),
    names_sep = '_',
    values_to = 'values') |>
  dplyr::mutate(
    cell_num = gsub(cell_num, pattern = ' ratio', replacement = '')) |>
  dplyr::mutate(
    cell = gsub(cell, pattern = ' per puncta', replacement = '')) |>
  dplyr::mutate(
    puncta_num = dplyr::case_when(!grepl(values, pattern = '\\.') ~ values,
                                  TRUE ~ NA)) |>
  dplyr::mutate(
    overall_puncta_num = dplyr::case_when(!is.na(puncta_num) ~ 1,
                                          TRUE ~ NA_real_)) |>
  dplyr::group_by(overall_puncta_num) |>
  dplyr::mutate(overall_puncta_num = cumsum(overall_puncta_num)) |>
  dplyr::ungroup() |>
  tidyr::fill(overall_puncta_num, .direction = 'down') |>
  dplyr::filter(
    !is.na(values)
  ) |>
  tidyr::pivot_wider(
    id_cols = c('cell_num', 'puncta_num' ,'overall_puncta_num'), 
    names_from = 'cell', 
    values_from = 'values') |>
  tidyr::fill(`Puncta ID`, .direction = 'down') |>
  dplyr::filter(!is.na(`Puncta Area`)) %>%
  dplyr::select(where(~!all(is.na(.)))) |>
  dplyr::relocate(`Puncta ID`, .after = 1) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\/', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '``', replacement = '')) |>
  dplyr::rename(GreenRed_Ratio = GREENRED_ratio) |>
  # dplyr::mutate(dplyr::across(c(4:8), ~as.numeric(.x))) |>
  dplyr::select(-overall_puncta_num)
```

```{r ReARR MUT cells 6 through 8, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_Mut_puncta_6_8 <- FIRE_pHly_Mut_puncta |>
  dplyr::slice(-1) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+1$', replacement = 'Puncta Area_1')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+2$', replacement = 'Puncta Area_2')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+3$', replacement = 'Puncta Area_3')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+4$', replacement = 'Puncta Area_4')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+5$', replacement = 'Puncta Area_5')) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains('Puncta Area'), ~ as.numeric(.x))) %>%
  dplyr::mutate(
    dplyr::across(c(dplyr::contains('Puncta ID')), ~ 
                    dplyr::case_when(grepl(., pattern = 'Avg.') ~ NA,
                                     TRUE ~ .))) %>%
  dplyr::mutate(
    dplyr::across(c(dplyr::contains("Circularity")), ~
                    dplyr::case_when(grepl(., pattern = '[:alpha:]') ~ NA,
                                     TRUE ~ .))) |>
  dplyr::slice(c(46:82)) %>%
  dplyr::mutate(dplyr::across(c(dplyr::contains('_2')), ~dplyr::lead(.))) |>
  dplyr::mutate(dummy_1 = dplyr::lag(`Puncta Area_1`) - `Puncta Area_1`,
                .after = 3) |>
  dplyr::mutate(dummy_1 = dplyr::case_when(is.na(dummy_1) &
                                             dplyr::lead(!is.na(dummy_1)) ~ 0,
                                           TRUE ~ dummy_1)) |>
  dplyr::mutate(dummy_2 = dplyr::lag(`Puncta Area_2`) - `Puncta Area_2`,
                .after = 10) |>
  dplyr::mutate(dummy_2 = dplyr::case_when(is.na(dummy_2) &
                                             dplyr::lead(!is.na(dummy_2)) ~ 0,
                                           TRUE ~ dummy_2)) |>
  dplyr::mutate(dummy_3 = dplyr::lag(`Puncta Area_3`) - `Puncta Area_3`,
                .after = 18) |>
  dplyr::mutate(dummy_3 = dplyr::case_when(is.na(dummy_3) &
                                             dplyr::lead(!is.na(dummy_3)) ~ 0,
                                           TRUE ~ dummy_3)) |>

  dplyr::mutate(`Puncta Area_1` = dplyr::case_when(is.na(dummy_1) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_1`)) |>
  dplyr::mutate(`Puncta Area_2` = dplyr::case_when(is.na(dummy_2) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_2`)) |>
  dplyr::mutate(`Puncta Area_3` = dplyr::case_when(is.na(dummy_3) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_3`)) %>%
  dplyr::mutate(
    dplyr::across(c(dplyr::contains('Area_')), ~as.character(.x))) |>
  dplyr::select(-dplyr::contains('dummy')) |>
  tidyr::pivot_longer(
    cols = tidyr::everything(),
    names_to = c('cell', 'cell_num'),
    names_sep = '_',
    values_to = 'values') |>
  dplyr::mutate(
    cell_num = gsub(cell_num, pattern = ' ratio', replacement = '')) |>
  dplyr::mutate(
    cell = gsub(cell, pattern = ' per puncta', replacement = '')) |>
  dplyr::mutate(
    puncta_num = dplyr::case_when(!grepl(values, pattern = '\\.') ~ values,
                                  TRUE ~ NA)) |>
  dplyr::mutate(
    overall_puncta_num = dplyr::case_when(!is.na(puncta_num) ~ 1,
                                          TRUE ~ NA_real_)) |>
  dplyr::group_by(overall_puncta_num) |>
  dplyr::mutate(overall_puncta_num = cumsum(overall_puncta_num)) |>
  dplyr::ungroup() |>
  tidyr::fill(overall_puncta_num, .direction = 'down') |>
  dplyr::filter(!is.na(values)) |>
  tidyr::pivot_wider(
    id_cols = c('cell_num', 'puncta_num' ,'overall_puncta_num'),
    names_from = 'cell',
    values_from = 'values') |>
  tidyr::fill(`Puncta ID`, .direction = 'down') |>
  dplyr::filter(!is.na(`Puncta Area`)) %>%
  dplyr::select(where(~!all(is.na(.)))) |>
  dplyr::relocate(`Puncta ID`, .after = 1) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\/', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '``', replacement = '')) %>%
  dplyr::rename(GreenRed_Ratio = GREENRED_ratio) |>
  # dplyr::mutate(dplyr::across(c(4:8), ~as.numeric(.x))) |>
  dplyr::select(-overall_puncta_num) |>
  dplyr::mutate(
    cell_num = dplyr::case_when(cell_num == 1 ~ "6",
                                cell_num == 2 ~ "7",
                                cell_num == 3 ~ "8"))
```

```{r ReARR MUT cells 9 through 11, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_Mut_puncta_9_11 <- FIRE_pHly_Mut_puncta |>
  dplyr::slice(-1) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+1$', replacement = 'Puncta Area_1')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+2$', replacement = 'Puncta Area_2')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+3$', replacement = 'Puncta Area_3')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+4$', replacement = 'Puncta Area_4')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+5$', replacement = 'Puncta Area_5')) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains('Puncta Area'), ~ as.numeric(.x))) |>
  dplyr::slice(c(84:122)) |>
  dplyr::slice(-1) %>%
  dplyr::mutate(
    dplyr::across(c(dplyr::contains('Puncta ID')), ~
                    dplyr::case_when(grepl(., pattern = 'Avg.') ~ NA,
                                     TRUE ~ .))) %>%
  dplyr::mutate(
    dplyr::across(c(dplyr::contains("Circularity")), ~
                    dplyr::case_when(grepl(., pattern = '[:alpha:]') ~ NA,
                                     TRUE ~ .))) |>
  dplyr::mutate(dummy_1 = dplyr::lag(`Puncta Area_1`) - `Puncta Area_1`,
                .after = 3) |>
  dplyr::mutate(dummy_1 = dplyr::case_when(is.na(dummy_1) &
                                             dplyr::lead(!is.na(dummy_1)) ~ 0,
                                           TRUE ~ dummy_1)) |>
  dplyr::mutate(dummy_2 = dplyr::lag(`Puncta Area_2`) - `Puncta Area_2`,
                .after = 10) |>
  dplyr::mutate(dummy_2 = dplyr::case_when(is.na(dummy_2) &
                                             dplyr::lead(!is.na(dummy_2)) ~ 0,
                                           TRUE ~ dummy_2)) |>
  dplyr::mutate(dummy_3 = dplyr::lag(`Puncta Area_3`) - `Puncta Area_3`,
                .after = 18) |>
  dplyr::mutate(dummy_3 = dplyr::case_when(is.na(dummy_3) &
                                             dplyr::lead(!is.na(dummy_3)) ~ 0,
                                           TRUE ~ dummy_3)) |>
  dplyr::mutate(`Puncta Area_1` = dplyr::case_when(is.na(dummy_1) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_1`)) |>
  dplyr::mutate(`Puncta Area_2` = dplyr::case_when(is.na(dummy_2) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_2`)) |>
  dplyr::mutate(`Puncta Area_3` = dplyr::case_when(is.na(dummy_3) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_3`)) |>
  dplyr::mutate(
    `Puncta Circularity_1` = dplyr::case_when(is.na(dummy_1) &
                                                is.na(`Puncta ID_1`) ~ NA,
                                              TRUE ~ `Puncta Circularity_1`)) |>
  dplyr::mutate(
    `Puncta Circularity_2` = dplyr::case_when(is.na(dummy_2) &
                                                is.na(`Puncta ID_2`) ~ NA,
                                              TRUE ~ `Puncta Circularity_2`)) |>
  dplyr::mutate(
    `Puncta Circularity_3` = dplyr::case_when(is.na(dummy_3) &
                                                is.na(`Puncta ID_3`) ~ NA,
                                              TRUE ~ `Puncta Circularity_3`)) |>
  dplyr::select(-dplyr::contains('dummy')) |>
  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(
      `Puncta Circularity_1` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_1`))) |>
  dplyr::mutate(
    `Puncta Area_2` = dplyr::case_when(
      `Puncta Circularity_2` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_2`))) |>
  dplyr::mutate(
    `Puncta Area_3` = dplyr::case_when(
      `Puncta Circularity_3` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_3`))) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains('Puncta Area'), ~as.character(.))) |>
  tidyr::pivot_longer(
    cols = tidyr::everything(), 
    names_to = c('cell', 'cell_num'), 
    names_sep = '_', 
    values_to = 'values') |>
  dplyr::mutate(
    cell_num = gsub(cell_num, pattern = ' ratio', replacement = '')) |>
  dplyr::mutate(
    cell = gsub(cell, pattern = ' per puncta', replacement = '')) |>
  dplyr::mutate(
    puncta_num = dplyr::case_when(!grepl(values, pattern = '\\.') ~ values,
                                  TRUE ~ NA)) |>
  dplyr::mutate(
    overall_puncta_num = dplyr::case_when(!is.na(puncta_num) ~ 1,
                                          TRUE ~ NA_real_)) |>
  dplyr::group_by(overall_puncta_num) |>
  dplyr::mutate(overall_puncta_num = cumsum(overall_puncta_num)) |>
  dplyr::ungroup() |>
  tidyr::fill(overall_puncta_num, .direction = 'down') |>
  dplyr::filter(!is.na(values)) |>
  tidyr::pivot_wider(
    id_cols = c('cell_num', 'puncta_num' ,'overall_puncta_num'),
    names_from = 'cell',
    values_from = 'values') |>
  tidyr::fill(`Puncta ID`, .direction = 'down') |>
  dplyr::filter(!is.na(`Puncta Area`)) %>%
  dplyr::select(where(~!all(is.na(.)))) |>
  dplyr::relocate(`Puncta ID`, .after = 1) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\/', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '``', replacement = '')) |>
  dplyr::rename(GreenRed_Ratio = GREENRED_ratio) |>
  # dplyr::mutate(dplyr::across(c(4:8), ~as.numeric(.x))) |>
  dplyr::select(-overall_puncta_num) |>
  dplyr::mutate(cell_num = dplyr::case_when(cell_num == 1 ~ "9",
                                            cell_num == 2 ~ "10",
                                            cell_num == 3 ~ "11"))
```

```{r ReARR MUT cells 12 and 13, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_Mut_puncta_12_13 <- FIRE_pHly_Mut_puncta |>
  dplyr::slice(-1) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+1$', replacement = 'Puncta Area_1')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+2$', replacement = 'Puncta Area_2')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+3$', replacement = 'Puncta Area_3')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+4$', replacement = 'Puncta Area_4')) %>%
  dplyr::rename_with(
    ~gsub(.x, pattern = 'Puncta Area.+5$', replacement = 'Puncta Area_5')) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains('Puncta Area'), ~ as.numeric(.x))) |>
  dplyr::slice(c(125:147)) %>%
  dplyr::mutate(
    dplyr::across(c(dplyr::contains('Puncta ID')), ~
                    dplyr::case_when(grepl(., pattern = 'Avg.') ~ NA,
                                     TRUE ~ .))) %>%
  dplyr::mutate(
    dplyr::across(c(dplyr::contains("Circularity")), ~
                    dplyr::case_when(grepl(., pattern = '[:alpha:]') ~ NA,
                                     TRUE ~ .))) |>
  dplyr::mutate(dummy_1 = dplyr::lag(`Puncta Area_1`) - `Puncta Area_1`,
                .after = 3) |>
  dplyr::mutate(dummy_1 = dplyr::case_when(is.na(dummy_1) &
                                             dplyr::lead(!is.na(dummy_1)) ~ 0,
                                           TRUE ~ dummy_1)) |>
  dplyr::mutate(dummy_2 = dplyr::lag(`Puncta Area_2`) - `Puncta Area_2`,
                .after = 10) |>
  dplyr::mutate(dummy_2 = dplyr::case_when(is.na(dummy_2) &
                                             dplyr::lead(!is.na(dummy_2)) ~ 0,
                                           TRUE ~ dummy_2)) |>
  dplyr::mutate(`Puncta Area_1` = dplyr::case_when(is.na(dummy_1) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_1`)) |>
  dplyr::mutate(`Puncta Area_2` = dplyr::case_when(is.na(dummy_2) ~ NA_real_,
                                                   TRUE ~ `Puncta Area_2`)) |>
  dplyr::mutate(
    `Puncta Circularity_1` = dplyr::case_when(is.na(dummy_1) &
                                                is.na(`Puncta ID_1`) ~ NA,
                                              TRUE ~ `Puncta Circularity_1`)) |>
  dplyr::mutate(
    `Puncta Circularity_2` = dplyr::case_when(is.na(dummy_2) &
                                                is.na(`Puncta ID_2`) ~ NA,
                                              TRUE ~ `Puncta Circularity_2`)) |>
  dplyr::select(-dplyr::contains('dummy')) |>
  dplyr::mutate(
    `Puncta Area_1` = dplyr::case_when(
      `Puncta Circularity_1` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_1`))) |>
  dplyr::mutate(
    `Puncta Area_2` = dplyr::case_when(
      `Puncta Circularity_2` == "Puncta Circularity" ~ 'Puncta Area',
      TRUE ~ as.character(`Puncta Area_2`))) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains('Puncta Area'), ~as.character(.))) |>
  tidyr::pivot_longer(
    cols = tidyr::everything(),
    names_to = c('cell', 'cell_num'),
    names_sep = '_',
    values_to = 'values') |>
  dplyr::mutate(
    cell_num = gsub(cell_num, pattern = ' ratio', replacement = '')) |>
  dplyr::mutate(
    cell = gsub(cell, pattern = ' per puncta', replacement = '')) |>
  dplyr::mutate(
    puncta_num = dplyr::case_when(!grepl(values, pattern = '\\.') ~ values,
                                  TRUE ~ NA)) |>
  dplyr::mutate(
    overall_puncta_num = dplyr::case_when(!is.na(puncta_num) ~ 1,
                                          TRUE ~ NA_real_)) |>
  dplyr::group_by(overall_puncta_num) |>
  dplyr::mutate(overall_puncta_num = cumsum(overall_puncta_num)) |>
  dplyr::ungroup() |>
  tidyr::fill(overall_puncta_num, .direction = 'down') |>
  dplyr::filter(!is.na(values)) |>
  tidyr::pivot_wider(
    id_cols = c('cell_num', 'puncta_num' ,'overall_puncta_num'),
    names_from = 'cell',
    values_from = 'values') |>
  tidyr::fill(`Puncta ID`, .direction = 'down') |>
  dplyr::filter(!is.na(`Puncta Area`)) %>%
  dplyr::select(where(~!all(is.na(.)))) |>
  dplyr::relocate(`Puncta ID`, .after = 1) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\s', replacement = '_')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '\\/', replacement = '')) %>%
  dplyr::rename_with(~gsub(.x, pattern = '``', replacement = '')) %>%
  dplyr::rename(GreenRed_Ratio = GREENRED_ratio) |>
  # dplyr::mutate(dplyr::across(c(4:8), ~as.numeric(.x))) |>
  dplyr::select(-overall_puncta_num) |>
  dplyr::mutate(cell_num = dplyr::case_when(cell_num == 1 ~ "12",
                                            cell_num == 2 ~ "13"))
```

```{r Join MUT cells, eval = F, include = T, message = F, warning = F, echo = T}
FIRE_pHly_Mut_puncta_tot <- FIRE_pHly_Mut_puncta_1_5 |>
  dplyr::full_join(FIRE_pHly_Mut_puncta_6_8) |>
  dplyr::full_join(FIRE_pHly_Mut_puncta_9_11) |>
  dplyr::full_join(FIRE_pHly_Mut_puncta_12_13) %>%
  dplyr::mutate(dplyr::across(c(1:2), ~as.numeric(.x))) |>
  dplyr::arrange(cell_num, Puncta_ID) %>%
  dplyr::mutate(dplyr::across(c(1:2), ~as.character(.x)))
```

#### Join WT and MUT Data

```{r Join WT and MUT data, eval = F, include = T, message = F, warning = F, echo = T}
Puncta_data <- FIRE_pHly_WT_puncta_tot %>%
  dplyr::mutate(dplyr::across(c(1:2), ~as.numeric(.x))) |>
  dplyr::arrange(cell_num, Puncta_ID) |>
  dplyr::mutate(Genotype = 'WT', .before = 1) %>%
  dplyr::mutate(dplyr::across(c(2:3), ~as.character(.x))) |>
  dplyr::full_join(
    FIRE_pHly_Mut_puncta_tot |>
      dplyr::mutate(Genotype = 'MUT', .before = 1))

Puncta_data <- Puncta_data |>
  dplyr::full_join(
    
    FIRE_pHly_WT_cell_sum |>
      dplyr::mutate(Genotype = 'WT', .before = 1) |>
      dplyr::select(-Filename) |>
      dplyr::full_join(
        
        FIRE_pHly_Mut_cell_sum |>
          dplyr::mutate(Genotype = 'MUT', .before = 1) |>
          dplyr::select(-Filename)
        ) |>
      dplyr::mutate(cell_num = as.character(cell_num))
    ) %>%
  dplyr::rename_with(
    ~gsub(.x,
          pattern = '^(\\w+)_Mean_Intensity',
          replacement = 'Intra_Puncta_\\1_Intensity')) %>%
  dplyr::rename_with(
    ~gsub(.x,
          pattern = 'Puncta_Mean_(\\w+)(.+?$)',
          replacement = 'Cell_Avg_Puncta_\\1\\2'))

rm(list = ls()[which(grepl(ls(), pattern = 'FIREpHly_') == T)])
```

### Visualize {.tabset .tabset-pills .tabset-fade}

<span style="color:black;font-size: 16px">Investigate the distributions of measured variables</span>

#### Puncta Area Histogram

```{r Puncta Area Histogram full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = Puncta_Area, col = Genotype, fill = Genotype, alpha = 0.5)) +
  geom_histogram(binwidth = 0.01) +
  labs(title = 'Hippocampal Neuron Puncta Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Count\n(binwidth = 0.01)') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.85, 0.5),
        legend.title = element_text(face = 'bold', size = 10),
        legend.text = element_text(face = 'bold', size = 10)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area Histogram (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta Area Histogram cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = Puncta_Area, col = Genotype, fill = Genotype, alpha = 0.5)) +
  geom_histogram(binwidth = 0.01) +
  labs(title = 'Hippocampal Neuron Puncta Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Count\n(binwidth = 0.01)') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.85, 0.5),
        legend.title = element_text(face = 'bold', size = 10),
        legend.text = element_text(face = 'bold', size = 10)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area Density

```{r Puncta Area Density full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = Puncta_Area, col = Genotype, fill = Genotype)) +
  geom_density(alpha =  0.5) +
  labs(title = 'Hippocampal Neuron Puncta Area Density Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Density') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.80, 0.5),
        legend.title = element_text(face = 'bold', size = 11),
        legend.text = element_text(face = 'bold', size = 11)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area Density (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta Area Density cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = Puncta_Area, col = Genotype, fill = Genotype)) +
  geom_density(alpha =  0.5) +
  labs(title = 'Hippocampal Neuron Puncta Area Density Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Density') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.80, 0.5),
        legend.title = element_text(face = 'bold', size = 11),
        legend.text = element_text(face = 'bold', size = 11)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area Violin

```{r Puncta Area Violin, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = Puncta_Area, y = Genotype, color = Genotype, fill = Genotype)
         ) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), alpha = 0.2) +
  # geom_boxplot(inherit.aes = T,
  #              outlier.shape = 'triangle',
  #              outlier.alpha = 0.5, outlier.color = 'black', alpha = 0.5) +
  geom_jitter(aes(width = 0.1, alpha = 0.5, color = Genotype)) +
  labs(title = 'Hippocampal Neuron Puncta Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Genotype') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        panel.grid.major.y = element_blank(),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = 'none'
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Acidity Histogram

```{r Puncta Acidity Histogram full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = GreenRed_Ratio, col = Genotype, fill = Genotype, alpha = 0.5)
         ) +
  geom_histogram(binwidth = 0.1) +
  labs(title = 'Hippocampal Neuron Puncta Acidity Distributions',
       x = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       y = 'Count\n(binwidth = 0.1)') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.8, 0.5),
        legend.title = element_text(face = 'bold', size = 11),
        legend.text = element_text(face = 'bold', size = 11)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Acidity Histogram (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta Acidity Histogram cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = GreenRed_Ratio, col = Genotype, fill = Genotype, alpha = 0.5)
         ) +
  geom_histogram(binwidth = 0.1) +
  labs(title = 'Hippocampal Neuron Puncta Acidity Distributions',
       x = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       y = 'Count\n(binwidth = 0.1)') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.8, 0.5),
        legend.title = element_text(face = 'bold', size = 11),
        legend.text = element_text(face = 'bold', size = 11)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Acidity Density

```{r Puncta Acidity Density full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = GreenRed_Ratio, col = Genotype, fill = Genotype)) +
  geom_density(alpha =  0.5) +
  labs(title = 'Hippocampal Neuron Puncta Acidity Density Distributions',
       x = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       y = 'Density') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.80, 0.5),
        legend.title = element_text(face = 'bold', size = 11),
        legend.text = element_text(face = 'bold', size = 11)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Acidity Density (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta Acidity Density cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = GreenRed_Ratio, col = Genotype, fill = Genotype)) +
  geom_density(alpha =  0.5) +
  labs(title = 'Hippocampal Neuron Puncta Acidity Density Distributions',
       x = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       y = 'Density') +
  guides(col = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 10),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.80, 0.5),
        legend.title = element_text(face = 'bold', size = 11),
        legend.text = element_text(face = 'bold', size = 11)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area and Acidity Contour

```{r Puncta Area and Acidity 2d density full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 5}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num),
                Puncta_Area_to_Cell_Body_Area_Ratio = Puncta_Area/Cell_Body_Area
                ) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = Puncta_Area,
             y = GreenRed_Ratio, col = Genotype, fill = Genotype)) +
  geom_point(alpha = 0.1, size = 2.5) +
  geom_density_2d(contour_var = 'density', linewidth = 1, alpha = 0.7) +
  labs(title = 'Hippocampal Neuron Puncta Acidity and Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       #(', '&mu;m<sup>2</sup>', ')',
       y = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       fill = 'Genotype') +
  guides(fill = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 10),
        axis.text = element_text(face = 'bold', size = 9),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.80, 0.6),
        legend.title = element_text(face = 'bold', size = 9),
        legend.text = element_text(face = 'bold', size = 9)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area and Acidity Contour (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta Area and Acidity 2d density cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 5}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num),
                Puncta_Area_to_Cell_Body_Area_Ratio = Puncta_Area/Cell_Body_Area
                ) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot(aes(x = Puncta_Area,
             y = GreenRed_Ratio, col = Genotype, fill = Genotype)) +
  geom_point(alpha = 0.1, size = 2.5) +
  geom_density_2d(contour_var = 'density', linewidth = 1, alpha = 0.7) +
  labs(title = 'Hippocampal Neuron Puncta Acidity and Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       #(', '&mu;m<sup>2</sup>', ')',
       y = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       fill = 'Genotype') +
  guides(fill = 'none', alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_text(face = 'bold', size = 10),
        axis.text = element_text(face = 'bold', size = 9),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.position = c(0.80, 0.6),
        legend.title = element_text(face = 'bold', size = 9),
        legend.text = element_text(face = 'bold', size = 9)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```


### Statistics {.tabset .tabset-pills .tabset-fade}

<span style="color:black;font-size: 16px">Perform weighted linear regressions on puncta data</span>  

<span style="color:black;font-size: 18px">It appropriately accounts for:</span>  

* <span style="color:black;font-size: 16px">experimenter bias</span>  
* <span style="color:black;font-size: 16px">inter-mouse variability</span>  
* <span style="color:black;font-size: 16px">(genotypic) inter-puncta variability</span>

#### Puncta Acidity

```{r Puncta Acidity wlm, include = T, message = F, warning = F, echo = F}
Puncta_avg_acidity <- Puncta_data |>
  dplyr::mutate(genotype_puncta_n = NA_real_, .after = Puncta_ID) |>
  dplyr::group_by(Genotype) |>
  dplyr::mutate(
    genotype_puncta_n = length(Puncta_ID)) |> # determine puncta_n per genotype
  dplyr::ungroup() |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::mutate(
    mouse_puncta_w = (length(Puncta_ID)/genotype_puncta_n)*10
    ) |> # give a "mouse" weight (around fractions of a whole mouse)
  dplyr::ungroup() |>
  dplyr::distinct(
    Genotype,
    cell_num,
    genotype_puncta_n,
    mouse_puncta_w,
    Puncta_Count,
    Cell_Avg_Puncta_GreenRedRatio)

puncta_acidity_lm <- lm(
  data = Puncta_avg_acidity,
  formula = Cell_Avg_Puncta_GreenRedRatio ~ Genotype,
  weights = mouse_puncta_w)

summary(puncta_acidity_lm)
```

<span style="color:navy;font-size: 18px">Strong significant difference between genotypes
(mutant more alkaline)</span>

<span style="color:black;font-size: 16px">Check shaprio-wilk</span>

```{r Puncta Acidity Shapiro, include = T, message = F, warning = F, echo = F}
## test for normality violations
shapiro_puncta_acidity <- shapiro.test(
  summary(puncta_acidity_lm)$residuals |> as.numeric())

shapiro.test(summary(puncta_acidity_lm)$residuals |> as.numeric())
```
<span style="color:black;font-size: 18px">Not non-normal</span>

#### Puncta Area
```{r Puncta Area wlm, include = T, message = F, warning = F, echo = F}
Puncta_avg_area <- Puncta_data |>
  dplyr::mutate(genotype_puncta_n = NA_real_, .after = Puncta_ID) |>
  dplyr::group_by(Genotype) |>
  dplyr::mutate(
    genotype_puncta_n = length(Puncta_ID)) |> # determine puncta_n per genotype
  dplyr::ungroup() |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::mutate(mouse_puncta_w = (length(Puncta_ID)/genotype_puncta_n)*10,
                Cell_Avg_Puncta_Area = mean(as.numeric(Puncta_Area))
                ) |> # give a "mouse" weight (around fractions of a whole mouse)
  dplyr::ungroup() |>
  dplyr::distinct(
    Genotype,
    cell_num,
    genotype_puncta_n,
    mouse_puncta_w,
    Puncta_Count,
    Cell_Avg_Puncta_Area)

puncta_area_lm <- lm(
  Cell_Avg_Puncta_Area ~ Genotype,
  data = Puncta_avg_area,
  weights = mouse_puncta_w)

summary(puncta_area_lm)
```

<span style="color:black;font-size: 18px">No significant difference between genotypes in
auto-detected puncta in terms of their areas</span>

<span style="color:black;font-size: 16px">Check shapiro-wilk</span>

```{r Puncta Area Shapiro, include = T, message = F, warning = F, echo = F}
## test for normality violations
shapiro_puncta_area <- shapiro.test(
  summary(puncta_area_lm)$residuals |> as.numeric())

shapiro.test(summary(puncta_area_lm)$residuals |> as.numeric())
```

<span style="color:black;font-size: 18px">Not non-normal</span>

#### Puncta Number (wlm)
```{r Puncta Number wlm, include = T, message = F, warning = F, echo = F}
Puncta_n <- Puncta_data |>
  dplyr::mutate(genotype_puncta_n = NA_real_, .after = Puncta_ID) |>
  dplyr::group_by(Genotype) |>
  dplyr::mutate(genotype_puncta_n = length(Puncta_ID)) |>
  dplyr::ungroup() |>
  dplyr::mutate(mouse_puncta_w = (length(Puncta_ID)/genotype_puncta_n)*10) |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::mutate(puncta_n = n()) |>
  dplyr::ungroup() |>
  dplyr::distinct(Genotype, cell_num, puncta_n, mouse_puncta_w)

puncta_n_lm <- lm(
  data = Puncta_n,
  formula = puncta_n ~ Genotype,
  weights = mouse_puncta_w)

summary(puncta_n_lm)
```

<span style="color:black;font-size: 18px">No significant difference between genotypes</span>

#### Puncta Number (Welch's t)
```{r Puncta number Welchs t, include = T, message = F, warning = F, echo = T}
## more traditional Welch's t
t.test(
  x = c(Puncta_data |>
          dplyr::group_by(Genotype) |>
          dplyr::distinct(Puncta_Count) |>
          dplyr::ungroup() |>
          dplyr::filter(Genotype == "WT") |>
          dplyr::select(Puncta_Count) |>
          unlist() |> as.numeric()
),
y = c(Puncta_data |>
          dplyr::group_by(Genotype) |>
          dplyr::distinct(Puncta_Count) |>
          dplyr::ungroup() |>
          dplyr::filter(Genotype == "MUT") |>
          dplyr::select(Puncta_Count) |>
          unlist() |> as.numeric()
),
alternative = 'two.sided', var.equal = F
)
```
<span style="color:black;font-size: 18px">No significant difference between genotype-dependent
puncta number auto-detected by computer software</span>

<span style="color:black;font-size: 16px">Check shapiro-wilk</span>

```{r Puncta Number Shapiro, include = T, message = F, warning = F, echo = F}
## test for normality violations
shapiro_puncta_n <- shapiro.test(
  summary(puncta_n_lm)$residuals |> as.numeric())

shapiro.test(summary(puncta_n_lm)$residuals |> as.numeric())
```

<span style="color:black;font-size: 18px">Not non-normal</span>

#### Cell Body Area
```{r Cell Body Area lm, include = T, message = F, warning = F, echo = T}
  ## Welch's t test
t.test(x = c(Puncta_data |>
               dplyr::group_by(Genotype, cell_num) |>
               dplyr::distinct(Cell_Body_Area) |>
               dplyr::ungroup() |>
               dplyr::filter(Genotype == "WT") |>
               dplyr::select(Cell_Body_Area) |>
               unlist() |> as.numeric()
),
y = c(Puncta_data |>
        dplyr::group_by(Genotype, cell_num) |>
        dplyr::distinct(Cell_Body_Area) |>
        dplyr::ungroup() |>
        dplyr::filter(Genotype == "MUT") |>
        dplyr::select(Cell_Body_Area) |>
        unlist() |> as.numeric()
),
alternative = 'two.sided', var.equal = F)
```

<span style="color:darkred;font-size: 18px">Mutant cell bodies are significantly larger than
wild-type cell bodies; this is likely due to sampling bias and likely does not
relate to pH-dependent results since those are weighted by the number of puncta,
which is not significantly different</span>

<span style="color:black;font-size: 16px">Check shapiro-wilk</span>

```{r Cell Body Area Shapiro, include = T, message = F, warning = F, echo = T}
  ## Examine residuals
    ## extract from lm (~ same as Welch's t test)
cell_area_lm <- lm(data = Puncta_data |>
                     dplyr::group_by(Genotype, cell_num) |>
                     dplyr::distinct(Cell_Body_Area) |>
                     dplyr::ungroup(),
                   formula = Cell_Body_Area ~ Genotype)

  ## Shapiro.wilk
shapiro_cell_area <- shapiro.test(
  summary(cell_area_lm)$residuals |> as.numeric())

shapiro.test(summary(cell_area_lm)$residuals |> as.numeric())
```

<span style="color:darkred;font-size: 18px">Non-normal residuals, suggesting cell body size
difference is difficult to properly discern a significant difference due to
outliers or, more broadly, differently-distributed cell body areas. This is
obvious and, again, not necessarily relevant</span>

<span style="color:black;font-size: 16px">Significant. Show the residuals</span>

#### Cell Body Area residuals dist
```{r Cell Body Area lm residuals dist, include = T, message = F, warning = F, echo = T, fig.width = 6, fig.height = 4}
  ## Cell Body area residuals distributions
Puncta_data |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::distinct(Cell_Body_Area) |>
  dplyr::ungroup() |>
  dplyr::mutate(Cell_Body_Area = as.numeric(Cell_Body_Area),
                resids = lm(data = Puncta_data |>
                              dplyr::group_by(Genotype, cell_num) |>
                              dplyr::distinct(Cell_Body_Area) |>
                              dplyr::ungroup(),
                            formula = as.numeric(Cell_Body_Area) ~ Genotype
                            )$residuals |> as.numeric()
                ) |>
  ggplot(aes(x = resids, y = Genotype, color = Genotype, fill = Genotype)) +
  geom_violin(alpha = 0.3) +
  stat_summary(fun.y = 'median',
               geom = 'point',
               color = 'black',
               size = 5,
               show.legend = FALSE) +
  guides(alpha = 'none') +
  geom_jitter(data = Puncta_data |>
                dplyr::group_by(Genotype, cell_num) |>
                dplyr::distinct(Cell_Body_Area) |>
                dplyr::ungroup() |>
                dplyr::mutate(
                  Cell_Body_Area = as.numeric(Cell_Body_Area),
                  resids = lm(data = Puncta_data |>
                                dplyr::group_by(Genotype, cell_num) |>
                                dplyr::distinct(Cell_Body_Area) |>
                                dplyr::ungroup(),
                              formula = as.numeric(Cell_Body_Area) ~ Genotype
                              )$residuals |> as.numeric()
                ),
              aes(x = resids,
                  y = Genotype), alpha = 1, width = 0.01, height = 0.1) +
  labs(title = 'Hippocampal Neuron Cell Body\nlm fit residual distributions',
       x = 'lm fit residuals',
       y = 'Genotype') +
  theme_bw() +
  theme(title = element_text(face = 'bold', size = 13),
        axis.title = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 11),
        panel.grid = element_blank(),
        legend.text = element_text(face = 'bold', size = 10)
  ) +
  guides(alpha = 'none') +
  scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  scale_fill_manual(values = c('navy', 'darkgoldenrod3'))
```

<span style="color:darkred;font-size: 18px">The residual average cell body size for each mouse is
not the same between genotypes</span>

<span style="color:black;font-size: 16px">What's the shape of the dv, taking both genotypes into account?</span>

#### Cell Body Area density
```{r Cell Body Area density, include = T, message = F, warning = F, echo = T}
Puncta_data |> dplyr::distinct(Cell_Body_Area) |> 
  ggplot(aes(x = as.numeric(Cell_Body_Area))) +
  geom_density(fill = 'black', alpha = 0.5) +
  labs(x = expression(paste("Cell Body Area (", mu, m^2, ")")))
```

<span style="color:darkred;font-size: 18px">Negative binomial. Unsurprising, particularly for
small sample sizes; the borderline difference suggests the sample sizes are
nearly powerful enough</span>


<span style="color:black;font-size: 18px">Still, consider alternatives:</span> 

* <span style="color:black;font-size: 16px">a `glm` with an **inverse-Gaussian fit** (probably the appropriate alternative)</span>  
* <span style="color:black;font-size: 16px">`Wilcoxon-ranked sum (Mann-Whitney)` (probably the next appropriate alternative)</span>  
* <span style="color:black;font-size: 16px">`Komolgorov-Smirnov`</span>  

<span style="color:black;font-size: 16px">First, the `glm`</span>
```{r Cell Body Area glm, include = T, message = F, warning = F, echo = T}
  ## GLM
cell_area_glm <- glm(data = Puncta_data |>
                       dplyr::group_by(Genotype, cell_num) |>
                       dplyr::distinct(Cell_Body_Area) |>
                       dplyr::ungroup(),
                     formula = as.numeric(Cell_Body_Area) ~ Genotype,
                     family = 'Gamma')

summary(cell_area_glm)
```

<span style="color:navy;font-size: 18px">No significant difference between genotypes when
using a `glm` with an **inverse-Gaussian** to account for different (non-normal)
distribution shapes</span>


<span style="color:black;font-size: 18px">What about the `MannWhitney`/`Wilcoxon-ranked sum`?</span>    

* <span style="color:black;font-size: 16px">Compares the medians of two groups because the data violate assumptions
(such as normality, as in this case)</span>  
* <span style="color:black;font-size: 16px">often, "outliers" skew distributions and/or unequal variances between groups</span>

```{r Cell Body Area MannWhitney, include = T, message = F, warning = F, echo = T}
wilcox.test(data = Puncta_data |>
              dplyr::group_by(Genotype, cell_num) |>
              dplyr::distinct(Cell_Body_Area) |>
              dplyr::ungroup(),
            as.numeric(Cell_Body_Area) ~ Genotype)
```

<span style="color:darkred;font-size: 18px">Significant difference between the genotypes. Not
sure how this contributes to pH difference in endolysosomes marked by the
FIREpHly marker (Lamp1)</span>


<span style="color:black;font-size: 18px">What about the `Kolmogorov-Smirnov`?</span>

* <span style="color:black;font-size: 16px">`KS test` does *not* assume the sample means of two groups come from the same 
distribution (a more conservative, non-parametric test)</span>


<span style="color:black;font-size: 16px">We assume this in genetic studies (hence the `glm`)</span>

```{r Cell Body Area KS test, include = T, message = F, warning = F, echo = T}
  ## KS
ks.test(x = c(Puncta_data |>
                dplyr::group_by(Genotype, cell_num) |>
                dplyr::distinct(Cell_Body_Area) |>
                dplyr::ungroup() |>
                dplyr::filter(Genotype == "WT") |>
                dplyr::select(Cell_Body_Area) |>
                unlist() |> as.numeric()
        ),
        y = c(Puncta_data |>
                dplyr::group_by(Genotype, cell_num) |>
                dplyr::distinct(Cell_Body_Area) |>
                dplyr::ungroup() |>
                dplyr::filter(Genotype == "MUT") |>
                dplyr::select(Cell_Body_Area) |>
                unlist() |> as.numeric()
        ),
        alternative = 'two.sided')
```

<span style="color:darkred;font-size: 18px">Significant difference between the genotypes.</span>


<span style="color:black;font-size: 18px">Defer to GraphPad Prism statistical results, though I am satisfied by the `glm`
with the inverse-Gaussian fit; again, this is a minor issue, though I will note
it here</span>

<span style="color:black;font-size: 16px">Is there a relationship between cell body size and puncta size?</span>
<span style="color:black;font-size: 16px">Do the genotypes differ? (see `Cell Body Area vs Avg Puncta Area scatter w/fit` tab)</span>

#### Cell Body Area vs Avg Puncta Area scatter w/fit

```{r Cell Body Area Scatter w lm fit, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(
    GreenRed_Ratio = as.numeric(GreenRed_Ratio),
    Puncta_Area = as.numeric(Puncta_Area),
    Cell_Body_Area = as.numeric(Cell_Body_Area),
    cell_num = as.numeric(cell_num),
    Puncta_Area_to_Cell_Body_Area_Ratio = Puncta_Area/Cell_Body_Area) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::mutate(mean_Puncta_Area = mean(Puncta_Area)) |>
  dplyr::distinct(Cell_Body_Area, mean_Puncta_Area) |>
  ggplot(aes(x = Cell_Body_Area,
             y = mean_Puncta_Area,
             col = Genotype,
             fill = Genotype)) +
  geom_point(aes(x = Cell_Body_Area,
                 y = mean_Puncta_Area,
                 col = Genotype,
                 fill = Genotype), size = 3) +
  labs(title = 'Hippocampal Neuron Puncta Area and Cell Body Area',
       x = paste0('Neuronal Cell Body Area (', '&mu;m<sup>2</sup>', ')'),
       y = paste0('Cell Average Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       fill = 'Genotype') +
  guides(alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_markdown(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 9),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.title = element_text(face = 'bold', size = 11),
        legend.text = element_text(face = 'bold', size = 11)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3")) +
  scale_y_continuous(breaks = c(0.400, 0.500, 0.600, 0.700, 0.800),
                     labels = c(0.400, 0.500, 0.600, 0.700, 0.800)) +
  geom_smooth(
    aes(x = Cell_Body_Area,
        y = Puncta_data |>
          as.data.frame() |>
          dplyr::mutate(
            GreenRed_Ratio = as.numeric(GreenRed_Ratio),
            Puncta_Area = as.numeric(Puncta_Area),
            Cell_Body_Area = as.numeric(Cell_Body_Area),
            cell_num = as.numeric(cell_num),
            Puncta_Area_to_Cell_Body_Area_Ratio = Puncta_Area/Cell_Body_Area
            ) |>
          # dplyr::filter(GreenRed_Ratio < 25) |>
          # dplyr::filter(Puncta_Area < 2) |>
          dplyr::group_by(Genotype, cell_num) |>
          dplyr::mutate(mean_Puncta_Area = mean(Puncta_Area)) |>
          dplyr::distinct(Cell_Body_Area, mean_Puncta_Area) |>
          dplyr::ungroup() |>
          dplyr::select(mean_Puncta_Area) |>
          unlist() |> as.numeric()
        ),
    method = 'lm', se = F)
```

#### Cell Body Area vs Avg Puncta Area summary

```{r Cell Body and Genotype Do Not Predict Avg Puncta Area, include = T, message = F, warning = F, echo = T}
summary(lm(data = Puncta_data |>
     as.data.frame() |>
     dplyr::mutate(
       Puncta_Area = as.numeric(Puncta_Area),
       Cell_Body_Area = as.numeric(Cell_Body_Area),
       cell_num = as.numeric(cell_num)) |>
     dplyr::group_by(Genotype, cell_num) |>
     dplyr::mutate(mean_Puncta_Area = mean(Puncta_Area)) |>
     dplyr::distinct(Cell_Body_Area, mean_Puncta_Area) |>
     dplyr::ungroup(),
   
   formula = mean_Puncta_Area ~ 
     Cell_Body_Area*Genotype
     ))
```

<span style="color:black;font-size: 18px">No clear relationship between average puncta area
and cell body area between the two genotypes (though, mutants have larger cell
bodies)</span>

<span style="color:black;font-size: 16px">Thus, mutant endolysosomal cell bodies may be significantly larger; however,
there is no difference in the puncta size between the two genotypes</span>

### Stats Plots {.tabset .tabset-pills .tabset-fade}

<span style="color:black;font-size: 16px">Visualize the statistical test results</span>

#### Puncta Acidity Bar

```{r Puncta Acidity Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
puncta_acidity_lm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `puncta_acidity_lm$model$Genotype`) |>
  dplyr::mutate(
                fitted.means = c(puncta_acidity_lm$fitted.values |>
                                   unlist() |>
                                   as.numeric()
                                 )[c(1,14)],
                fitted.se = c(summary(puncta_acidity_lm)$coeff[,2][2] |>
                                unlist() |>
                                as.numeric(),
                              summary(puncta_acidity_lm)$coeff[,2][1] |>
                                unlist() |>
                                as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

ggplot(aes(
  x = Genotype,
  y = fitted.means,
  color = Genotype,
  fill = Genotype,
  alpha = 0.5))+
  geom_bar(stat = 'identity') +
  geom_errorbar(aes(x = Genotype, ymin = y_min, ymax = y_max), width = 0.25) +
  geom_point(data = puncta_acidity_lm$model$Genotype |>
                as.data.frame() |>
                dplyr::rename(Genotype = `puncta_acidity_lm$model$Genotype`) |>
                dplyr::mutate(
                  fitted.means = c(
                    puncta_acidity_lm$fitted.values |> unlist() |> as.numeric()),
                  fitted.se = c(
                    rep(
                      summary(puncta_acidity_lm)$coeff[,2][2] |>
                        unlist() |>
                        as.numeric(),
                      10),
                    rep(
                      summary(puncta_acidity_lm)$coeff[,2][1] |>
                        unlist() |>
                        as.numeric(),
                      13)),
                  avg_gr_ratio = c(
                    as.numeric(puncta_acidity_lm$model$Cell_Avg_Puncta_GreenRedRatio)
                    )) |>
                dplyr::group_by(Genotype) |>
                dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
                dplyr::ungroup(),
              aes(x = Genotype, y = avg_gr_ratio)) +
  labs(title = 'Hippocampal Neuron Puncta Acidity',
       x = 'Genotype',
       y = 'Weighted Cell Average Puncta Acidity (a.u.)') +
  theme_bw() +
  theme(title = element_text(face = 'bold', size = 13),
        axis.title = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 11),
        panel.grid = element_blank(),
        legend.text = element_text(face = 'bold', size = 10)
        ) +
  guides(alpha = 'none') +
  scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  geom_segment(x = 1, xend = 2, y = 2, yend = 2, color = 'black', size = 1) +
  # geom_signif()
  geom_text(
    aes(label = "**",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_acidity_lm)$fstatistic[1],
        #                 summary(puncta_acidity_lm)$fstatistic[2],
        #                 summary(puncta_acidity_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |> unlist() |> as.numeric(), 4)
        #        ),
        fontface = 'bold'
        ),
    size = 7,
    color = 'black',
    x = 1.5,
    y = 2.1)
```

#### Puncta Area Bar

```{r Puncta Area Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
## puncta area
puncta_area_lm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `puncta_area_lm$model$Genotype`) |>
  dplyr::mutate(
    fitted.means = c(puncta_area_lm$fitted.values |> unlist() |> as.numeric())[c(1,14)],
    fitted.se = c(summary(puncta_area_lm)$coeff[,2][2] |> unlist() |> as.numeric(),
                  summary(puncta_area_lm)$coeff[,2][1] |> unlist() |> as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

  ggplot(aes(
    x = Genotype,
    y = fitted.means,
    color = Genotype,
    fill = Genotype,
    alpha = 0.5))+
  geom_bar(stat = 'identity') +
  geom_errorbar(aes(x = Genotype, ymin = y_min, ymax = y_max), width = 0.25) +
  geom_point(data = puncta_area_lm$model$Genotype |>
               as.data.frame() |>
               dplyr::rename(Genotype = `puncta_area_lm$model$Genotype`) |>
               dplyr::mutate(
                 fitted.means = c(
                   puncta_area_lm$fitted.values |> unlist() |> as.numeric()),
                 fitted.se = c(
                   rep(
                     summary(puncta_area_lm)$coeff[,2][2] |>
                       unlist() |>
                       as.numeric(), 
                     10),
                   rep(
                     summary(puncta_area_lm)$coeff[,2][1] |>
                       unlist() |>
                       as.numeric(),
                     13)),
                 avg_puncta_area = c(
                   as.numeric(puncta_area_lm$model$Cell_Avg_Puncta_Area)
                 )) |>
               dplyr::group_by(Genotype) |>
               dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
               dplyr::ungroup(),
             aes(x = Genotype, y = avg_puncta_area)) +
  labs(title = 'Hippocampal Neuron Puncta Area',
       x = 'Genotype',
       y = bquote('Weighted Cell Average Puncta Area '(mu*m^2)),
       ) +
  theme_bw() +
  theme(title = element_text(face = 'bold', size = 13),
        axis.title = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 11),
        panel.grid = element_blank(),
        legend.text = element_text(face = 'bold', size = 10)
  ) +
  guides(alpha = 'none') +
  scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  geom_segment(x = 1, xend = 2, y = 0.8, yend = 0.8, color = 'black', size = 1) +
  # geom_signif()
  geom_text(
    aes(label = "N.S.",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_acidity_lm)$fstatistic[1],
        #                 summary(puncta_acidity_lm)$fstatistic[2],
        #                 summary(puncta_acidity_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |> 
        #                unlist() |> 
        #                as.numeric(), 
        #              4)
        #        ),
        fontface = 'bold'
  ),
  size = 7,
  color = 'black',
  x = 1.5,
  y = 0.85)
```

#### Puncta Number Bar

```{r Puncta Number Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
puncta_n_lm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `puncta_n_lm$model$Genotype`) |>
  dplyr::mutate(
    fitted.means = c(puncta_n_lm$fitted.values |>
                       unlist() |>
                       as.numeric()
                     )[c(1,14)],
    fitted.se = c(summary(puncta_n_lm)$coeff[,2][2] |>
                    unlist() |>
                    as.numeric(),
                  summary(puncta_n_lm)$coeff[,2][1] |>
                    unlist() |>
                    as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

  ggplot(aes(
    x = Genotype,
    y = fitted.means,
    color = Genotype,
    fill = Genotype,
    alpha = 0.5))+
  geom_bar(stat = 'identity') +
  geom_errorbar(aes(x = Genotype, ymin = y_min, ymax = y_max), width = 0.25) +
  geom_point(data = puncta_n_lm$model$Genotype |>
               as.data.frame() |>
               dplyr::rename(Genotype = `puncta_n_lm$model$Genotype`) |>
               dplyr::mutate(
                 fitted.means = c(puncta_n_lm$fitted.values |> unlist() |> as.numeric()),
                 fitted.se = c(
                   rep(summary(puncta_n_lm)$coeff[,2][2] |>
                         unlist() |>
                         as.numeric(),
                       10),
                   rep(summary(puncta_n_lm)$coeff[,2][1] |>
                         unlist() |>
                         as.numeric(),
                       13)),
                 avg_puncta_n = c(as.numeric(puncta_n_lm$model$puncta_n)
                 )) |>
               dplyr::group_by(Genotype) |>
               dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
               dplyr::ungroup(),
             aes(x = Genotype, y = avg_puncta_n)) +
  labs(title = 'Hippocampal Neuron Puncta Number',
       x = 'Genotype',
       y = 'Weighted Cell Average Puncta Number',
  ) +
  theme_bw() +
  theme(title = element_text(face = 'bold', size = 13),
        axis.title = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 11),
        panel.grid = element_blank(),
        legend.text = element_text(face = 'bold', size = 10)
  ) +
  guides(alpha = 'none') +
  scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  geom_segment(x = 1, xend = 2, y = 30, yend = 30, color = 'black', size = 1) +
  # geom_signif()
  geom_text(
    aes(label = "N.S.",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_n_lm)$fstatistic[1],
        #                 summary(puncta_n_lm)$fstatistic[2],
        #                 summary(puncta_n_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |> unlist() |> as.numeric(), 4)
        #                      ),
        fontface = 'bold'
  ),
  size = 7,
  color = 'black',
  x = 1.5,
  y = 32)
```

#### Cell Body Area Bar (Welch's t)

```{r Cell Body Area Welch Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
cell_area_lm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `cell_area_lm$model$Genotype`) |>
  dplyr::mutate(
    fitted.means = c(
      cell_area_lm$fitted.values |> unlist() |> as.numeric())[c(1,14)],
    fitted.se = c(
      summary(cell_area_lm)$coeff[,2][2] |> unlist() |> as.numeric(),
      summary(cell_area_lm)$coeff[,2][1] |> unlist() |> as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

  ggplot(aes(
    x = Genotype,
    y = fitted.means,
    color = Genotype,
    fill = Genotype,
    alpha = 0.5))+
  geom_bar(stat = 'identity') +
  geom_errorbar(aes(x = Genotype, ymin = y_min, ymax = y_max), width = 0.25) +
  geom_point(data = cell_area_lm$model$Genotype |>
               as.data.frame() |>
               dplyr::rename(Genotype = `cell_area_lm$model$Genotype`) |>
               dplyr::mutate(
                 fitted.means = c(
                   cell_area_lm$fitted.values |> unlist() |> as.numeric()),
                 fitted.se = c(
                   rep(summary(cell_area_lm)$coeff[,2][2] |>
                         unlist() |>
                         as.numeric(),
                       10),
                   rep(summary(cell_area_lm)$coeff[,2][1] |>
                         unlist() |>
                         as.numeric(),
                       13)),
                 avg_cell_body_area = c(
                   as.numeric(cell_area_lm$model$Cell_Body_Area)
                 )) |>
               dplyr::group_by(Genotype) |>
               dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
               dplyr::ungroup(),
             aes(x = Genotype, y = avg_cell_body_area)) +
  labs(title = "Hippocampal Neuron Cell Body Area (Welch's t)",
       x = 'Genotype',
       y = bquote('Cell Body Area '(mu*m^2))) +
  theme_bw() +
  theme(title = element_text(face = 'bold', size = 13),
        axis.title = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 11),
        panel.grid = element_blank(),
        legend.text = element_text(face = 'bold', size = 10)
  ) +
  guides(alpha = 'none') +
  scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  geom_segment(x = 1, xend = 2, y = 400, yend = 400, color = 'black', size = 1) +
  # geom_signif()
  geom_text(
    aes(label = "*",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_acidity_lm)$fstatistic[1],
        #                 summary(puncta_acidity_lm)$fstatistic[2],
        #                 summary(puncta_acidity_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |>
        #                unlist() |>
        #                as.numeric(),
        #              4)
        #        ),
        fontface = 'bold'
        ),
    size = 7,
    color = 'black',
    x = 1.5,
    y = 410)
```

#### Cell Body Area Bar (glm)

```{r Cell Body Area Gamma Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
cell_area_glm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `cell_area_glm$model$Genotype`) |>
  dplyr::mutate(
    fitted.means = c(
      cell_area_glm$fitted.values |> unlist() |> as.numeric())[c(1,11)],
    fitted.se = c(
      emmeans::emmeans(object = cell_area_glm, ~ "Genotype",
                       type = 'response') |>
        as.data.frame() |>
        dplyr::filter(Genotype == "WT") |>
        dplyr::select(SE) |>
        unlist() |> as.numeric(),
      emmeans::emmeans(object = cell_area_glm, ~ "Genotype",
                       type = 'response') |>
        as.data.frame() |>
        dplyr::filter(Genotype == "MUT") |>
        dplyr::select(SE) |>
        unlist() |> as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

  ggplot(aes(
    x = Genotype,
    y = fitted.means,
    color = Genotype,
    fill = Genotype,
    alpha = 0.5))+
  geom_bar(stat = 'identity') +
  geom_errorbar(aes(x = Genotype,
                    ymin = y_min,
                    ymax = y_max), width = 0.25, inherit.aes = T) +
  geom_point(data = cell_area_glm$model$Genotype |>
               as.data.frame() |>
               dplyr::rename(Genotype = `cell_area_glm$model$Genotype`) |>
               dplyr::mutate(
                 fitted.means = c(
                   cell_area_glm$fitted.values |> unlist() |> as.numeric()),
                 fitted.se = c(
                   rep(summary(cell_area_glm)$coeff[,2][2] |>
                         unlist() |>
                         as.numeric(),
                       10),
                   rep(summary(cell_area_glm)$coeff[,2][1] |>
                         unlist() |>
                         as.numeric(),
                       13)),
                 avg_cell_body_area = c(
                   as.numeric(cell_area_glm$model$`as.numeric(Cell_Body_Area)`
                 ))) |>
               dplyr::group_by(Genotype) |>
               dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
               dplyr::ungroup(),
             aes(x = Genotype, y = avg_cell_body_area)) +
  labs(title = 'Hippocampal Neuron Cell Body Area (glm-Gamma)',
       x = 'Genotype',
       y = bquote('Cell Body Area '(mu*m^2))) +
  theme_bw() +
  theme(title = element_text(face = 'bold', size = 12.5),
        axis.title = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 11),
        panel.grid = element_blank(),
        legend.text = element_text(face = 'bold', size = 10)
  ) +
  guides(alpha = 'none') +
  scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  geom_segment(x = 1, xend = 2, y = 385, yend = 385, color = 'black', size = 1) +
  # geom_signif()
  geom_text(
    aes(label = "N.S.",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_acidity_lm)$fstatistic[1],
        #                 summary(puncta_acidity_lm)$fstatistic[2],
        #                 summary(puncta_acidity_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |> unlist() |> as.numeric(), 4)
        #                      ),
        fontface = 'bold'
        ),
    size = 7,
    color = 'black',
    x = 1.5,
    y = 412)
```

### Results Tables {.tabset .tabset-pills .tabset-fade}

#### Tidied Puncta Data

```{r Puncta Data, include = T, message = F, warning = F, echo = F}
DT::datatable(Puncta_data %>%
                dplyr::rename_with(.cols = dplyr::contains("_"), ~gsub(.x, pattern = '^(.+?)(.+$)', replacement = '`\\1\\2`')) %>%
                dplyr::rename_with(.cols = dplyr::contains('_'),~gsub(.x, pattern = '_', replacement = ' ')) %>%
                dplyr::rename_with(.cols = dplyr::contains("Puncta Count"), ~gsub(.x, pattern = 'Puncta Count', replacement = '#')) %>%
                dplyr::mutate(across(c(4:ncol(.)), ~ as.numeric(.x))) %>%
                dplyr::mutate(across(c(4:ncol(.)), ~ round(.x, digits = 4))), width = '50%')
```

```{r Export puncta data, eval = F, include=F, warning =F, message =F, echo = F}
write.table(
  Puncta_data,
  'C:\\Users\\Erik\\Desktop\\Programming\\R\\Bio\\Endo\\tidied_puncta_data.csv',
  row.names = F,
  col.names = T,
  sep = ',')
```

```{r Gather Stats Results, include = T, message = F, warning = F, echo = F}
puncta_acidity_lm_results <- puncta_acidity_lm |>
  broom::tidy() |>
  dplyr::full_join(
    puncta_acidity_lm |>
      broom::glance()
    )

puncta_area_lm_results <- puncta_area_lm |>
  broom::tidy() |>
  dplyr::full_join(
    puncta_area_lm |> 
      broom::glance()
    )

puncta_n_lm_results <- puncta_n_lm |> 
  broom::tidy() |>
  dplyr::full_join(
    puncta_n_lm |> broom::glance()
    )

cell_area_lm_results <- cell_area_lm |> 
  broom::tidy() |>
  dplyr::full_join(
    cell_area_lm |> 
      broom::glance()
    )

cell_area_glm_results <- cell_area_glm |> 
  broom::tidy() |> 
  dplyr::mutate(null.deviance = NA) |>
  dplyr::full_join(cell_area_glm |> broom::glance())


lm_results <- puncta_acidity_lm_results |> 
  dplyr::mutate(target_var = "puncta_acidity") |>
  dplyr::full_join(puncta_area_lm_results |> 
                     dplyr::mutate(target_var = 'puncta_area')) |>
  dplyr::full_join(puncta_n_lm_results |> 
                     dplyr::mutate(target_var = 'puncta_n')) |>
  dplyr::full_join(cell_area_lm_results |> 
                     dplyr::mutate(target_var = 'cell_body_area_lm')) |>
  dplyr::full_join(cell_area_glm_results |> 
                     dplyr::mutate(target_var = 'cell_body_area_glm')) |>
  dplyr::relocate(target_var, .before = 1)
```

#### Table of Stats

```{r Model results table, include = T, message = F, warning = F, echo = F}
DT::datatable(lm_results %>%
                dplyr::mutate(across(c(3:ncol(.)), ~as.numeric(.x))) %>% 
                dplyr::mutate(across(c(3:ncol(.)), ~round(.x, digits = 5))), width = '50%')
```

#### Table of Predicted Values

```{r Gather predictions weights and residuals, eval = T, include = F, message = F, warning=F, echo = T}
lm_results_preds_and_resids <- puncta_acidity_lm |> 
  broom::augment() |> 
  dplyr::mutate(target_var = 'puncta_acidity') |>
  dplyr::full_join(puncta_area_lm |> 
                     broom::augment() |> 
                     dplyr::mutate(target_var = 'puncta_area')) |>
  dplyr::full_join(puncta_n_lm |> 
                     broom::augment() |> 
                     dplyr::mutate(target_var = 'puncta_n')) |>
  dplyr::full_join(cell_area_lm |> 
                     broom::augment() |> 
                     dplyr::mutate(target_var = 'cell_body_area_lm') |> 
                     dplyr::rename(Cell_Body_Area_lm = Cell_Body_Area)) |>
  dplyr::full_join(cell_area_glm |> 
                     broom::augment() |> 
                     dplyr::mutate(
                       target_var = 'cell_body_area_glm',
                       `as.numeric(Cell_Body_Area)` = as.character(
                         `as.numeric(Cell_Body_Area)`)
                       ) |> 
                     dplyr::rename(
                       Cell_Body_Area_glm = `as.numeric(Cell_Body_Area)`
                       )
                   ) |>
  dplyr::relocate(1, .after = target_var) |>
  dplyr::relocate(.resid, .after = .fitted)
```

```{r Predictions in table, eval = T, include = T, message = F, warning = F, echo = T}
DT::datatable(lm_results_preds_and_resids %>%
                dplyr::mutate(across(c(2:ncol(.),-9), ~ as.numeric(.x))) %>%
                dplyr::mutate(across(c(2:ncol(.),-9), ~ round(.x, digits = 4))), width = '50%')
```

#### Shapiro Results Table

```{r Gather shapiro results, eval = T, include = F, message = F, warning = F, echo = T}
shapiro_test_results <- shapiro_puncta_acidity |>
  broom::tidy() |>
  dplyr::full_join(shapiro_puncta_acidity |>
                     broom::glance()
                   ) |>
  dplyr::mutate(target_var = 'puncta_acidity') |>
  dplyr::full_join(shapiro_cell_area |>
                     broom::tidy() |>
                     dplyr::full_join(shapiro_cell_area |>
                                        broom::glance()
                                      ) |>
                     dplyr::mutate(target_var = 'cell_body_area')
                   ) |>
  dplyr::full_join(shapiro_puncta_area |>
                     broom::tidy() |>
                     dplyr::full_join(shapiro_puncta_area |>
                                        broom::glance() |>
                                        dplyr::mutate(
                                          target_var = 'puncta_area'))) |>
  dplyr::full_join(shapiro_puncta_n |>
                     broom::tidy() |>
                     dplyr::full_join(shapiro_puncta_n |>
                                        broom::glance()) |> dplyr::mutate(
                                          target_var = 'puncta_n'))
```

```{r Shapiro results table, include = T, message = F, warning = F, echo = T}
DT::datatable(shapiro_test_results %>%
                dplyr::mutate(across(c(1:2), ~ round(.x, digits = 4))), width = '50%')
```

