---
title: "FIREpHly"
author: "Erik Larsen"
date: "2025-01-22"
output:
  html_document:
    toc: true
    fig_width: 10
    fig_height: 10
  pdf_document:
    fig_width: 10
    fig_height: 10
    latex_engine: xelatex
  md_document:
    variant: gfm
vignette: >
  %\VignetteIndexEntry{IPMS vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 10,
  dev = c("png", "pdf"),
  fig.path = "figures/"
)
```

### Overview

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('### Overview {.tabset .tabset-pills .tabset-fade}\n')
}
```

This markdown was developed to formally document the data analysis of FIRE-pHly 
data for **Dr. Martha Bhattacharya's lab** at the **University of Arizona** for
the endolysosomal paper under revision (2025-02-10).

Until an image is built, the `R version` used was **R 4.3.2** with the
packages installed below

### Set up Environment

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('### Set up Environment {.tabset .tabset-pills .tabset-fade}\n')
}
```

#### Attach packages

```{r Attach packages, include = T, message = F, warning = F, echo = T}
packages <- c(#'TMEM',
               'Endo',
              'tidyverse',
              'ggplot2',
              'ggtext',
              # 'readr',
              'ggsignif',
              'emmeans',
              'broom'
              )
for ( package in packages ) {
  if (!require(package, character.only = T)) {
    install.packages(package)
    library(package, character.only = T)
  }
}
```

### Import FIRE-pHly Data

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('### Import FIRE-pHly Data {.tabset .tabset-pills .tabset-fade}\n')
}
```

<span style="color:black;font-size: 18px">Directly load the `tidied_puncta_data`</span>

```{r FIREpHly data load, include = T, message = F, warning = F, echo = T}
Endo::data(tidied_puncta_data)
Puncta_data <- tidied_puncta_data
rm(tidied_puncta_data)
```

<span style="color:black;font-size: 18px">Code chunks that clean the raw data
from separate Excel sheets into the data object, `tidied_puncta_data`, have been
included in the [R Markdown vignette](https://github.com/eriklarsen4/Endo/blob/dev/vignettes/FIREpHly.Rmd)</span>

### Visualize

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('### Visualize {.tabset .tabset-pills .tabset-fade}\n')
}
```

<span style="color:black;font-size: 16px">Investigate the distributions of measured variables</span>

#### Puncta Area Histogram

```{r Puncta_Area_Histogram_full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = Puncta_Area, col = Genotype, fill = Genotype, alpha = 0.5)) +
  ggplot2::geom_histogram(binwidth = 0.01) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Count\n(binwidth = 0.01)') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.85, 0.5),
        legend.title = ggplot2::element_text(face = 'bold', size = 10),
        legend.text = ggplot2::element_text(face = 'bold', size = 10)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area Histogram (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta_Area_Histogram_cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = Puncta_Area, col = Genotype, fill = Genotype, alpha = 0.5)) +
  ggplot2::geom_histogram(binwidth = 0.01) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Count\n(binwidth = 0.01)') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.85, 0.5),
        legend.title = ggplot2::element_text(face = 'bold', size = 10),
        legend.text = ggplot2::element_text(face = 'bold', size = 10)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area Density

```{r Puncta_Area_Density_full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = Puncta_Area, col = Genotype, fill = Genotype)) +
  ggplot2::geom_density(alpha =  0.5) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Area Density Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Density') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.80, 0.5),
        legend.title = ggplot2::element_text(face = 'bold', size = 11),
        legend.text = ggplot2::element_text(face = 'bold', size = 11)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area Density (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta_Area_Density_cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = Puncta_Area, col = Genotype, fill = Genotype)) +
  ggplot2::geom_density(alpha =  0.5) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Area Density Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Density') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.80, 0.5),
        legend.title = ggplot2::element_text(face = 'bold', size = 11),
        legend.text = ggplot2::element_text(face = 'bold', size = 11)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area Violin

```{r Puncta_Area_Violin, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = Puncta_Area, y = Genotype, color = Genotype, fill = Genotype)
         ) +
  ggplot2::geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), alpha = 0.2) +
  # ggplot2::geom_boxplot(inherit.aes = T,
  #              outlier.shape = 'triangle',
  #              outlier.alpha = 0.5, outlier.color = 'black', alpha = 0.5) +
  ggplot2::geom_jitter(aes(width = 0.1, alpha = 0.5, color = Genotype)) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       y = 'Genotype') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        panel.grid.major.y = ggplot2::element_blank(),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = 'none'
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Acidity Histogram

```{r Puncta_Acidity_Histogram_full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = GreenRed_Ratio, col = Genotype, fill = Genotype, alpha = 0.5)
         ) +
  ggplot2::geom_histogram(binwidth = 0.1) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Acidity Distributions',
       x = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       y = 'Count\n(binwidth = 0.1)') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.8, 0.5),
        legend.title = ggplot2::element_text(face = 'bold', size = 11),
        legend.text = ggplot2::element_text(face = 'bold', size = 11)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Acidity Histogram (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta_Acidity_Histogram_cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = GreenRed_Ratio, col = Genotype, fill = Genotype, alpha = 0.5)
         ) +
  ggplot2::geom_histogram(binwidth = 0.1) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Acidity Distributions',
       x = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       y = 'Count\n(binwidth = 0.1)') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.8, 0.5),
        legend.title = ggplot2::element_text(face = 'bold', size = 11),
        legend.text = ggplot2::element_text(face = 'bold', size = 11)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Acidity Density

```{r Puncta_Acidity_Density_full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = GreenRed_Ratio, col = Genotype, fill = Genotype)) +
  ggplot2::geom_density(alpha =  0.5) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Acidity Density Distributions',
       x = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       y = 'Density') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.80, 0.5),
        legend.title = ggplot2::element_text(face = 'bold', size = 11),
        legend.text = ggplot2::element_text(face = 'bold', size = 11)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Acidity Density (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta_Acidity_Density_cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num)) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = GreenRed_Ratio, col = Genotype, fill = Genotype)) +
  ggplot2::geom_density(alpha =  0.5) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Acidity Density Distributions',
       x = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       y = 'Density') +
  ggplot2::guides(col = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 10),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.80, 0.5),
        legend.title = ggplot2::element_text(face = 'bold', size = 11),
        legend.text = ggplot2::element_text(face = 'bold', size = 11)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area and Acidity Contour

```{r Puncta_Area_and_Acidity_2d_density_full, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 5}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num),
                Puncta_Area_to_Cell_Body_Area_Ratio = Puncta_Area/Cell_Body_Area
                ) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = Puncta_Area,
             y = GreenRed_Ratio, col = Genotype, fill = Genotype)) +
  ggplot2::geom_point(alpha = 0.1, size = 2.5) +
  ggplot2::geom_density_2d(contour_var = 'density', linewidth = 1, alpha = 0.7) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Acidity and Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       #(', '&mu;m<sup>2</sup>', ')',
       y = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       fill = 'Genotype') +
  ggplot2::guides(fill = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 10),
        axis.text = ggplot2::element_text(face = 'bold', size = 9),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.80, 0.6),
        legend.title = ggplot2::element_text(face = 'bold', size = 9),
        legend.text = ggplot2::element_text(face = 'bold', size = 9)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```

#### Puncta Area and Acidity Contour (zoom)

<span style="color:black;font-size: 16px">Crop to better-discern differences in the majority of the data</span>

```{r Puncta_Area_and_Acidity_2d_density_cropped, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 5}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(GreenRed_Ratio = as.numeric(GreenRed_Ratio),
                Puncta_Area = as.numeric(Puncta_Area),
                Cell_Body_Area = as.numeric(Cell_Body_Area),
                cell_num = as.numeric(cell_num),
                Puncta_Area_to_Cell_Body_Area_Ratio = Puncta_Area/Cell_Body_Area
                ) |>
  dplyr::filter(GreenRed_Ratio < 25) |>
  dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype) |>
  ggplot2::ggplot(aes(x = Puncta_Area,
             y = GreenRed_Ratio, col = Genotype, fill = Genotype)) +
  ggplot2::geom_point(alpha = 0.1, size = 2.5) +
  ggplot2::geom_density_2d(contour_var = 'density', linewidth = 1, alpha = 0.7) +
  ggplo2::labs(title = 'Hippocampal Neuron Puncta Acidity and Area Distributions',
       x = paste0('Neuronal Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       #(', '&mu;m<sup>2</sup>', ')',
       y = 'Neuronal Puncta Average Green:Red Fluorescence Intensity (a.u.)',
       fill = 'Genotype') +
  ggplot2::guides(fill = 'none', alpha = 'none')+
  ggplot2::theme_bw() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title.x = ggplot2::element_markdown(face = 'bold', size = 11),
        axis.title.y = ggplot2::element_text(face = 'bold', size = 10),
        axis.text = ggplot2::element_text(face = 'bold', size = 9),
        axis.ticks = ggplot2::element_line(color = 'black'),
        panel.grid.minor = ggplot2::element_blank(),
        legend.position = c(0.80, 0.6),
        legend.title = ggplot2::element_text(face = 'bold', size = 9),
        legend.text = ggplot2::element_text(face = 'bold', size = 9)
  ) +
  ggplot2::scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  ggplot2::scale_fill_manual(values = c("navy", "darkgoldenrod3"))
```


### Statistics

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('### Statistics {.tabset .tabset-pills .tabset-fade}\n')
}
```

<span style="color:black;font-size: 16px">Perform weighted linear regressions on puncta data</span>  

<span style="color:black;font-size: 18px">It appropriately accounts for:</span>  

* <span style="color:black;font-size: 16px">experimenter bias</span>  
* <span style="color:black;font-size: 16px">inter-mouse variability</span>  
* <span style="color:black;font-size: 16px">(genotypic) inter-puncta variability</span>

#### Puncta Acidity

```{r Puncta Acidity wlm, include = T, message = F, warning = F, echo = F}
Puncta_avg_acidity <- Puncta_data |>
  dplyr::mutate(genotype_puncta_n = NA_real_, .after = Puncta_ID) |>
  dplyr::group_by(Genotype) |>
  dplyr::mutate(
    genotype_puncta_n = length(Puncta_ID)) |> # determine puncta_n per genotype
  dplyr::ungroup() |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::mutate(
    mouse_puncta_w = (length(Puncta_ID)/genotype_puncta_n)*10
    ) |> # give a "mouse" weight (around fractions of a whole mouse)
  dplyr::ungroup() |>
  dplyr::distinct(
    Genotype,
    cell_num,
    genotype_puncta_n,
    mouse_puncta_w,
    Puncta_Count,
    Cell_Avg_Puncta_GreenRedRatio)

puncta_acidity_lm <- lm(
  data = Puncta_avg_acidity,
  formula = Cell_Avg_Puncta_GreenRedRatio ~ Genotype,
  weights = mouse_puncta_w)

summary(puncta_acidity_lm)
```

<span style="color:navy;font-size: 18px">Strong significant difference between genotypes
(mutant more alkaline)</span>

<span style="color:black;font-size: 16px">Check shaprio-wilk</span>

```{r Puncta Acidity Shapiro, include = T, message = F, warning = F, echo = F}
## test for normality violations
shapiro_puncta_acidity <- shapiro.test(
  summary(puncta_acidity_lm)$residuals |> as.numeric())

shapiro.test(summary(puncta_acidity_lm)$residuals |> as.numeric())
```
<span style="color:black;font-size: 18px">Not non-normal</span>

#### Puncta Area
```{r Puncta Area wlm, include = T, message = F, warning = F, echo = F}
Puncta_avg_area <- Puncta_data |>
  dplyr::mutate(genotype_puncta_n = NA_real_, .after = Puncta_ID) |>
  dplyr::group_by(Genotype) |>
  dplyr::mutate(
    genotype_puncta_n = length(Puncta_ID)) |> # determine puncta_n per genotype
  dplyr::ungroup() |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::mutate(mouse_puncta_w = (length(Puncta_ID)/genotype_puncta_n)*10,
                Cell_Avg_Puncta_Area = mean(as.numeric(Puncta_Area))
                ) |> # give a "mouse" weight (around fractions of a whole mouse)
  dplyr::ungroup() |>
  dplyr::distinct(
    Genotype,
    cell_num,
    genotype_puncta_n,
    mouse_puncta_w,
    Puncta_Count,
    Cell_Avg_Puncta_Area)

puncta_area_lm <- lm(
  Cell_Avg_Puncta_Area ~ Genotype,
  data = Puncta_avg_area,
  weights = mouse_puncta_w)

summary(puncta_area_lm)
```

<span style="color:black;font-size: 18px">No significant difference between genotypes in
auto-detected puncta in terms of their areas</span>

<span style="color:black;font-size: 16px">Check shapiro-wilk</span>

```{r Puncta Area Shapiro, include = T, message = F, warning = F, echo = F}
## test for normality violations
shapiro_puncta_area <- shapiro.test(
  summary(puncta_area_lm)$residuals |> as.numeric())

shapiro.test(summary(puncta_area_lm)$residuals |> as.numeric())
```

<span style="color:black;font-size: 18px">Not non-normal</span>

#### Puncta Number (wlm)
```{r Puncta Number wlm, include = T, message = F, warning = F, echo = F}
Puncta_n <- Puncta_data |>
  dplyr::mutate(genotype_puncta_n = NA_real_, .after = Puncta_ID) |>
  dplyr::group_by(Genotype) |>
  dplyr::mutate(genotype_puncta_n = length(Puncta_ID)) |>
  dplyr::ungroup() |>
  dplyr::mutate(mouse_puncta_w = (length(Puncta_ID)/genotype_puncta_n)*10) |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::mutate(puncta_n = n()) |>
  dplyr::ungroup() |>
  dplyr::distinct(Genotype, cell_num, puncta_n, mouse_puncta_w)

puncta_n_lm <- lm(
  data = Puncta_n,
  formula = puncta_n ~ Genotype,
  weights = mouse_puncta_w)

summary(puncta_n_lm)
```

<span style="color:black;font-size: 18px">No significant difference between genotypes</span>

#### Puncta Number (Welch's t)
```{r Puncta number Welchs t, include = T, message = F, warning = F, echo = T}
## more traditional Welch's t
t.test(
  x = c(Puncta_data |>
          dplyr::group_by(Genotype) |>
          dplyr::distinct(Puncta_Count) |>
          dplyr::ungroup() |>
          dplyr::filter(Genotype == "WT") |>
          dplyr::select(Puncta_Count) |>
          unlist() |> as.numeric()
),
y = c(Puncta_data |>
          dplyr::group_by(Genotype) |>
          dplyr::distinct(Puncta_Count) |>
          dplyr::ungroup() |>
          dplyr::filter(Genotype == "MUT") |>
          dplyr::select(Puncta_Count) |>
          unlist() |> as.numeric()
),
alternative = 'two.sided', var.equal = F
)
```
<span style="color:black;font-size: 18px">No significant difference between genotype-dependent
puncta number auto-detected by computer software</span>

<span style="color:black;font-size: 16px">Check shapiro-wilk</span>

```{r Puncta Number Shapiro, include = T, message = F, warning = F, echo = F}
## test for normality violations
shapiro_puncta_n <- shapiro.test(
  summary(puncta_n_lm)$residuals |> as.numeric())

shapiro.test(summary(puncta_n_lm)$residuals |> as.numeric())
```

<span style="color:black;font-size: 18px">Not non-normal</span>

#### Cell Body Area
```{r Cell Body Area lm, include = T, message = F, warning = F, echo = T}
  ## Welch's t test
t.test(x = c(Puncta_data |>
               dplyr::group_by(Genotype, cell_num) |>
               dplyr::distinct(Cell_Body_Area) |>
               dplyr::ungroup() |>
               dplyr::filter(Genotype == "WT") |>
               dplyr::select(Cell_Body_Area) |>
               unlist() |> as.numeric()
),
y = c(Puncta_data |>
        dplyr::group_by(Genotype, cell_num) |>
        dplyr::distinct(Cell_Body_Area) |>
        dplyr::ungroup() |>
        dplyr::filter(Genotype == "MUT") |>
        dplyr::select(Cell_Body_Area) |>
        unlist() |> as.numeric()
),
alternative = 'two.sided', var.equal = F)
```

<span style="color:darkred;font-size: 18px">Mutant cell bodies are significantly larger than
wild-type cell bodies; this is likely due to sampling bias and likely does not
relate to pH-dependent results since those are weighted by the number of puncta,
which is not significantly different</span>

<span style="color:black;font-size: 16px">Check shapiro-wilk</span>

```{r Cell Body Area Shapiro, include = T, message = F, warning = F, echo = T}
  ## Examine residuals
    ## extract from lm (~ same as Welch's t test)
cell_area_lm <- lm(data = Puncta_data |>
                     dplyr::group_by(Genotype, cell_num) |>
                     dplyr::distinct(Cell_Body_Area) |>
                     dplyr::ungroup(),
                   formula = Cell_Body_Area ~ Genotype)

  ## Shapiro.wilk
shapiro_cell_area <- shapiro.test(
  summary(cell_area_lm)$residuals |> as.numeric())

shapiro.test(summary(cell_area_lm)$residuals |> as.numeric())
```

<span style="color:darkred;font-size: 18px">Non-normal residuals, suggesting cell body size
difference is difficult to properly discern a significant difference due to
outliers or, more broadly, differently-distributed cell body areas. This is
obvious and, again, not necessarily relevant</span>

<span style="color:black;font-size: 16px">Significant. Show the residuals</span>

#### Cell Body Area residuals dist
```{r Cell_Body_Area_lm_residuals_dist, include = T, message = F, warning = F, echo = T, fig.width = 6, fig.height = 4}
  ## Cell Body area residuals distributions
Puncta_data |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::distinct(Cell_Body_Area) |>
  dplyr::ungroup() |>
  dplyr::mutate(Cell_Body_Area = as.numeric(Cell_Body_Area),
                resids = lm(data = Puncta_data |>
                              dplyr::group_by(Genotype, cell_num) |>
                              dplyr::distinct(Cell_Body_Area) |>
                              dplyr::ungroup(),
                            formula = as.numeric(Cell_Body_Area) ~ Genotype
                            )$residuals |> as.numeric()
                ) |>
  ggplot(aes(x = resids, y = Genotype, color = Genotype, fill = Genotype)) +
  geom_violin(alpha = 0.3) +
  stat_summary(fun.y = 'median',
               geom = 'point',
               color = 'black',
               size = 5,
               show.legend = FALSE) +
  guides(alpha = 'none') +
  geom_jitter(data = Puncta_data |>
                dplyr::group_by(Genotype, cell_num) |>
                dplyr::distinct(Cell_Body_Area) |>
                dplyr::ungroup() |>
                dplyr::mutate(
                  Cell_Body_Area = as.numeric(Cell_Body_Area),
                  resids = lm(data = Puncta_data |>
                                dplyr::group_by(Genotype, cell_num) |>
                                dplyr::distinct(Cell_Body_Area) |>
                                dplyr::ungroup(),
                              formula = as.numeric(Cell_Body_Area) ~ Genotype
                              )$residuals |> as.numeric()
                ),
              aes(x = resids,
                  y = Genotype), alpha = 1, width = 0.01, height = 0.1) +
  labs(title = 'Hippocampal Neuron Cell Body\nlm fit residual distributions',
       x = 'lm fit residuals',
       y = 'Genotype') +
  theme_bw() +
  theme(title = element_text(face = 'bold', size = 13),
        axis.title = element_text(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 11),
        panel.grid = element_blank(),
        legend.text = element_text(face = 'bold', size = 10)
  ) +
  guides(alpha = 'none') +
  scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  scale_fill_manual(values = c('navy', 'darkgoldenrod3'))
```

<span style="color:darkred;font-size: 18px">The residual average cell body size for each mouse is
not the same between genotypes</span>

<span style="color:black;font-size: 16px">What's the shape of the dv, taking both genotypes into account?</span>

#### Cell Body Area density
```{r Cell_Body_Area_density, include = T, message = F, warning = F, echo = T}
Puncta_data |> dplyr::distinct(Cell_Body_Area) |> 
  ggplot(aes(x = as.numeric(Cell_Body_Area))) +
  geom_density(fill = 'black', alpha = 0.5) +
  labs(x = expression(paste("Cell Body Area (", mu, m^2, ")")))
```

<span style="color:darkred;font-size: 18px">Negative binomial. Unsurprising, particularly for
small sample sizes; the borderline difference suggests the sample sizes are
nearly powerful enough</span>


<span style="color:black;font-size: 18px">Still, consider alternatives:</span> 

* <span style="color:black;font-size: 16px">a `glm` with an **inverse-Gaussian fit** (probably the appropriate alternative)</span>  
* <span style="color:black;font-size: 16px">`Wilcoxon-ranked sum (Mann-Whitney)` (probably the next appropriate alternative)</span>  
* <span style="color:black;font-size: 16px">`Komolgorov-Smirnov`</span>  

<span style="color:black;font-size: 16px">First, the `glm`</span>
```{r Cell Body Area glm, include = T, message = F, warning = F, echo = T}
  ## GLM
cell_area_glm <- glm(data = Puncta_data |>
                       dplyr::group_by(Genotype, cell_num) |>
                       dplyr::distinct(Cell_Body_Area) |>
                       dplyr::ungroup(),
                     formula = as.numeric(Cell_Body_Area) ~ Genotype,
                     family = 'Gamma')

summary(cell_area_glm)
```

<span style="color:navy;font-size: 18px">No significant difference between genotypes when
using a `glm` with an **inverse-Gaussian** to account for different (non-normal)
distribution shapes</span>


<span style="color:black;font-size: 18px">What about the `MannWhitney`/`Wilcoxon-ranked sum`?</span>    

* <span style="color:black;font-size: 16px">Compares the medians of two groups because the data violate assumptions
(such as normality, as in this case)</span>  
* <span style="color:black;font-size: 16px">often, "outliers" skew distributions and/or unequal variances between groups</span>

```{r Cell Body Area MannWhitney, include = T, message = F, warning = F, echo = T}
wilcox.test(data = Puncta_data |>
              dplyr::group_by(Genotype, cell_num) |>
              dplyr::distinct(Cell_Body_Area) |>
              dplyr::ungroup(),
            as.numeric(Cell_Body_Area) ~ Genotype)
```

<span style="color:darkred;font-size: 18px">Significant difference between the genotypes. Not
sure how this contributes to pH difference in endolysosomes marked by the
FIREpHly marker (Lamp1)</span>


<span style="color:black;font-size: 18px">What about the `Kolmogorov-Smirnov`?</span>

* <span style="color:black;font-size: 16px">`KS test` does *not* assume the sample means of two groups come from the same 
distribution (a more conservative, non-parametric test)</span>


<span style="color:black;font-size: 16px">We assume this in genetic studies (hence the `glm`)</span>

```{r Cell Body Area KS test, include = T, message = F, warning = F, echo = T}
  ## KS
ks.test(x = c(Puncta_data |>
                dplyr::group_by(Genotype, cell_num) |>
                dplyr::distinct(Cell_Body_Area) |>
                dplyr::ungroup() |>
                dplyr::filter(Genotype == "WT") |>
                dplyr::select(Cell_Body_Area) |>
                unlist() |> as.numeric()
        ),
        y = c(Puncta_data |>
                dplyr::group_by(Genotype, cell_num) |>
                dplyr::distinct(Cell_Body_Area) |>
                dplyr::ungroup() |>
                dplyr::filter(Genotype == "MUT") |>
                dplyr::select(Cell_Body_Area) |>
                unlist() |> as.numeric()
        ),
        alternative = 'two.sided')
```

<span style="color:darkred;font-size: 18px">Significant difference between the genotypes.</span>


<span style="color:black;font-size: 18px">Defer to GraphPad Prism statistical results, though I am satisfied by the `glm`
with the inverse-Gaussian fit; again, this is a minor issue, though I will note
it here</span>

<span style="color:black;font-size: 16px">Is there a relationship between cell body size and puncta size?</span>
<span style="color:black;font-size: 16px">Do the genotypes differ? (see below)</span>

#### Cell Body Area vs Avg Puncta Area scatter w/fit

```{r Cell_Body_Area_Scatter_w_lm_fit, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
Puncta_data |>
  as.data.frame() |>
  dplyr::mutate(
    GreenRed_Ratio = as.numeric(GreenRed_Ratio),
    Puncta_Area = as.numeric(Puncta_Area),
    Cell_Body_Area = as.numeric(Cell_Body_Area),
    cell_num = as.numeric(cell_num),
    Puncta_Area_to_Cell_Body_Area_Ratio = Puncta_Area/Cell_Body_Area) |>
  # dplyr::filter(GreenRed_Ratio < 25) |>
  # dplyr::filter(Puncta_Area < 2) |>
  dplyr::group_by(Genotype, cell_num) |>
  dplyr::mutate(mean_Puncta_Area = mean(Puncta_Area)) |>
  dplyr::distinct(Cell_Body_Area, mean_Puncta_Area) |>
  ggplot(aes(x = Cell_Body_Area,
             y = mean_Puncta_Area,
             col = Genotype,
             fill = Genotype)) +
  geom_point(aes(x = Cell_Body_Area,
                 y = mean_Puncta_Area,
                 col = Genotype,
                 fill = Genotype), size = 3) +
  labs(title = 'Hippocampal Neuron Puncta Area and Cell Body Area',
       x = paste0('Neuronal Cell Body Area (', '&mu;m<sup>2</sup>', ')'),
       y = paste0('Cell Average Puncta Area (', '&mu;m<sup>2</sup>', ')'),
       fill = 'Genotype') +
  guides(alpha = 'none')+
  theme_bw() +
  theme(plot.title = element_text(face = 'bold', size = 13),
        axis.title.x = element_markdown(face = 'bold', size = 11),
        axis.title.y = element_markdown(face = 'bold', size = 11),
        axis.text = element_text(face = 'bold', size = 9),
        axis.ticks = element_line(color = 'black'),
        panel.grid.minor = element_blank(),
        legend.title = element_text(face = 'bold', size = 11),
        legend.text = element_text(face = 'bold', size = 11)
  ) +
  scale_color_manual(values = c("navy", "darkgoldenrod3")) +
  scale_fill_manual(values = c("navy", "darkgoldenrod3")) +
  scale_y_continuous(breaks = c(0.400, 0.500, 0.600, 0.700, 0.800),
                     labels = c(0.400, 0.500, 0.600, 0.700, 0.800)) +
  geom_smooth(
    aes(x = Cell_Body_Area,
        y = Puncta_data |>
          as.data.frame() |>
          dplyr::mutate(
            GreenRed_Ratio = as.numeric(GreenRed_Ratio),
            Puncta_Area = as.numeric(Puncta_Area),
            Cell_Body_Area = as.numeric(Cell_Body_Area),
            cell_num = as.numeric(cell_num),
            Puncta_Area_to_Cell_Body_Area_Ratio = Puncta_Area/Cell_Body_Area
            ) |>
          # dplyr::filter(GreenRed_Ratio < 25) |>
          # dplyr::filter(Puncta_Area < 2) |>
          dplyr::group_by(Genotype, cell_num) |>
          dplyr::mutate(mean_Puncta_Area = mean(Puncta_Area)) |>
          dplyr::distinct(Cell_Body_Area, mean_Puncta_Area) |>
          dplyr::ungroup() |>
          dplyr::select(mean_Puncta_Area) |>
          unlist() |> as.numeric()
        ),
    method = 'lm', se = F)
```

#### Cell Body Area vs Avg Puncta Area summary

```{r Cell Body and Genotype Do Not Predict Avg Puncta Area, include = T, message = F, warning = F, echo = T}
summary(lm(data = Puncta_data |>
     as.data.frame() |>
     dplyr::mutate(
       Puncta_Area = as.numeric(Puncta_Area),
       Cell_Body_Area = as.numeric(Cell_Body_Area),
       cell_num = as.numeric(cell_num)) |>
     dplyr::group_by(Genotype, cell_num) |>
     dplyr::mutate(mean_Puncta_Area = mean(Puncta_Area)) |>
     dplyr::distinct(Cell_Body_Area, mean_Puncta_Area) |>
     dplyr::ungroup(),
   
   formula = mean_Puncta_Area ~ 
     Cell_Body_Area*Genotype
     ))
```

<span style="color:black;font-size: 18px">No clear relationship between average puncta area
and cell body area between the two genotypes (though, mutants have larger cell
bodies)</span>

<span style="color:black;font-size: 16px">Thus, mutant endolysosomal cell bodies may be significantly larger; however,
there is no difference in the puncta size between the two genotypes</span>

### Stats Plots

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('### Stats Plots {.tabset .tabset-pills .tabset-fade}\n')
}
```

<span style="color:black;font-size: 16px">Visualize the statistical test results</span>

#### Puncta Acidity Bar

```{r Puncta_Acidity_Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
puncta_acidity_lm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `puncta_acidity_lm$model$Genotype`) |>
  dplyr::mutate(
                fitted.means = c(puncta_acidity_lm$fitted.values |>
                                   unlist() |>
                                   as.numeric()
                                 )[c(1,14)],
                fitted.se = c(summary(puncta_acidity_lm)$coeff[,2][2] |>
                                unlist() |>
                                as.numeric(),
                              summary(puncta_acidity_lm)$coeff[,2][1] |>
                                unlist() |>
                                as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

ggplot2::ggplot(aes(
  x = Genotype,
  y = fitted.means,
  color = Genotype,
  fill = Genotype,
  alpha = 0.5))+
  ggplot2::geom_bar(stat = 'identity') +
  ggplot2::geom_errorbar(aes(x = Genotype, ymin = y_min, ymax = y_max), width = 0.25) +
  ggplot2::geom_point(data = puncta_acidity_lm$model$Genotype |>
                as.data.frame() |>
                dplyr::rename(Genotype = `puncta_acidity_lm$model$Genotype`) |>
                dplyr::mutate(
                  fitted.means = c(
                    puncta_acidity_lm$fitted.values |> unlist() |> as.numeric()),
                  fitted.se = c(
                    rep(
                      summary(puncta_acidity_lm)$coeff[,2][2] |>
                        unlist() |>
                        as.numeric(),
                      10),
                    rep(
                      summary(puncta_acidity_lm)$coeff[,2][1] |>
                        unlist() |>
                        as.numeric(),
                      13)),
                  avg_gr_ratio = c(
                    as.numeric(puncta_acidity_lm$model$Cell_Avg_Puncta_GreenRedRatio)
                    )) |>
                dplyr::group_by(Genotype) |>
                dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
                dplyr::ungroup(),
              aes(x = Genotype, y = avg_gr_ratio)) +
  ggplot2::labs(title = 'Hippocampal Neuron Puncta Acidity',
       x = 'Genotype',
       y = 'Weighted Cell Average Puncta Acidity (a.u.)') +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 11),
        panel.grid = ggplot2::element_blank(),
        legend.text = ggplot2::element_text(face = 'bold', size = 10)
        ) +
  ggplot2::guides(alpha = 'none') +
  ggplot2::scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::geom_segment(x = 1, xend = 2, y = 2, yend = 2, color = 'black', size = 1) +
  # ggplot2::geom_signif()
  ggplot2::geom_text(
    aes(label = "**",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_acidity_lm)$fstatistic[1],
        #                 summary(puncta_acidity_lm)$fstatistic[2],
        #                 summary(puncta_acidity_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |> unlist() |> as.numeric(), 4)
        #        ),
        fontface = 'bold'
        ),
    size = 7,
    color = 'black',
    x = 1.5,
    y = 2.1)
```

#### Puncta Area Bar

```{r Puncta_Area_Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
## puncta area
puncta_area_lm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `puncta_area_lm$model$Genotype`) |>
  dplyr::mutate(
    fitted.means = c(puncta_area_lm$fitted.values |> unlist() |> as.numeric())[c(1,14)],
    fitted.se = c(summary(puncta_area_lm)$coeff[,2][2] |> unlist() |> as.numeric(),
                  summary(puncta_area_lm)$coeff[,2][1] |> unlist() |> as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

  ggplot2::ggplot(aes(
    x = Genotype,
    y = fitted.means,
    color = Genotype,
    fill = Genotype,
    alpha = 0.5))+
  ggplot2::geom_bar(stat = 'identity') +
  ggplot2::geom_errorbar(aes(x = Genotype, ymin = y_min, ymax = y_max), width = 0.25) +
  ggplot2::geom_point(data = puncta_area_lm$model$Genotype |>
               as.data.frame() |>
               dplyr::rename(Genotype = `puncta_area_lm$model$Genotype`) |>
               dplyr::mutate(
                 fitted.means = c(
                   puncta_area_lm$fitted.values |> unlist() |> as.numeric()),
                 fitted.se = c(
                   rep(
                     summary(puncta_area_lm)$coeff[,2][2] |>
                       unlist() |>
                       as.numeric(), 
                     10),
                   rep(
                     summary(puncta_area_lm)$coeff[,2][1] |>
                       unlist() |>
                       as.numeric(),
                     13)),
                 avg_puncta_area = c(
                   as.numeric(puncta_area_lm$model$Cell_Avg_Puncta_Area)
                 )) |>
               dplyr::group_by(Genotype) |>
               dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
               dplyr::ungroup(),
             aes(x = Genotype, y = avg_puncta_area)) +
  ggplot2::labs(title = 'Hippocampal Neuron Puncta Area',
       x = 'Genotype',
       y = bquote('Weighted Cell Average Puncta Area '(mu*m^2)),
       ) +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 11),
        panel.grid = ggplot2::element_blank(),
        legend.text = ggplot2::element_text(face = 'bold', size = 10)
  ) +
  ggplot2::guides(alpha = 'none') +
  ggplot2::scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::geom_segment(x = 1, xend = 2, y = 0.8, yend = 0.8, color = 'black', size = 1) +
  # ggplot2::geom_signif()
  ggplot2::geom_text(
    aes(label = "N.S.",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_acidity_lm)$fstatistic[1],
        #                 summary(puncta_acidity_lm)$fstatistic[2],
        #                 summary(puncta_acidity_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |> 
        #                unlist() |> 
        #                as.numeric(), 
        #              4)
        #        ),
        fontface = 'bold'
  ),
  size = 7,
  color = 'black',
  x = 1.5,
  y = 0.85)
```

#### Puncta Number Bar

```{r Puncta_Number_Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
puncta_n_lm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `puncta_n_lm$model$Genotype`) |>
  dplyr::mutate(
    fitted.means = c(puncta_n_lm$fitted.values |>
                       unlist() |>
                       as.numeric()
                     )[c(1,14)],
    fitted.se = c(summary(puncta_n_lm)$coeff[,2][2] |>
                    unlist() |>
                    as.numeric(),
                  summary(puncta_n_lm)$coeff[,2][1] |>
                    unlist() |>
                    as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

  ggplot2::ggplot(aes(
    x = Genotype,
    y = fitted.means,
    color = Genotype,
    fill = Genotype,
    alpha = 0.5))+
  ggplot2::geom_bar(stat = 'identity') +
  ggplot2::geom_errorbar(aes(x = Genotype, ymin = y_min, ymax = y_max), width = 0.25) +
  ggplot2::geom_point(data = puncta_n_lm$model$Genotype |>
               as.data.frame() |>
               dplyr::rename(Genotype = `puncta_n_lm$model$Genotype`) |>
               dplyr::mutate(
                 fitted.means = c(puncta_n_lm$fitted.values |> unlist() |> as.numeric()),
                 fitted.se = c(
                   rep(summary(puncta_n_lm)$coeff[,2][2] |>
                         unlist() |>
                         as.numeric(),
                       10),
                   rep(summary(puncta_n_lm)$coeff[,2][1] |>
                         unlist() |>
                         as.numeric(),
                       13)),
                 avg_puncta_n = c(as.numeric(puncta_n_lm$model$puncta_n)
                 )) |>
               dplyr::group_by(Genotype) |>
               dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
               dplyr::ungroup(),
             aes(x = Genotype, y = avg_puncta_n)) +
  ggplot2::labs(title = 'Hippocampal Neuron Puncta Number',
       x = 'Genotype',
       y = 'Weighted Cell Average Puncta Number',
  ) +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 13),
        axis.title = ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::element_text(face = 'bold', size = 11),
        panel.grid = ggplot2::element_blank(),
        legend.text = ggplot2::element_text(face = 'bold', size = 10)
  ) +
  ggplot2::guides(alpha = 'none') +
  ggplot2::scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::geom_segment(x = 1, xend = 2, y = 30, yend = 30, color = 'black', size = 1) +
  # ggplot2::geom_signif()
  ggplot2::geom_text(
    aes(label = "N.S.",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_n_lm)$fstatistic[1],
        #                 summary(puncta_n_lm)$fstatistic[2],
        #                 summary(puncta_n_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |> unlist() |> as.numeric(), 4)
        #                      ),
        fontface = 'bold'
  ),
  size = 7,
  color = 'black',
  x = 1.5,
  y = 32)
```

#### Cell Body Area Bar (Welch's t)

```{r Cell_Body_Area_Welch_Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
cell_area_lm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `cell_area_lm$model$Genotype`) |>
  dplyr::mutate(
    fitted.means = c(
      cell_area_lm$fitted.values |> unlist() |> as.numeric())[c(1,14)],
    fitted.se = c(
      summary(cell_area_lm)$coeff[,2][2] |> unlist() |> as.numeric(),
      summary(cell_area_lm)$coeff[,2][1] |> unlist() |> as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

  ggplot2::ggplot2::ggplot(aes(
    x = Genotype,
    y = fitted.means,
    color = Genotype,
    fill = Genotype,
    alpha = 0.5))+
  ggplot2::ggplot2::geom_bar(stat = 'identity') +
  ggplot2::ggplot2::geom_errorbar(aes(x = Genotype, ymin = y_min, ymax = y_max), width = 0.25) +
  ggplot2::ggplot2::geom_point(data = cell_area_lm$model$Genotype |>
               as.data.frame() |>
               dplyr::rename(Genotype = `cell_area_lm$model$Genotype`) |>
               dplyr::mutate(
                 fitted.means = c(
                   cell_area_lm$fitted.values |> unlist() |> as.numeric()),
                 fitted.se = c(
                   rep(summary(cell_area_lm)$coeff[,2][2] |>
                         unlist() |>
                         as.numeric(),
                       10),
                   rep(summary(cell_area_lm)$coeff[,2][1] |>
                         unlist() |>
                         as.numeric(),
                       13)),
                 avg_cell_body_area = c(
                   as.numeric(cell_area_lm$model$Cell_Body_Area)
                 )) |>
               dplyr::group_by(Genotype) |>
               dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
               dplyr::ungroup(),
             aes(x = Genotype, y = avg_cell_body_area)) +
  ggplot2::ggplot2::labs(title = "Hippocampal Neuron Cell Body Area (Welch's t)",
       x = 'Genotype',
       y = bquote('Cell Body Area '(mu*m^2))) +
  ggplot2::ggplot2::theme_bw() +
  ggplot2::ggplot2::theme(title = ggplot2::ggplot2::element_text(face = 'bold', size = 13),
        axis.title = ggplot2::ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::ggplot2::element_text(face = 'bold', size = 11),
        panel.grid = ggplot2::ggplot2::element_blank(),
        legend.text = ggplot2::ggplot2::element_text(face = 'bold', size = 10)
  ) +
  ggplot2::ggplot2::guides(alpha = 'none') +
  ggplot2::ggplot2::scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::ggplot2::scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::ggplot2::geom_segment(x = 1, xend = 2, y = 400, yend = 400, color = 'black', size = 1) +
  # ggplot2::geom_signif()
  ggplot2::ggplot2::geom_text(
    aes(label = "*",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_acidity_lm)$fstatistic[1],
        #                 summary(puncta_acidity_lm)$fstatistic[2],
        #                 summary(puncta_acidity_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |>
        #                unlist() |>
        #                as.numeric(),
        #              4)
        #        ),
        fontface = 'bold'
        ),
    size = 7,
    color = 'black',
    x = 1.5,
    y = 410)
```

#### Cell Body Area Bar (glm)

```{r Cell_Body_Area_Gamma_Bar, include = T, message = F, warning = F, echo = F, fig.width = 6, fig.height = 4}
cell_area_glm$model$Genotype |>
  as.data.frame() |>
  dplyr::slice(c(1,14)) |>
  dplyr::rename(Genotype = `cell_area_glm$model$Genotype`) |>
  dplyr::mutate(
    fitted.means = c(
      cell_area_glm$fitted.values |> unlist() |> as.numeric())[c(1,11)],
    fitted.se = c(
      emmeans::emmeans(object = cell_area_glm, ~ "Genotype",
                       type = 'response') |>
        as.data.frame() |>
        dplyr::filter(Genotype == "WT") |>
        dplyr::select(SE) |>
        unlist() |> as.numeric(),
      emmeans::emmeans(object = cell_area_glm, ~ "Genotype",
                       type = 'response') |>
        as.data.frame() |>
        dplyr::filter(Genotype == "MUT") |>
        dplyr::select(SE) |>
        unlist() |> as.numeric())) |>
  dplyr::distinct(Genotype, fitted.means, fitted.se) |>
  dplyr::mutate(y_min = fitted.means - fitted.se,
                y_max = fitted.means + fitted.se) |>

  ggplot2::ggplot2::ggplot(aes(
    x = Genotype,
    y = fitted.means,
    color = Genotype,
    fill = Genotype,
    alpha = 0.5))+
  ggplot2::ggplot2::geom_bar(stat = 'identity') +
  ggplot2::ggplot2::geom_errorbar(aes(x = Genotype,
                    ymin = y_min,
                    ymax = y_max), width = 0.25, inherit.aes = T) +
  ggplot2::ggplot2::geom_point(data = cell_area_glm$model$Genotype |>
               as.data.frame() |>
               dplyr::rename(Genotype = `cell_area_glm$model$Genotype`) |>
               dplyr::mutate(
                 fitted.means = c(
                   cell_area_glm$fitted.values |> unlist() |> as.numeric()),
                 fitted.se = c(
                   rep(summary(cell_area_glm)$coeff[,2][2] |>
                         unlist() |>
                         as.numeric(),
                       10),
                   rep(summary(cell_area_glm)$coeff[,2][1] |>
                         unlist() |>
                         as.numeric(),
                       13)),
                 avg_cell_body_area = c(
                   as.numeric(cell_area_glm$model$`as.numeric(Cell_Body_Area)`
                 ))) |>
               dplyr::group_by(Genotype) |>
               dplyr::mutate(mouse_n = dplyr::row_number(), .after = Genotype) |>
               dplyr::ungroup(),
             aes(x = Genotype, y = avg_cell_body_area)) +
  ggplot2::ggplot2::labs(title = 'Hippocampal Neuron Cell Body Area (glm-Gamma)',
       x = 'Genotype',
       y = bquote('Cell Body Area '(mu*m^2))) +
  ggplot2::ggplot2::theme_bw() +
  ggplot2::ggplot2::theme(title = ggplot2::ggplot2::element_text(face = 'bold', size = 12.5),
        axis.title = ggplot2::ggplot2::element_text(face = 'bold', size = 11),
        axis.text = ggplot2::ggplot2::element_text(face = 'bold', size = 11),
        panel.grid = ggplot2::ggplot2::element_blank(),
        legend.text = ggplot2::ggplot2::element_text(face = 'bold', size = 10)
  ) +
  ggplot2::ggplot2::guides(alpha = 'none') +
  ggplot2::ggplot2::scale_color_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::ggplot2::scale_fill_manual(values = c('navy', 'darkgoldenrod3')) +
  ggplot2::ggplot2::geom_segment(x = 1, xend = 2, y = 385, yend = 385, color = 'black', size = 1) +
  # ggplot2::geom_signif()
  ggplot2::ggplot2::geom_text(
    aes(label = "N.S.",
        # paste0('p-value: ',
        #        round(pf(summary(puncta_acidity_lm)$fstatistic[1],
        #                 summary(puncta_acidity_lm)$fstatistic[2],
        #                 summary(puncta_acidity_lm)$fstatistic[3],
        #                 lower.tail = FALSE) |> unlist() |> as.numeric(), 4)
        #                      ),
        fontface = 'bold'
        ),
    size = 7,
    color = 'black',
    x = 1.5,
    y = 412)
```

### Results Tables

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('### Results Tables {.tabset .tabset-pills .tabset-fade}\n')
}
```

#### Tidied Puncta Data

```{r Puncta Data, include = T, message = F, warning = F, echo = F}
Puncta_data %>%
  dplyr::rename_with(.cols = dplyr::contains("_"), ~gsub(.x, pattern = '^(.+?)(.+$)', replacement = '`\\1\\2`')) %>%
  dplyr::rename_with(.cols = dplyr::contains('_'),~gsub(.x, pattern = '_', replacement = ' ')) %>%
  dplyr::rename_with(.cols = dplyr::contains("Puncta Count"), ~gsub(.x, pattern = 'Puncta Count', replacement = '#')) %>%
  dplyr::mutate(across(c(4:ncol(.)), ~ as.numeric(.x))) %>%
  dplyr::mutate(across(c(4:ncol(.)), ~ round(.x, digits = 4))) |> 
  head()
```

```{r Gather Stats Results, include = T, message = F, warning = F, echo = F}
puncta_acidity_lm_results <- puncta_acidity_lm |>
  broom::tidy() |>
  dplyr::full_join(
    puncta_acidity_lm |>
      broom::glance()
    )

puncta_area_lm_results <- puncta_area_lm |>
  broom::tidy() |>
  dplyr::full_join(
    puncta_area_lm |> 
      broom::glance()
    )

puncta_n_lm_results <- puncta_n_lm |> 
  broom::tidy() |>
  dplyr::full_join(
    puncta_n_lm |> broom::glance()
    )

cell_area_lm_results <- cell_area_lm |> 
  broom::tidy() |>
  dplyr::full_join(
    cell_area_lm |> 
      broom::glance()
    )

cell_area_glm_results <- cell_area_glm |> 
  broom::tidy() |> 
  dplyr::mutate(null.deviance = NA) |>
  dplyr::full_join(cell_area_glm |> broom::glance())


lm_results <- puncta_acidity_lm_results |> 
  dplyr::mutate(target_var = "puncta_acidity") |>
  dplyr::full_join(puncta_area_lm_results |> 
                     dplyr::mutate(target_var = 'puncta_area')) |>
  dplyr::full_join(puncta_n_lm_results |> 
                     dplyr::mutate(target_var = 'puncta_n')) |>
  dplyr::full_join(cell_area_lm_results |> 
                     dplyr::mutate(target_var = 'cell_body_area_lm')) |>
  dplyr::full_join(cell_area_glm_results |> 
                     dplyr::mutate(target_var = 'cell_body_area_glm')) |>
  dplyr::relocate(target_var, .before = 1)
```

#### Table of Stats

```{r Model results table, include = T, message = F, warning = F, echo = F}
lm_results %>%
  dplyr::mutate(across(c(3:ncol(.)), ~as.numeric(.x))) %>% 
  dplyr::mutate(across(c(3:ncol(.)), ~round(.x, digits = 5))) |> 
  head()
```

#### Table of Predicted Values

```{r Gather predictions weights and residuals, eval = T, include = F, message = F, warning=F, echo = T}
lm_results_preds_and_resids <- puncta_acidity_lm |> 
  broom::augment() |> 
  dplyr::mutate(target_var = 'puncta_acidity') |>
  dplyr::full_join(puncta_area_lm |> 
                     broom::augment() |> 
                     dplyr::mutate(target_var = 'puncta_area')) |>
  dplyr::full_join(puncta_n_lm |> 
                     broom::augment() |> 
                     dplyr::mutate(target_var = 'puncta_n')) |>
  dplyr::full_join(cell_area_lm |> 
                     broom::augment() |> 
                     dplyr::mutate(target_var = 'cell_body_area_lm') |> 
                     dplyr::rename(Cell_Body_Area_lm = Cell_Body_Area)) |>
  dplyr::full_join(cell_area_glm |> 
                     broom::augment() |> 
                     dplyr::mutate(
                       target_var = 'cell_body_area_glm',
                       `as.numeric(Cell_Body_Area)` = as.character(
                         `as.numeric(Cell_Body_Area)`)
                       ) |> 
                     dplyr::rename(
                       Cell_Body_Area_glm = `as.numeric(Cell_Body_Area)`
                       )
                   ) |>
  dplyr::relocate(1, .after = target_var) |>
  dplyr::relocate(.resid, .after = .fitted)
```

```{r Predictions in table, eval = T, include = T, message = F, warning = F, echo = T}
lm_results_preds_and_resids %>%
  dplyr::mutate(across(c(2:ncol(.),-9), ~ as.numeric(.x))) %>%
  dplyr::mutate(across(c(2:ncol(.),-9), ~ round(.x, digits = 4))) |> 
  head()
```

#### Shapiro Results Table

```{r Gather shapiro results, eval = T, include = F, message = F, warning = F, echo = T}
shapiro_test_results <- shapiro_puncta_acidity |>
  broom::tidy() |>
  dplyr::full_join(shapiro_puncta_acidity |>
                     broom::glance()
                   ) |>
  dplyr::mutate(target_var = 'puncta_acidity') |>
  dplyr::full_join(shapiro_cell_area |>
                     broom::tidy() |>
                     dplyr::full_join(shapiro_cell_area |>
                                        broom::glance()
                                      ) |>
                     dplyr::mutate(target_var = 'cell_body_area')
                   ) |>
  dplyr::full_join(shapiro_puncta_area |>
                     broom::tidy() |>
                     dplyr::full_join(shapiro_puncta_area |>
                                        broom::glance() |>
                                        dplyr::mutate(
                                          target_var = 'puncta_area'))) |>
  dplyr::full_join(shapiro_puncta_n |>
                     broom::tidy() |>
                     dplyr::full_join(shapiro_puncta_n |>
                                        broom::glance()) |> dplyr::mutate(
                                          target_var = 'puncta_n'))
```

```{r Shapiro results table, include = T, message = F, warning = F, echo = T}
shapiro_test_results %>%
  dplyr::mutate(across(c(1:2), ~ round(.x, digits = 4))) |> 
  head()
```

