---
title: "IMPS Cluster Analysis"
author: "Erik Larsen"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    fig_width: 10
    fig_height: 10
  pdf_document:
    fig_width: 10
    fig_height: 10
    latex_engine: xelatex
  md_document:
    variant: gfm
vignette: >
  %\VignetteIndexEntry{IPMS Clustering vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 10,
  dev = c("png", "pdf"),
  fig.path = "../analysis/R/hSaint/"
)
```

## Overview

This markdown was developed to formally document an ad hoc data analysis pipeline for 
TMEM184B immunoprecipitation tandem mass-spec experiments for 
**Dr. Martha Bhattacharya's lab** at the **University of Arizona** for the
endolysosomal paper under revision (2025-02-28) for the Journal of Cell Science

Until a container is built, the `R version` used was **R 4.3.2** with the
packages installed below

## Set up Environment

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('## Set up Environment {.tabset .tabset-pills .tabset-fade}\n')
}
```

### Attach Packages

```{r Attach Packages, eval=T, include = T, message = F, warning = F, echo = T}
library(tidyverse)
library(Endo)
library(TMEM)

library(dbscan)
library(kernlab)
library(RSpectra)
library(pheatmap)
library(dynamicTreeCut)
```

### Load the Proteomics TSCs

```{r Load the IPMS hierarchical SAINT results, eval = T, include = T, message = F, warning = F, echo = T}
IPMS_counts <- Endo::IPMS_counts |> 
  dplyr::select(-1) |> 
  dplyr::rename_with(
    ~Endo::IPMS_counts |> 
      dplyr::select(-1) |> 
      dplyr::slice(1) |> 
      unlist() |> 
      as.character()
  ) |> 
  dplyr::slice(-1) |> 
  dplyr::select(-dplyr::contains("407")) |> # remove extra samples
  dplyr::rename(Protein = 1, AN = 2, MW = 3) |> # convert column names shorter
  dplyr::mutate(Protein = stringr::str_extract(Protein, pattern = 'GN=[[:alnum:]]+') %>%
                  gsub(., pattern = 'GN\\=', replacement = '')) |> # mutate HUGO symbols
  dplyr::mutate(
        dplyr::across(dplyr::contains("_"), ~dplyr::if_else(.x == '?', '0', .x)),
        dplyr::across(dplyr::contains("_"), ~dplyr::if_else(.x == '', '0', .x)),
        dplyr::across(dplyr::contains("_"), ~as.numeric(.x)
                      ) # replace ?'s, empty columns with 0's; convert to numeric
        ) |> 
      dplyr::filter(
        !grepl(AN, pattern = "DECOY")
        ) |> # filter decoy proteins out
      
      dplyr::rename_with(
        ~gsub(.x, pattern = '[0-9]+_', replacement = '')
        ) |> # remove _'s from column names
      
      dplyr::rename_with(
        ~gsub(.x, pattern = '^m', replacement = '')
        ) |> # remove m's from column names (mTMEM)
      
      dplyr::rename(BirAV5_1 = `BirA-V1`, 
                    BirAV5_2 = `BirA-V2`,
                    TMEMV5_1 = `TMEM-V1`,
                    TMEMV5_2 = `TMEM-V2`
                    ) |> 
  dplyr::filter(!is.na(Protein))

  # keep MW and AN for future mapping if necessary
protein_map <- IPMS_counts |> 
  dplyr::select(Protein, AN, MW) |> 
  dplyr::mutate(MW = gsub(MW, pattern = ' kDa', replacement = '') |> as.numeric())

  # keep the df for matrix creation
IPMS_counts <- IPMS_counts |> 
  dplyr::select(-AN, -MW)

  # sum the proteins that have multiple accessions for the same symbol
IPMS_counts <- IPMS_counts |> 
  dplyr::group_by(Protein) |> 
  dplyr::summarize(dplyr::across(dplyr::everything(), sum))

head(IPMS_counts)
```

### Load the Hierarchical SAINT Posterior Probabilities

```{r Load the Hierarchical SAINT results}
hSAINT <- readr::read_csv('../../analysis/python/hierarchical_results.csv', col_names = T) |> 
  dplyr::group_by(Protein) |> 
  dplyr::summarize(score = mean(gamma3)) |> 
  dplyr::arrange(desc(score))
```

```{r Add Empirical Flags}
hSAINT <- hSAINT |> 
  dplyr::mutate(
    lit_flag = dplyr::case_when(
      grepl(Protein,
            pattern = 'AHNAK|ALB|ANXA(1|2)|ASS1|ATP5|CFL1|CLTC|CSDA|EDARRAD|ENO|FARS(A|B)|FASN|FKSG30|GAPDH|GFAP|ILF(2|3)|LDHA|LGALS(1|3)|PCB(1|2)|PDIA6|PHB|PHB2|POTE2|PPIA|PRDX(1|2|3|4)|SERPIN(H1|A11)|SLC25A|TUFM|TXN|UBA52') ~ 1,
      TRUE ~ 0), # Mulcahy contams (2008 paper)
    lit_flag = dplyr::case_when(
      lit_flag == 1 ~ 1,
      grepl(Protein,
            pattern = 'EEF1|EIF|HNRN|HSPA|KRT|TUB(A|B)|RPL|HIST2|H2A|RRP|(X|I)PO|NUP|DNAJ') ~ 1,
      TRUE ~ 0), # Dunham contams (2008 paper)
    CRAPome_flag = dplyr::case_when(Protein %in% c(
      Endo::CRAPome_results |>
        dplyr::filter(!grepl(Mapped, pattern = '/|identifier')) |>
        dplyr::select(1:7) |>
        dplyr::rename(User_input = User,
                      Mapped_Gene_Symbol = Input,
                      Num_Exp_Found = Mapped,
                      Num_Exp_Total = Symbol,
                      Avg_SC = Num,
                      Max_SC = of) |>
        dplyr::mutate(dplyr::across(c(3,5:7), ~as.numeric(.x))) |>
        dplyr::select(-Gene) |> 
        dplyr::filter(Num_Exp_Found > 35.8) |> # greater than 5% of experiments
        dplyr::select(Mapped_Gene_Symbol) |>
        unlist() |>
        as.character() |> 
        sort()
      ) ~ 1, TRUE ~ 0)
  )
```


### Transform Data

```{r transform data}
## re-shape 
IPMS_mat <- as.matrix(IPMS_counts[,-1])
rownames(IPMS_mat) <- IPMS_counts |> 
  dplyr::select(1) |> unlist() |> as.character()

# remove all zero's rows
IPMS_mat <- IPMS_mat[rowSums(IPMS_mat) > 0 , , drop = FALSE]
# remove all zero variance rows
IPMS_mat <- IPMS_mat[apply(IPMS_mat, 1, sd)> 0, , drop = FALSE]

# log transformed
IPMS_mat_log <- log1p(IPMS_mat)

# Z-transformed (confirming clusters are insensitive to large counts)
IPMS_mat_Z <- t(scale(t(IPMS_mat)))
```

## Clustering

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('## Clustering {.tabset .tabset-pills .tabset-fade}\n')
}
```

### Hierarchical

#### Raw Counts

```{r Hierarchical Clustering raw}
d <- stats::as.dist(1 - stats::cor(t(IPMS_mat), use = 'pairwise.complete.obs'))
hc <- stats::hclust(d, method = "average")
```

```{r Grid Search Cluster Size}
sizes <- c(20, 30, 50, 80, 100)
results <- list()

for (m in sizes) {
  cl <- dynamicTreeCut::cutreeDynamic(
    dendro = hc,
    distM = as.matrix(d),
    deepSplit = 1,
    pamRespectsDendro = TRUE,
    minClusterSize = m
  )
  results[[as.character(m)]] <- cl
  cat("minClusterSize =", m, "→", length(table(cl)), "modules\n")
}
rm(list = c('cl', 'm', 'sizes'))
```

  + `optimal minimum cluster size` is **50** (elbow; diminishing returns after)
  
  + `# modules` = **28**

```{r Clusters on Raw Counts}
clusters_opt <- dynamicTreeCut::cutreeDynamic(hc,
                                          distM = as.matrix(d),
                                          deepSplit = 1,
                                          pamRespectsDendro = T,
                                          minClusterSize = 50)
names(clusters_opt) <- rownames(IPMS_mat)
```
```{r Get Modules}
module_ids <- sort(unique(clusters_opt))
module_colors <- stats::setNames(
  grDevices::rainbow(length(module_ids), s = 0.6, v = 0.9),
  module_ids
)

annotation_colors <- list(Module = module_colors)
```

Sparse data is too difficult to discern from a global view

  -> Z transform the raw counts after clustering to plot
  
```{r RawZ scale}
IPMS_z <- t(scale(t(IPMS_mat)))
colnames(IPMS_z) <- colnames(IPMS_mat)

condition <- sub('_.*', '', colnames(IPMS_mat))

col_order <- unlist(
  lapply(
    split(seq_along(condition), condition), function(idx) {
      submat <- IPMS_z[, idx, drop = FALSE]
      hc_sub <- stats::hclust(stats::dist(t(submat)), method = 'ward.D2')
      idx[hc_sub$order]
    }))

IPMS_z_ordered <- IPMS_z[, col_order]
```

## Module Descriptions

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('## Module Descriptions {.tabset .tabset-pills .tabset-fade}\n')
}
```

### Hierarchical Raw Counts

Extract gene names from the hierarchically clustered modules and convert to a dataframe

```{r Extract Gene Names from Modules}
modules_list_idx <- lapply(sort(unique(clusters_opt)), function(m) {
  which(clusters_opt == m)
})
names(modules_list_idx) <- sort(unique(clusters_opt))

modules_list <- lapply(sort(unique(clusters_opt)), function(m) {
  rownames(IPMS_mat)[clusters_opt == m]
})
names(modules_list) <- sort(unique(clusters_opt)) |> as.character()

modules_df <- modules_list %>%
  purrr::map_df(., .f = as.data.frame, .id = 'module') |> 
  dplyr::rename(Protein = 2) |> 
  dplyr::relocate(Protein, .before = 1)
```

Include score summaries (mean and median posterior probability scores, ranks, and literature or CRAPome contamination rate)

```{r Summarize SAINT Scores and Contamination Rates}
module_scores <- modules_df |>  
  dplyr::inner_join(
    hSAINT
  ) |> 
  dplyr::arrange(desc(score)) |> 
  dplyr::group_by(module) |> 
  dplyr::summarize(mean_score = mean(score),
                   median_score = stats::median(score),
                   n = dplyr::n(),
                   lit_flag_perc = (sum(lit_flag)/n)*100,
                   CRAPome_flag_perc = (sum(CRAPome_flag)/n)*100) |> 
  dplyr::arrange(desc(mean_score)) |> 
  dplyr::mutate(mean_rank = dplyr::row_number()) |> 
  dplyr::arrange(desc(median_score)) |> 
  dplyr::mutate(median_rank = dplyr::row_number()) |> 
  dplyr::arrange(desc(mean_score))
```

Join the module scores to the modules (per protein) dataframe and the `hSAINT` results for classification

```{r Join the Summary dataframe to the Protein Level dataframes}
modules_df <- modules_df |> 
  dplyr::inner_join(
    hSAINT
  ) |> 
  dplyr::full_join(
    module_scores |> 
      dplyr::ungroup()
  ) |> 
  dplyr::mutate(SAINT_classification = dplyr::case_when(mean_rank <= 5 ~ 'High SAINT',
                                                        mean_rank > 5 ~ 'Low SAINT'
                                                  ),
                contams_classification = dplyr::case_when(lit_flag_perc > 5 ~'High Contaminants',
                                                          TRUE ~ 'Low Contaminants')) |> 
  dplyr::mutate(classification = paste0(SAINT_classification, ", ", contams_classification)) |> 
  dplyr::select(-SAINT_classification,
                -contams_classification) |> 
  dplyr::relocate(classification, .after = module)
```

```{r Downstream Analysis}
library(clusterProfiler)
library(org.Hs.eg.db)
library(ReactomePA)
library(AnnotationDbi)

EntrezIDs <- AnnotationDbi::select(
  org.Hs.eg.db,
  keys = modules_df |> dplyr::distinct(Protein) |> unlist() |> as.character(),
  columns = 'ENTREZID',
  keytype = 'SYMBOL'
) |> 
  dplyr::filter(!is.na(2))

EntrezMap <- stats::setNames(EntrezIDs$ENTREZID, EntrezIDs$SYMBOL)
```

```{r}
get_GO <- function(genes, ontology) {
  clusterProfiler::enrichGO(
    gene = modules_df |> dplyr::distinct(Protein) |> unlist() |> as.character(),
    OrgDb = org.Hs.eg.db,
    keyType = 'SYMBOL',
    ont = ontology,
    pAdjustMethod = 'BH',
    qvalueCutoff = 0.05,
    readable = T
  )
}

get_kegg <- function(genes, EntrezMap) {
  entrez <- EntrezMap[genes]
  entrez <- entrez[!is.na(entrez)]
  if (length(entrez)==0) {
    return(NULL)
  }
  clusterProfiler::enrichKEGG(
    gene = entrez,
    organism = 'hsa',
    pAdjustMethod = 'BH',
    qvalueCutoff = 0.05
  )
}

get_reactome <- function(genes, EntrezMap) {
  entrez <- EntrezMap[genes]
  entrez <- entrez[!is.na(entrez)]
  if (length(entrez)==0) {
    return(NULL)
  }
  ReactomePA::enrichPathway(
    gene = entrez,
    organism = 'human',
    pAdjustMethod = 'BH',
    qvalueCutoff = 0.05,
    readable = T
  )
}

enrichment_results <- lapply(modules_df |> dplyr::distinct(module) |> unlist() |> as.character(), function(mod){
  genes <- modules_df |> dplyr::filter(module == mod) |> dplyr::distinct(Protein) |> unlist() |> as.character()
  
  list(
    module = mod,
    go_bp = get_GO(genes, ontology = 'BP'),
    go_cc = get_GO(genes, ontology = 'CC'),
    go_mf = get_GO(genes, ontology = 'MF'),
    
    kegg = get_kegg(genes, EntrezMap),
    reactome = get_reactome(genes, EntrezMap)
  )
})

names(enrichment_results) <- modules_df |> dplyr::distinct(module) |> unlist() |> as.character()
```


## Plots

```{r, results='asis', echo=FALSE}
if (knitr::is_html_output()) {
  cat('## Plots {.tabset .tabset-pills .tabset-fade}\n')
}
```

### Hierarchical

#### Raw Counts

```{r RawClusterZAll}
pheatmap::pheatmap(
  IPMS_z_ordered,
  color = grDevices::colorRampPalette(c('navy', 'white', 'darkgoldenrod'))((200)),
  cluster_rows = hc,
  cluster_cols = F,
  show_rownames = F,
  annotation_row = data.frame(Module = clusters_opt),
  annotation_colors = annotation_colors,
  angle_col = 0,
  use_raster = F,
  border_color = NA
)
```

####

```{r}

```


#### Z-scored Counts

```{r Hierarchical Clustering Z, include = T, warning = F, message = F, echo = T}
d_Z <- as.dist(1 - cor(t(IPMS_mat_Z), method = "pearson"))
hc_Z <- hclust(d_Z, method = "average")
```

