---
title: "Spectral Clustering vignette"
author: "Erik Larsen"
date: "`r Sys.Date()`"
always_allow_html: true
output:
  html_document:
    toc: true
    fig_width: 10
    fig_height: 10
  pdf_document:
    fig_width: 10
    fig_height: 10
    latex_engine: xelatex
  md_document:
    variant: gfm
vignette: >
  %\VignetteIndexEntry{Spectral Clustering vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

This markdown was developed to formally document an ad-hoc cluster analysis for 
TMEM184B immunoprecipitation tandem mass-spec experiments for 
**Dr. Martha Bhattacharya's lab** at the **University of Arizona** for the
endolysosomal paper under revision (2025-02-28) for the Journal of Cell Science

This vignette documents the `Spectral Clustering` of this IPMS data

```{r reset-shiny-mode, include=FALSE}
options(htmlwidgets.shinyMode = FALSE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 12,
  dev = c("png", "pdf"),
  fig.path = "../../analysis/R/hClust/"
)
```

## Attach Packages

```{r Attach Packages, message=F,warning=F}
# data/wrangling
library(tidyverse)
library(Endo)
library(DT)

# clustering
library(pheatmap)
library(dynamicTreeCut)
  ## (kNN)
library(FNN)

# GSEA/viz
library(clusterProfiler)
library(org.Hs.eg.db)
library(ReactomePA)
library(AnnotationDbi)

# progress bar
library(progressr)

# parallelization
library(future)
library(future.apply)

# network viz
library(visNetwork)

options(stringsAsFactors = FALSE)
```

## Load the Pre-Computed Data

```{r Data Load}
# Load precomputed objects from preprocessing
load("../../analysis/R/precompute_objects.rda")
```

```{r Second Data Load, echo = FALSE}
rm(IPMS_mat_log)
rm(IPMS_mat_Z)
```

## Transform the Data to Distance Matrix

```{r Compute Distance Matrix}
IPMS_dist <- 1 - stats::cor(t(IPMS_mat),
                            use = 'pairwise.complete.obs') |> 
  as.matrix()
```


```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Spectral Clustering {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Spectral Clustering</strong></summary>\n')
} else {
  cat('# Spectral Clustering\n')
}
```

Spectral clustering *uses the same correlation-based distance representation as
[hierarchical clustering](HierarchicalClustering.Rmd).

We compute the pairwise distance matrix as 
**1 - Pearson correlation between proteins**, matching the above vignette, exactly.

This method was chosen because of the wild variation in protein abundance, 
contamination proteins often inflating magnitude, immunoprecipitation (bait) 
biases, emphasis on the pattern in terms of signal, not scale.

Correlation distance:

+ centers and scales each protein
+ removes/accounts for magnitude effects, focusing on the shape of the profile
  + is therefore robust to contaminants and bait biases

This is standard in proteomics clustering

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('## Similarity Matrix {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Similarity Matrix</strong></summary>\n')
} else {
  cat('## Similarity Matrix\n')
}
```

Build a similarity matrix from the distance matrix derived from correlation distances of raw counts

  -> will be used for clustering (closeness between data, e.g. proteins)
  
  Two options:
  
  1. Gaussian similarity matrix (using the Radial Basis Function kernel)
  
    + ideal for smooth, low-noise datasets
    + smooth, continuous calculations of distances without hard cutoffs
    
  2. k-Nearest Neighbors adjacency graph
  
    + ideal for sparse or data with heteregeneous density; noisy data (e.g. 
    IPMS datasets with lots of contaminants)
    
  We will compare and select the method that yields the most stable Laplacian
  spectrum
  
### Gaussian (Radial Basis Function) Kernel Similarity Matrix

*S_ij* = exp(-(*D_ij*^2)/2*sigma*^2)
  
```{r Sim Matrix Construction w Gaussian kernel aka radial basis kernel}
# choose a kernel width (sigma) based on the distance distribution
sigma <- stats::median(IPMS_dist)

# compute the Gaussian (RBF) similarity matrix
sim_mat <- exp(-(IPMS_dist^2)/(2*sigma^2))
```
  
### kNN Adjacency

```{r Sim Matrix Construction w kNN}
# compute k-nearest neighbors from teh correlation-distance matrix
knn_idx <- FNN::get.knn(IPMS_dist, k = 10)$nn.index

# convert to binary adjacency matrix
adjacency <- matrix(0, nrow = nrow(knn_index), ncol = nrow(knn_idx))

for (i in seq_len(nrow(knn_idx))) {
  adjacency[i, knn_idx[i, ]] <- 1
}

# make symmetrical
symmetrical_adjacency <- (adjacency + t(adjacency)) > 0

# build kNN graph
knn_graph <- FNN::get.knn(, k = 10)$nn.index
```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Laplacian {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Laplacian</strong></summary>\n')
} else {
  cat('# Laplacian\n')
}
```

Compute the graph `Laplacian` of the similarity or adjacency matrix

+ this is the formal encoding of the graph structure based on distribution of 
space (similarity distances between nodes)

+ **The Laplacian** measures how each point (protein) differs from the weighted
average of its neighbors:

  + L = D - W

+ where:
  
  + *W* is either the `Gaussian similarity matrix` (*S*, `sim_mat`) or `kNN adjacency matrix`
  (*A*, `adjacency_sym`)
  + *D* is the degree matrix (diagonal, i.e. total connection strength of a node)
    + D[i,i] = sum_j*W[i,j]
    + `Gaussian` degrees vary smoothly; `kNN` degrees are roughly constant
    
+ The standard approach (used here) to compute the `Laplacian` for spectral clustering is to
normalize it to handle contaminants, uneven cluster sizes and heterogeneous densities:

  + *L_norm* = *D*^(-1/2)(*D*-*W*)*D*^(-1/2)
  or *L_norm* = *I*-*D*^(-1/2)*WD*^(-1/2)
  
+ **The Laplacian** is the operator whose eigenvectors reveal:

  + connected components
  + cluster structure

## Diagonal, Normalized Laplacian

```{r Construct the Laplacian on the Gaussian}
# choose W: either sim_mat (Gaussian) or A_sym (kNN)
if ( choose_similarity_approach == 'A' ) {
  W <- sim_mat
} else {
  W <- adjacency_sim
}

# degree matrix
D <- diag(rowSums(W))

# normalized Laplacian
D_inv_sqrt <- diag(1 / sqrt(rowSums(W)))
L_norm <- diag(nrow(W)) - D_inv_sqrt %*% W %*% D_inv_sqrt
```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Eigen Decomposition {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Eigen Decomposition</strong></summary>\n')
} else {
  cat('# Eigen Decomposition\n')
}
```

Conduct Eigen decomposition and extract eigenvectors as an embedding

## Similarity Matrix

```{r Conduct Eigen decomposition on similarity matrix}
# compute eigen decomposition of the normalized Laplacian
eig <- eigen(L_norm, symmetric = TRUE)

# extract eigenvalues and eigenvectors
eigenvalues <- eig$values
eigenvectors <- eig$vectors
```

## Choose Embedding Dimension

```{r Select Number of Eigenvectors to retain}
# inspect eigenvalues to identify the eigengap
plot(eigenvalues,
     type = "b",
     main = "Laplacian Eigenvalue Spectrum",
     xlab = "Index",
     ylab = "Eigenvalue")
```

```{r}
# choose k based on the eigengap
k <- 4   # example

# spectral embedding: use the first k non-trivial eigenvectors
embedding <- eigenvectors[, 2:(k + 1)]
```


```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# k-means clustering {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>k-means clustering</strong></summary>\n')
} else {
  cat('# k-means\n')
}
```

Conduct k-means clustering on the eigenvectors/embedding

```{r kMeans on embeddings}
set.seed(4)
labels <- stats::kmeans(embedding, centers = k)$cluster
```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Results {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Results</strong></summary>\n')
} else {
  cat('# Results\n')
}
```

```{r Collect Results}
spectral_result <- list(
  labels = labels,
  embedding = embedding,
  similarity = sim_mat
)
```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Visualizations {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Visualizations</strong></summary>\n')
} else {
  cat('# Visualizations\n')
}
```

## Cluster Barplot

```{r ClusterBarPlot}
```

## Heatmap of Similarity Matrix

```{r SimMatHeatmap}

```

## Embedding

```{r PCA of Embedding}

```

## Network

```{r}

```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Coherence {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Coherence</strong></summary>\n')
} else {
  cat('# Coherence\n')
}
```

```{r Compute coherence}

```

