---
title: "IPMS Clustering Pre-Processing"
author: "Erik Larsen"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    fig_width: 10
    fig_height: 10
  pdf_document:
    fig_width: 10
    fig_height: 10
    latex_engine: xelatex
  md_document:
    variant: gfm
vignette: >
  %\VignetteIndexEntry{Clustering PreProcessing vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 10,
  dev = c("png", "pdf"),
  fig.path = "../analysis/R/hSaint/"
)
```

# Overview

This markdown was developed to formally document an ad-hoc cluster analysis for 
TMEM184B immunoprecipitation tandem mass-spec experiments for 
**Dr. Martha Bhattacharya's lab** at the **University of Arizona** for the
endolysosomal paper under revision (2025-02-28) for the Journal of Cell Science

This vignette documents the data pre-processing of IPMS counts and [Hierarchical 
SAINT mixture modeling](../python/README.md) for `Hierarchical Clustering`, 
`Spectral Clustering`, and `HDBSCAN`

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Set up Environment {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Set up Environment</strong></summary>\n')
} else {
  cat('# Set up Environment\n')
}
```

## Attach Packages

```{r Attach Packages}
# data/wrangling
library(tidyverse)
library(Endo)
```

## Load the Proteomics TSCs

```{r Load the IPMS hierarchical SAINT results}
IPMS_counts <- Endo::IPMS_counts |> 
  dplyr::select(-1) |> 
  dplyr::rename_with(
    ~Endo::IPMS_counts |> 
      dplyr::select(-1) |> 
      dplyr::slice(1) |> 
      unlist() |> as.character() 
  ) |> 
  dplyr::slice(-1) |> 
  dplyr::select(-dplyr::contains("407")) |> # remove extra samples
  dplyr::rename(Protein = 1, AN = 2, MW = 3) |> # convert column names shorter
  dplyr::mutate(Protein = stringr::str_extract(Protein,
                                               pattern = 'GN=[[:alnum:]]+') %>%
                  gsub(.,
                       pattern = 'GN\\=',
                       replacement = '')) |> # mutate HUGO symbols
  dplyr::mutate(
        dplyr::across(dplyr::contains("_"), ~dplyr::if_else(.x == '?', '0', .x)),
        dplyr::across(dplyr::contains("_"), ~dplyr::if_else(.x == '', '0', .x)),
        dplyr::across(dplyr::contains("_"), ~as.numeric(.x)
                      ) # replace ?'s, empty columns with 0's; make numeric
        ) |> 
      dplyr::filter(
        !grepl(AN, pattern = "DECOY")
        ) |> # filter decoy proteins out
      
      dplyr::rename_with(
        ~gsub(.x, pattern = '[0-9]+_', replacement = '')
        ) |> # remove _'s from column names
      
      dplyr::rename_with(
        ~gsub(.x, pattern = '^m', replacement = '')
        ) |> # remove m's from column names (mTMEM)
      
      dplyr::rename(BirAV5_1 = `BirA-V1`, 
                    BirAV5_2 = `BirA-V2`,
                    TMEMV5_1 = `TMEM-V1`,
                    TMEMV5_2 = `TMEM-V2`
                    ) |> 
  dplyr::filter(!is.na(Protein))

  # keep MW and AN for future mapping if necessary
protein_map <- IPMS_counts |> 
  dplyr::select(Protein, AN, MW) |> 
  dplyr::mutate(MW = gsub(MW, pattern = ' kDa', replacement = '') |> 
                  as.numeric())

  # keep the df for matrix creation
IPMS_counts <- IPMS_counts |> 
  dplyr::select(-AN, -MW)

  # sum the proteins that have multiple accessions for the same symbol
IPMS_counts <- IPMS_counts |> 
  dplyr::group_by(Protein) |> 
  dplyr::summarize(dplyr::across(dplyr::everything(), sum))

head(IPMS_counts)
```

## Load the Hierarchical SAINT Posterior Probabilities

```{r Load the Hierarchical SAINT results}
hSAINT <- readr::read_csv('../../analysis/python/hierarchical_results.csv',
                          col_names = T) |> 
  dplyr::group_by(Protein) |> 
  dplyr::summarize(score = mean(gamma3)) |> 
  dplyr::arrange(desc(score))
```

```{r Add Empirical Flags}
hSAINT <- hSAINT |> 
  dplyr::mutate(
    lit_flag = dplyr::case_when(
      grepl(Protein,
            pattern = 'AHNAK|ALB|ANXA(1|2)|ASS1|ATP5|CFL1|CLTC|CSDA|EDARRAD|ENO|FARS(A|B)|FASN|FKSG30|GAPDH|GFAP|ILF(2|3)|LDHA|LGALS(1|3)|PCB(1|2)|PDIA6|PHB|PHB2|POTE2|PPIA|PRDX(1|2|3|4)|SERPIN(H1|A11)|SLC25A|TUFM|TXN|UBA52') ~ 1,
      TRUE ~ 0), # Mulcahy contams (2008 paper)
    lit_flag = dplyr::case_when(
      lit_flag == 1 ~ 1,
      grepl(Protein,
            pattern = 'EEF1|EIF|HNRN|HSPA|KRT|TUB(A|B)|RPL|HIST2|H2A|RRP|(X|I)PO|NUP|DNAJ') ~ 1,
      TRUE ~ 0), # Dunham contams (2008 paper)
    CRAPome_flag = dplyr::case_when(Protein %in% c(
      Endo::CRAPome_results |>
        dplyr::filter(!grepl(Mapped, pattern = '/|identifier')) |>
        dplyr::select(1:7) |>
        dplyr::rename(User_input = User,
                      Mapped_Gene_Symbol = Input,
                      Num_Exp_Found = Mapped,
                      Num_Exp_Total = Symbol,
                      Avg_SC = Num,
                      Max_SC = of) |>
        dplyr::mutate(dplyr::across(c(3,5:7), ~as.numeric(.x))) |>
        dplyr::select(-Gene) |> 
        dplyr::filter(Num_Exp_Found > 35.8) |> # greater than 5% of experiments
        dplyr::select(Mapped_Gene_Symbol) |>
        dplyr::pull() |> 
        sort()
      ) ~ 1, TRUE ~ 0)
  )
```

## Transform Data

```{r Transform data}
## re-shape 
IPMS_mat <- as.matrix(IPMS_counts[-1,-1])
rownames(IPMS_mat) <- IPMS_counts |> 
  dplyr::select(1) |> 
  dplyr::slice(-1) |> 
  dplyr::pull()

# remove all zero's rows
IPMS_mat <- IPMS_mat[rowSums(IPMS_mat) > 0 , , drop = FALSE]
# remove all zero variance rows
IPMS_mat <- IPMS_mat[apply(IPMS_mat, 1, sd)> 0, , drop = FALSE]

# log transformed
IPMS_mat_log <- log1p(IPMS_mat)

# Z-transformed (confirming clusters are insensitive to large counts)
IPMS_mat_Z <- t(scale(t(IPMS_mat)))
```

## Save Data

```{r Save PreCompute Objects}
save(IPMS_counts,
     IPMS_mat,
     IPMS_mat_log,
     IPMS_mat_Z,
     hSAINT,
     file = 'precompute_objects.rda')
```

```{r, results='asis', echo=FALSE}
if (!knitr::is_html_output()) {
  cat('</details>\n')
}
```
